---
title: "Mentoring for gender equality in early-career grant receipt: main analyses"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---

This lab journal demonstrates how we execute the main analyses discussed in the results section. 
  
----

# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}



fsave <- function(x, file, location="./data/processed/") {
  datename <- substr(gsub("[:-]", "", Sys.time()), 1,8)  
  totalname <- paste(location, datename, file, sep="")
  save(x, file = totalname)  
}



```

---  

# Packages


- `tidyverse`: For general data manipulation

- `boot`: To create bootstrapped standard errors, following the procedure delineated [here](https://www.jochemtolsma.nl/tutorials/me/)


```{r, results='hide'}

packages = c("tidyverse", "boot")

fpackage.check(packages)


```

--- 


# Input

We use one processed dataset

* [veni_ppf](data/processed/veni_ppf.rda): Processed dataset containing all independent variables and the dependent variable
    - name of dataset: `veni_ppf` 



```{r files, eval=TRUE}

load(file = "data/processed/veni_ppf.rda")

```

  
---  



# Analyses

```{r}

summary(veni_ppf$gender_2, useNA="always")

veni_ppf %>%
  filter(year>2002) %>%
  group_by(time, gender_2) %>%
  summarise(event = sum(veni),
            total = n()) %>%
  mutate(hazard = event/total) %>%
  ggplot(aes(x=time, y = log(-log(1-hazard)), group = gender_2, color=gender_2)) +
  geom_point() +
  geom_smooth()

veni_ppf %>%
  filter(year>2002) %>%
  group_by(time, gender_2) %>%
  summarise(event = sum(veni),
            total = n()) %>%
  mutate(hazard = event/total) %>%
  ggplot(aes(x=time, y = hazard, group = gender_2, color=gender_2)) +
  geom_point() +
  geom_smooth(se=FALSE) +
  scale_y_continuous(limits=c(0, 0.04))


```



# M1: Only gender and time

```{r}


#veni_ppf[veni_ppf$uni!="WUR",] -> veni_ppf
#veni_ppf[veni_ppf$uni!="EUR",]-> veni_ppf



M1 <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M1)


```



# M2: gender_2 * time

```{r}


M2 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M2)


```

Predicted probability Veni receipt extension period

```{r}

men_ext <- wom_ext <- veni_ppf
wom_ext$gender_2 <- "women" 
men_ext$gender_2 <- "men" 
    
wom_ext$gender_2 <- factor(wom_ext$gender_2, levels=levels(veni_ppf$gender_2))
men_ext$gender_2 <- factor(men_ext$gender_2, levels=levels(veni_ppf$gender_2))

wom_ext$phd_year <- 14
men_ext$phd_year <- 14

wom_ext$extended <- "after extension" 
men_ext$extended <- "after extension" 
    
wom_ext$extended <- factor(wom_ext$extended, levels=levels(veni_ppf$extended))
men_ext$extended <- factor(men_ext$extended, levels=levels(veni_ppf$extended))

predict(M2, newdata=wom_ext, type="response")[1]
predict(M2, newdata=men_ext, type="response")[1]

```





# M3: addition all control variables

```{r}

M3 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M3)

```


# M4: mediation teamsize and number of professors

```{r}

M4 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M4)

```




# M5: all mediations

```{r}

M5 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1),
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M5)

```





# M6 (supervision team * gender)

```{r}

M6 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1)*as.factor(gender_2),
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M6)

```





# Average marginal effects (AMEs)

## M1 

```{r, eval=FALSE}

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)
  
  suppressWarnings({
    
    # GENDER (H1)  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    #calculate the predicted probabilities for gender
    pw <- as.numeric(unlist(predict(M, type="response", newdata=dfwomen)))
    pm <- as.numeric(unlist(predict(M, type="response", newdata=dfmen)))
    
    # AME
    AME_gender <- mean(pw - pm, na.rm=TRUE)
    
    
    # EXTENDED
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    ptp <- as.numeric(unlist(predict(M, type="response", newdata=dfext1)))
    ptm <- as.numeric(unlist(predict(M, type="response", newdata=dfext0)))
    # AME
    AME_ext <- mean(ptp-ptm, na.rm=TRUE)

    
    # PHD COHORT MAIN
    s <- 1 # defining a small increment of time
    
    dfcohp <- dfcohm <- df
    dfcohp$phd_year <- df$phd_year + s
    dfcohm$phd_year <- df$phd_year - s
    pcohp <- as.numeric(unlist(predict(M, type="response", newdata=dfcohp)))
    pcohm <- as.numeric(unlist(predict(M, type="response", newdata=dfcohm)))
    # AME
    AME_cohort <- mean((pcohp-pcohm) / (2*s), na.rm=TRUE)

  })
  
  c(AME_gender, AME_ext, AME_cohort)
   #save results
}

b1 <- boot(veni_ppf, bootFunc, R = 1000, parallel="snow", ncpus=10)


fsave(b1, file = "boot1.rda", location = "./results/")



```


```{r, echo=FALSE}

load("./results/20240319boot1.rda")
b1 <- x
rm(x)

```

```{r}

original <- b1$t0
bias <- colMeans(b1$t) - b1$t0
se <- apply(b1$t, 2, sd)

boot.df1 <- data.frame(original=original, bias=bias, se=se)
row.names(boot.df1) <- c("AME_gender", "AME_ext", "AME_cohort")

boot.df1$t <- (boot.df1$original / boot.df1$se)

round(boot.df1, 5)


```


## M2 

Gender 
Gender * extension


```{r, eval=FALSE}

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M <- glm(formula = veni ~  as.factor(extended) * as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)
  
    suppressWarnings({
  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    #calculate the predicted probabilities for gender
    pw <- as.numeric(unlist(predict(M, type="response", newdata=dfwomen)))
    pm <- as.numeric(unlist(predict(M, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender <- mean(pw - pm, na.rm=TRUE)
   
    # extension interactions
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    
    pwp <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene1)))
    pwm <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene0)))
    pmp <- as.numeric(unlist(predict(M, type="response", newdata=dfmene1)))
    pmm <- as.numeric(unlist(predict(M, type="response", newdata=dfmene0)))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    ptp <- as.numeric(unlist(predict(M, type="response", newdata=dfext1)))
    ptm <- as.numeric(unlist(predict(M, type="response", newdata=dfext0)))

    
    # cohort main effect
    s <- 1
    dfcohp <- dfcohm <- df
    dfcohp$phd_year <- df$phd_year + s
    dfcohm$phd_year <- df$phd_year - s
    
    pcohp <- as.numeric(unlist(predict(M, type="response", newdata=dfcohp)))
    pcohm <- as.numeric(unlist(predict(M, type="response", newdata=dfcohm)))
    
    
# average marginal effects
AME_genderext <- mean((pwp - pmp) - (pwm - pmm), na.rm=TRUE)

AME_ext <- mean(ptp-ptm, na.rm=TRUE)

AME_cohort <- mean((pcohp-pcohm) / (2*s), na.rm=TRUE)


  })
  
  c(AME_gender, AME_ext, AME_genderext, AME_cohort)
   #save results
  
}

b2 <- boot(veni_ppf, bootFunc, R = 1000, parallel="snow", ncpus=10)


fsave(b2, file = "boot2.rda", location = "./results/")

```


```{r, echo=FALSE}

load("./results/20240319boot2.rda")
b2 <- x
rm(x)

```


```{r}

original <- b2$t0
bias <- colMeans(b2$t) - b2$t0
se <- apply(b2$t, 2, sd)

boot.df2 <- data.frame(original=original, bias=bias, se=se)
row.names(boot.df2) <- c("AME_gender", "AME_ext", "AME_genderext","AME_cohort")

boot.df2$t <- (boot.df2$original / boot.df2$se)

round(boot.df2, 5)


```


## M3

```{r,eval=FALSE}

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M <- glm(formula = veni ~  as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  suppressWarnings({
  
    # gender 
    
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    pw <- as.numeric(unlist(predict(M, type="response", newdata=dfwomen)))
    pm <- as.numeric(unlist(predict(M, type="response", newdata=dfmen)))
   
    # extension interactions
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    
    pwp <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene1)))
    pwm <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene0)))
    pmp <- as.numeric(unlist(predict(M, type="response", newdata=dfmene1)))
    pmm <- as.numeric(unlist(predict(M, type="response", newdata=dfmene0)))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    ptp <- as.numeric(unlist(predict(M, type="response", newdata=dfext1)))
    ptm <- as.numeric(unlist(predict(M, type="response", newdata=dfext0)))

    # cohort main effect
    s <- 1
    
    dfcohp <- dfcohm <- df
    dfcohp$phd_year <- df$phd_year + s
    dfcohm$phd_year <- df$phd_year - s
    
    pcohp <- as.numeric(unlist(predict(M, type="response", newdata=dfcohp)))
    pcohm <- as.numeric(unlist(predict(M, type="response", newdata=dfcohm)))
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    pcp <- as.numeric(unlist(predict(M, type="response", newdata=dfpcp)))
    pcm <- as.numeric(unlist(predict(M, type="response", newdata=dfpcm)))
    
    
    # pubs previous year
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    ppp <- as.numeric(unlist(predict(M, type="response", newdata=dfppp)))
    ppm <- as.numeric(unlist(predict(M, type="response", newdata=dfppm)))
    
 
# marginal effects

AME_gender <- mean(pw - pm, na.rm=TRUE)
    
AME_genderext <- mean((pwp - pmp) - (pwm - pmm), na.rm=TRUE)

AME_ext <- mean(ptp-ptm, na.rm=TRUE)

AME_cohort <- mean((pcohp-pcohm) / (2*s), na.rm=TRUE)

AME_cumulpubs <- mean((pcp - pcm) / (2*s), na.rm=TRUE)

AME_prevpubs <- mean((ppp - ppm) / (2*s), na.rm=TRUE)

  })
  
  c(AME_gender, AME_ext, AME_genderext, AME_cohort, AME_cumulpubs, AME_prevpubs)
   #save results
  
}

b3 <- boot(veni_ppf, bootFunc, R = 1000, parallel="snow", ncpus=10)


fsave(b3, file = "boot3a.rda", location = "./results/")


```



```{r, echo=FALSE}

load("./results/20240319boot3a.rda")
b3 <- x
rm(x)

```

```{r}

original <- b3$t0
bias <- colMeans(b3$t) - b3$t0
se <- apply(b3$t, 2, sd)

boot.df3 <- data.frame(original=original, bias=bias, se=se)
row.names(boot.df3) <- c("AME_gender", "AME_ext", "AME_genderext", "AME_cohort", "AME_cumulpubs", "AME_prevpubs")

boot.df3$t <- (boot.df3$original / boot.df3$se)

round(boot.df3, 5)

```



## M4

```{r, eval=FALSE}

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p), family = binomial(link="cloglog"), data = df)
  
      suppressWarnings({
  
    # gender 
    
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    pw <- as.numeric(unlist(predict(M, type="response", newdata=dfwomen)))
    pm <- as.numeric(unlist(predict(M, type="response", newdata=dfmen)))
   
    # extension interactions
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    
    pwp <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene1)))
    pwm <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene0)))
    pmp <- as.numeric(unlist(predict(M, type="response", newdata=dfmene1)))
    pmm <- as.numeric(unlist(predict(M, type="response", newdata=dfmene0)))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    ptp <- as.numeric(unlist(predict(M, type="response", newdata=dfext1)))
    ptm <- as.numeric(unlist(predict(M, type="response", newdata=dfext0)))

    
    # cohort main effect
    s <- 1
    
    dfcohp <- dfcohm <- df
    dfcohp$phd_year <- df$phd_year + s
    dfcohm$phd_year <- df$phd_year - s
    
    pcohp <- as.numeric(unlist(predict(M, type="response", newdata=dfcohp)))
    pcohm <- as.numeric(unlist(predict(M, type="response", newdata=dfcohm)))
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    pcp <- as.numeric(unlist(predict(M, type="response", newdata=dfpcp)))
    pcm <- as.numeric(unlist(predict(M, type="response", newdata=dfpcm)))
    
    
    # pubs previous year
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    ppp <- as.numeric(unlist(predict(M, type="response", newdata=dfppp)))
    ppm <- as.numeric(unlist(predict(M, type="response", newdata=dfppm)))
    
    # network size
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    pnsp <- as.numeric(unlist(predict(M, type="response", newdata=dfnsp)))
    pnsm <- as.numeric(unlist(predict(M, type="response", newdata=dfnsm)))
    
    # professors 
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    #dfprof$prof2p <- factor(dfprof$prof2p, levels=levels(df$prof2p))
    #dfnoprof$prof2p <- factor(dfnoprof$prof2p, levels=levels(df$prof2p))
  
    prof <- as.numeric(unlist(predict(M, type="response", newdata=dfprof)))
    noprof <- as.numeric(unlist(predict(M, type="response", newdata=dfnoprof)))
    

# marginal effects

AME_gender <- mean(pw - pm, na.rm=TRUE)
    
AME_genderext <- mean((pwp - pmp) - (pwm - pmm), na.rm=TRUE)

AME_ext <- mean(ptp-ptm, na.rm=TRUE)

AME_cohort <- mean((pcohp-pcohm) / (2*s), na.rm=TRUE)

AME_cumulpubs <- mean((pcp - pcm) / (2*s), na.rm=TRUE)

AME_prevpubs <- mean((ppp - ppm) / (2*s), na.rm=TRUE)

AME_netsize <- mean((pnsp-pnsm) / (2*s), na.rm=TRUE)

AME_prof <- mean(prof - noprof, na.rm=TRUE)

  })
  
  c(AME_gender, AME_ext, AME_genderext, AME_cohort, AME_cumulpubs, AME_prevpubs,  AME_netsize, AME_prof)
   #save results
  
}

b4 <- boot(veni_ppf, bootFunc, R = 999, parallel="snow", ncpus=10)


fsave(b4, file = "boot3b.rda", location = "./results/")


```



```{r, echo=FALSE}

load("./results/20240319boot3b.rda")
b4 <- x
rm(x)

```

```{r}

original <- b4$t0
bias <- colMeans(b4$t) - b4$t0
se <- apply(b4$t, 2, sd)

boot.df4 <- data.frame(original=original, bias=bias, se=se)
row.names(boot.df4) <- c("AME_gender", "AME_ext", "AME_genderext", "AME_cohort", "AME_cumulpubs", "AME_prevpubs", "AME_netsize", "AME_prof")

boot.df4$t <- (boot.df4$original / boot.df4$se)

round(boot.df4, 5)

```

## M5

```{r,eval=FALSE}

start_time <- Sys.time()

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  suppressWarnings({
  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    #calculate the predicted probabilities for gender
    pw <- as.numeric(unlist(predict(M, type="response", newdata=dfwomen)))
    pm <- as.numeric(unlist(predict(M, type="response", newdata=dfmen)))
    
   # extension interactions
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    
    pwp <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene1)))
    pwm <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene0)))
    pmp <- as.numeric(unlist(predict(M, type="response", newdata=dfmene1)))
    pmm <- as.numeric(unlist(predict(M, type="response", newdata=dfmene0)))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    ptp <- as.numeric(unlist(predict(M, type="response", newdata=dfext1)))
    ptm <- as.numeric(unlist(predict(M, type="response", newdata=dfext0)))

    
    # cohort main effect
    s <- 1
    dfcohp <- dfcohm <- df
    dfcohp$phd_year <- df$phd_year + s
    dfcohm$phd_year <- df$phd_year - s
    
    pcohp <- as.numeric(unlist(predict(M, type="response", newdata=dfcohp)))
    pcohm <- as.numeric(unlist(predict(M, type="response", newdata=dfcohm)))
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    pcp <- as.numeric(unlist(predict(M, type="response", newdata=dfpcp)))
    pcm <- as.numeric(unlist(predict(M, type="response", newdata=dfpcm)))
    
    
    # pubs previous year
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    ppp <- as.numeric(unlist(predict(M, type="response", newdata=dfppp)))
    ppm <- as.numeric(unlist(predict(M, type="response", newdata=dfppm)))
    
    
    # network size
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    pnsp <- as.numeric(unlist(predict(M, type="response", newdata=dfnsp)))
    pnsm <- as.numeric(unlist(predict(M, type="response", newdata=dfnsm)))
    
    # professors 
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    #dfprof$prof2p <- factor(dfprof$prof2p, levels=levels(df$prof2p))
    #dfnoprof$prof2p <- factor(dfnoprof$prof2p, levels=levels(df$prof2p))
  
    prof <- as.numeric(unlist(predict(M, type="response", newdata=dfprof)))
    noprof <- as.numeric(unlist(predict(M, type="response", newdata=dfnoprof)))
    
    # women supervisors
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
  
    ws <- as.numeric(unlist(predict(M, type="response", newdata=dfws)))
    ms <- as.numeric(unlist(predict(M, type="response", newdata=dfms)))
    
    
# marginal effects

AME_gender <- mean(pw - pm, na.rm=TRUE)
    
AME_genderext <- mean((pwp - pmp) - (pwm - pmm), na.rm=TRUE)

AME_ext <- mean(ptp-ptm, na.rm=TRUE)

AME_cohort <- mean((pcohp-pcohm) / (2*s), na.rm=TRUE)

AME_cumulpubs <- mean((pcp - pcm) / (2*s), na.rm=TRUE)

AME_prevpubs <- mean((ppp - ppm) / (2*s), na.rm=TRUE)
    
AME_netsize <- mean((pnsp-pnsm) / (2*s), na.rm=TRUE)

AME_prof <- mean(prof - noprof, na.rm=TRUE)

AME_womsv <- mean(ws - ms, na.rm=TRUE)

  })
  
  c(AME_gender, AME_ext, AME_genderext, AME_cohort, AME_cumulpubs, AME_prevpubs, AME_netsize, AME_prof, AME_womsv)
   #save results
  
}

b5 <- boot(veni_ppf, bootFunc, R = 1000, parallel="snow", ncpus=10)


fsave(b5, file = "boot3c.rda", location = "./results/")


end_time <- Sys.time()



end_time - start_time 

```



```{r, echo=FALSE}

load("./results/20240319boot3c.rda")
b5 <- x
rm(x)

```

```{r}

original <- b5$t0
bias <- colMeans(b5$t) - b5$t0
se <- apply(b5$t, 2, sd)

boot.df5 <- data.frame(original=original, bias=bias, se=se)
row.names(boot.df5) <- c("AME_gender", "AME_ext", "AME_genderext", "AME_cohort", "AME_cumulpubs", "AME_prevpubs", "AME_netsize", "AME_prof", "AME_womsv")

boot.df5$t <- (boot.df5$original / boot.df5$se)

round(boot.df5, 5)

```

## M6

```{r,eval=FALSE}

start_time <- Sys.time()

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  suppressWarnings({
  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    #calculate the predicted probabilities for gender
    pw <- as.numeric(unlist(predict(M, type="response", newdata=dfwomen)))
    pm <- as.numeric(unlist(predict(M, type="response", newdata=dfmen)))
    
    # extension interactions
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    
    pwp <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene1)))
    pwm <- as.numeric(unlist(predict(M, type="response", newdata=dfwomene0)))
    pmp <- as.numeric(unlist(predict(M, type="response", newdata=dfmene1)))
    pmm <- as.numeric(unlist(predict(M, type="response", newdata=dfmene0)))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    ptp <- as.numeric(unlist(predict(M, type="response", newdata=dfext1)))
    ptm <- as.numeric(unlist(predict(M, type="response", newdata=dfext0)))

    
    # cohort main effect
    s <- 1
    dfcohp <- dfcohm <- df
    dfcohp$phd_year <- df$phd_year + s
    dfcohm$phd_year <- df$phd_year - s
    
    pcohp <- as.numeric(unlist(predict(M, type="response", newdata=dfcohp)))
    pcohm <- as.numeric(unlist(predict(M, type="response", newdata=dfcohm)))
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    pcp <- as.numeric(unlist(predict(M, type="response", newdata=dfpcp)))
    pcm <- as.numeric(unlist(predict(M, type="response", newdata=dfpcm)))
    
    
    # pubs previous year
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    ppp <- as.numeric(unlist(predict(M, type="response", newdata=dfppp)))
    ppm <- as.numeric(unlist(predict(M, type="response", newdata=dfppm)))
    
    
    # network size
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    pnsp <- as.numeric(unlist(predict(M, type="response", newdata=dfnsp)))
    pnsm <- as.numeric(unlist(predict(M, type="response", newdata=dfnsm)))
    
    # professors 
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    #dfprof$prof2p <- factor(dfprof$prof2p, levels=levels(df$prof2p))
    #dfnoprof$prof2p <- factor(dfnoprof$prof2p, levels=levels(df$prof2p))
  
    prof <- as.numeric(unlist(predict(M, type="response", newdata=dfprof)))
    noprof <- as.numeric(unlist(predict(M, type="response", newdata=dfnoprof)))
    
    # women supervisors
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
  
    ws <- as.numeric(unlist(predict(M, type="response", newdata=dfws)))
    ms <- as.numeric(unlist(predict(M, type="response", newdata=dfms)))
    
    
    # women supervisors * gender_2
    dfwnows <- dfwws <- dfmnows <- dfmws <- df

    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    
    
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
    womnows <- as.numeric(unlist(predict(M, type="response", newdata=dfwnows)))
    womws <- as.numeric(unlist(predict(M, type="response", newdata=dfwws)))
    mennows <- as.numeric(unlist(predict(M, type="response", newdata=dfmnows)))
    menws <- as.numeric(unlist(predict(M, type="response", newdata=dfmws)))
    
    

# marginal effects

AME_gender <- mean(pw - pm, na.rm=TRUE)
    
AME_genderext <- mean((pwp - pmp) - (pwm - pmm), na.rm=TRUE)

AME_ext <- mean(ptp-ptm, na.rm=TRUE)

AME_cohort <- mean((pcohp-pcohm) / (2*s), na.rm=TRUE)

AME_cumulpubs <- mean((pcp - pcm) / (2*s), na.rm=TRUE)

AME_prevpubs <- mean((ppp - ppm) / (2*s), na.rm=TRUE)
    
AME_netsize <- mean((pnsp-pnsm) / (2*s), na.rm=TRUE)

AME_prof <- mean(prof - noprof, na.rm=TRUE)

AME_womsv <- mean(ws - ms, na.rm=TRUE)

AME_genderwomsv <- mean((womws - menws) - (womnows - mennows), na.rm=TRUE)


  })
  
  c(AME_gender, AME_ext, AME_genderext, AME_cohort, AME_cumulpubs, AME_prevpubs, AME_netsize, AME_prof, AME_womsv, AME_genderwomsv)
   #save results
  
}

b6 <- boot(veni_ppf, bootFunc, R = 1000, parallel="snow", ncpus=10)


fsave(b6, file = "boot4.rda", location = "./results/")


end_time <- Sys.time()



end_time - start_time 

```


```{r, echo=FALSE}

load("./results/20240527boot4.rda")
b6 <- x
rm(x)

```


```{r}

original <- b6$t0
bias <- colMeans(b6$t) - b6$t0
se <- apply(b6$t, 2, sd)

boot.df6 <- data.frame(original=original, bias=bias, se=se)
row.names(boot.df6) <- c("AME_gender", "AME_ext", "AME_genderext", "AME_cohort", "AME_cumulpubs", "AME_prevpubs", "AME_netsize", "AME_prof", "AME_womsv", "AME_genderwomsv")

boot.df6$t <- (boot.df6$original / boot.df6$se)

round(boot.df6, 5)

```




# Mediation analyses

```{r,eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2


bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)

  
  M2 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"), data = df)
  
  M3 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"), data = df)
  
  M4_size <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize,
          family = binomial(link="cloglog"), data = df)
  
  M4_prof <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M5 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)

  M6 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)

    suppressWarnings({
  
    # CREATING THE DATASETS
    s <- 1
      
    #gender
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))  
    

      
    # MODEL 1  
    
    #calculate the predicted probabilities for gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    
    # MODEL 2
    
    #calculate the predicted probabilities for gender
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
  
    # MODEL 3
    
    #calculate the predicted probabilities for gender
    pw3 <- as.numeric(unlist(predict(M3, type="response", newdata=dfwomen)))
    pm3 <- as.numeric(unlist(predict(M3, type="response", newdata=dfmen)))
    # average marginal effects
    AME_gender_m3 <- mean(pw3 - pm3, na.rm=TRUE)
    
    
    
    # MODEL 4
    
    ### ONLY SIZE
    #calculate the predicted probabilities for gender
    pw4_size <- as.numeric(unlist(predict(M4_size, type="response", newdata=dfwomen)))
    pm4_size <- as.numeric(unlist(predict(M4_size, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4_size <- mean(pw4_size - pm4_size, na.rm=TRUE)
    
  
    
    ### ONLY PROF
    #calculate the predicted probabilities for gender
    pw4_prof <- as.numeric(unlist(predict(M4_prof, type="response", newdata=dfwomen)))
    pm4_prof <- as.numeric(unlist(predict(M4_prof, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4_prof <- mean(pw4_prof - pm4_prof, na.rm=TRUE)
    
    
    
    ### BOTH SIZE + PROF
    
    #calculate the predicted probabilities for gender
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    
    
    # MODEL 5
    
    #calculate the predicted probabilities for gender
    pw5 <- as.numeric(unlist(predict(M5, type="response", newdata=dfwomen)))
    pm5 <- as.numeric(unlist(predict(M5, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m5 <- mean(pw5 - pm5, na.rm=TRUE)
    
    
    # MODEL 6
    
    #calculate the predicted probabilities for gender
    pw6 <- as.numeric(unlist(predict(M6, type="response", newdata=dfwomen)))
    pm6 <- as.numeric(unlist(predict(M6, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender_m6 <- mean(pw6 - pm6, na.rm=TRUE)
    
  
    
    # MEDIATION
    AME_gender_d4size <- mean((pw4_size - pm4_size) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d4prof <- mean((pw4_prof - pm4_prof) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d12 <- mean((pw2 - pm2) - (pw1 - pm1), na.rm=TRUE)
    
    AME_gender_d23 <- mean((pw3 - pm3) - (pw2 - pm2), na.rm=TRUE)
    
    AME_gender_d34 <- mean((pw4 - pm4) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d45 <- mean((pw5 - pm5) - (pw4 - pm4), na.rm=TRUE)

    AME_gender_d56 <- mean((pw6 - pm6) - (pw5 - pm5), na.rm=TRUE)

    
      })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3, AME_gender_m4_size, AME_gender_m4_prof, AME_gender_m4, AME_gender_m5, AME_gender_m6, AME_gender_d12, AME_gender_d23, AME_gender_d4size, AME_gender_d4prof, AME_gender_d34, AME_gender_d45, AME_gender_d56)
   #save results
}

mediations <- boot(data=veni_ppf, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(mediations, file = "mediations.rda", location = "./results/")


```


```{r, echo=FALSE}

load("./results/20240319mediations.rda")
mediations <- x
rm(x)

```


```{r}

original <- mediations$t0
bias <- colMeans(mediations$t) - mediations$t0
se <- apply(mediations$t, 2, sd)

boot.dfmed <- data.frame(original=original, bias=bias, se=se)
row.names(boot.dfmed) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3", "AME_gender_m4_size", "AME_gender_m4_prof", "AME_gender_m4", "AME_gender_m5", "AME_gender_m6", "AME_gender_d12", "AME_gender_d23", "AME_gender_d4size", "AME_gender_d4prof", "AME_gender_d34", "AME_gender_d45", "AME_gender_d56")

boot.dfmed$t <- (boot.dfmed$original / boot.dfmed$se)

round(boot.dfmed, 5)

```




