---
title: "Mentoring for gender equality in early-career grant receipt: main analyses"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---

This lab journal details the analyses performed to test our hypotheses.  
  
----

# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}



fsave <- function(x, file, location="./data/processed/") {
  datename <- substr(gsub("[:-]", "", Sys.time()), 1,8)  
  totalname <- paste(location, datename, file, sep="")
  save(x, file = totalname)  
}



```

---  

# Packages



```{r, results='hide'}

packages = c("tidyverse", "stringr", "stringi", "boot", "kableExtra")

fpackage.check(packages)


```

--- 


# Input

We use one processed dataset

* [veni_ppf](https://github.com/ammulders/amatteroftime/data/processed/veni_ppf.rda): person-period file used for analyses of Veni receipt
    - name of dataset: `veni_ppf` 



```{r files, eval=TRUE}

load(file = "data/processed/veni_ppf.rda")

load(file = "data/processed/veni_ppf_c1.rda")
load(file = "data/processed/veni_ppf_c2.rda")
load(file = "data/processed/veni_ppf_c3.rda")

```

  
---  


# Descriptive: gender differences in supervision team composition

```{r}

veni_ppf %>%
  distinct(id, .keep_all = TRUE) -> ind_level_data



ind_level_data %>%
  mutate(wom_sv = as.numeric(wom_sv1),
         wom_sv = wom_sv - 1) %>% # transform the 1/2 coding into 0/1 coding
  group_by(gender_2) %>%
  summarise(teamsize_m = mean(teamsize),
            teamsize_sd = sd(teamsize),
            profs_m = mean(prof2p),
            npubs_sv_m = mean(npubs_sv_norm),
            npubs_sv_sd = sd(npubs_sv_norm),
            wom_sv_m = mean(wom_sv)) -> svbygender




t.test(teamsize ~ gender_2, data=ind_level_data)
t.test(npubs_sv ~ gender_2, data=ind_level_data)

chisq.test(table(ind_level_data$gender_2, ind_level_data$prof2p))
chisq.test(table(ind_level_data$gender_2, ind_level_data$wom_sv1))

```



# Analyses

```{r}

summary(veni_ppf$gender_2, useNA="always")

veni_ppf %>%
  filter(year>2002) %>%
  group_by(time, gender_2) %>%
  summarise(event = sum(veni),
            total = n()) %>%
  mutate(hazard = event/total) %>%
  ggplot(aes(x=time, y = log(-log(1-hazard)), group = gender_2, color=gender_2)) +
  geom_point() +
  geom_smooth()

veni_ppf %>%
  filter(year>2002) %>%
  group_by(time, gender_2) %>%
  summarise(event = sum(veni),
            total = n()) %>%
  mutate(hazard = event/total) %>%
  ggplot(aes(x=time, y = hazard, group = gender_2, color=gender_2)) +
  geom_point() +
  geom_smooth(se=FALSE) +
  scale_y_continuous(limits=c(0, 0.04))


```


# Veni against time

```{r}


test1 <- glm(veni ~ time, family = binomial(link = "cloglog"), data = veni_ppf) # linear

test2 <- glm(veni ~ as.factor(time), family = binomial(link = "cloglog"), data = veni_ppf) # factor


AIC(test1, test2)



```



# M1: Only gender and time

```{r}


#veni_ppf[veni_ppf$uni!="WUR",] -> veni_ppf
#veni_ppf[veni_ppf$uni!="EUR",]-> veni_ppf

M1 <- glm(formula = veni ~ as.factor(time) + as.factor(gender_2),
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M1)


```



# M2: gender * time

```{r}


M2 <- glm(formula = veni ~ as.factor(time) + as.factor(gender_2) * phd_year,
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M2)


```




# M3: addition all control variables

```{r}

M3 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M3)

length(M3$coefficients) # df 25 

```


# M4: mediation teamsize and number of professors

```{r}


M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M4)


length(M4$coefficients)


```




# M5: all mediations

```{r}

M5 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1),
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M5)


length(M5$coefficients)


```





# M6 (supervision team * gender)

```{r}

M6 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2),
          family = binomial(link="cloglog"),
          data = veni_ppf)


summary(M6)

```





# Average marginal effects (AMEs)

## All models

```{r, eval=FALSE}


# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) * phd_year + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- .1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    time_levels <- levels(as.factor(df$time))
    ref_time <- "0"

    # cohort * gender datasets
    dfwcp <- dfwcm <- dfmcp <- dfmcm <- df
    dfwcp$gender_2 <- dfwcm$gender_2 <- "women"
    dfmcp$gender_2 <- dfmcm$gender_2 <- "men"
    
    dfwcp$gender_2 <- factor(dfwcp$gender_2, levels=levels(df$gender_2))
    dfwcm$gender_2 <- factor(dfwcm$gender_2, levels=levels(df$gender_2))
    dfmcp$gender_2 <- factor(dfmcp$gender_2, levels=levels(df$gender_2))
    dfmcm$gender_2 <- factor(dfmcm$gender_2, levels=levels(df$gender_2))
    
    dfwcp$phd_year <- dfmcp$phd_year <- df$phd_year + s
    dfwcm$phd_year <- dfmcm$phd_year <- df$phd_year - s
    
    # cohort datasets
    dfcp <- dfcm <- df
    dfcp$phd_year <- df$phd_year + s
    dfcm$phd_year <- df$phd_year - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    AME_time_m1 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m1 <- predict(M1, newdata=df_l, type="response")
     pt0m1 <- predict(M1, newdata=df_ref, type="response")
     
     AME_time_m1[level] <- mean(pt1m1 - pt0m1, na.rm=TRUE)
     
    }
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # cohort
    pcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcp)))
    pcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcm)))
    AME_cohort_m2 <- mean(pcp2 - pcm2, na.rm=TRUE)

    # gender * cohort
    pwcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcp)))
    pwcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcm)))
    pmcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcp)))
    pmcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcm)))
    AME_gendercohort_m2 <- mean(((pwcp2 - pmcp2) - (pwcm2 - pmcm2)) / (2*s), na.rm=TRUE)
    
    # time
    AME_time_m2 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m2 <- predict(M2, newdata=df_l, type="response")
     pt0m2 <- predict(M2, newdata=df_ref, type="response")
     
     AME_time_m2[level] <- mean(pt1m2 - pt0m2, na.rm=TRUE)
     
   }
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
   # cohort
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcm)))
    AME_cohort_m3a <- mean(pcp3a - pcm3a, na.rm=TRUE)

    # gender * cohort
    pwcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcp)))
    pwcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcm)))
    pmcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcp)))
    pmcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcm)))
    AME_gendercohort_m3a <- mean(((pwcp3a - pmcp3a) - (pwcm3a - pmcm3a)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3a <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3a <- predict(M3a, newdata=df_l, type="response")
     pt0m3a <- predict(M3a, newdata=df_ref, type="response")
     
     AME_time_m3a[level] <- mean(pt1m3a - pt0m3a, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # cohort
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcm)))
    AME_cohort_m3b <- mean(pcp3b - pcm3b, na.rm=TRUE)

    # gender * cohort
    pwcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcp)))
    pwcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcm)))
    pmcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcp)))
    pmcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcm)))
    AME_gendercohort_m3b <- mean(((pwcp3b - pmcp3b) - (pwcm3b - pmcm3b)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3b <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3b <- predict(M3b, newdata=df_l, type="response")
     pt0m3b <- predict(M3b, newdata=df_ref, type="response")
     
     AME_time_m3b[level] <- mean(pt1m3b - pt0m3b, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # cohort
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcm)))
    AME_cohort_m3c <- mean(pcp3c - pcm3c, na.rm=TRUE)
    
    # gender * cohort
    pwcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcp)))
    pwcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcm)))
    pmcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcp)))
    pmcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcm)))
    AME_gendercohort_m3c <- mean(((pwcp3c - pmcp3c) - (pwcm3c - pmcm3c)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3c <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3c <- predict(M3c, newdata=df_l, type="response")
     pt0m3c <- predict(M3c, newdata=df_ref, type="response")
     
     AME_time_m3c[level] <- mean(pt1m3c - pt0m3c, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # cohort
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcm)))
    AME_cohort_m4 <- mean(pcp4 - pcm4, na.rm=TRUE)
    
    # gender * cohort
    pwcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcp)))
    pwcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcm)))
    pmcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcp)))
    pmcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcm)))
    AME_gendercohort_m4 <- mean(((pwcp4 - pmcp4) - (pwcm4 - pmcm4)) / (2*s), na.rm=TRUE)
    
    # time
    AME_time_m4 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m4 <- predict(M4, newdata=df_l, type="response")
     pt0m4 <- predict(M4, newdata=df_ref, type="response")
     
     AME_time_m4[level] <- mean(pt1m4 - pt0m4, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_cohort_m2, AME_cohort_m3a, AME_cohort_m3b, AME_cohort_m3c, AME_cohort_m4, AME_gendercohort_m2, AME_gendercohort_m3a, AME_gendercohort_m3b, AME_gendercohort_m3c, AME_gendercohort_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_ame.rda", location = "./results/cont_cohort/")


```

```{r, echo=FALSE}

load("./results/cont_cohort/20250605_ame.rda")
AMEs <- x
rm(x)

```


```{r}

original <- AMEs$t0
bias <- colMeans(AMEs$t) - AMEs$t0
se <- apply(AMEs$t, 2, sd)

df.ames <- data.frame(original=original, bias=bias, se=se)
row.names(df.ames) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1_0", "AME_time_m1_1", "AME_time_m1_2", "AME_time_m1_3", "AME_time_m1_4", "AME_time_m1_5", "AME_time_m1_6", "AME_time_m1_7", "AME_time_m1_8", "AME_time_m2_0", "AME_time_m2_1", "AME_time_m2_2", "AME_time_m2_3", "AME_time_m2_4", "AME_time_m2_5", "AME_time_m2_6", "AME_time_m2_7", "AME_time_m2_8", "AME_time_m3a_0", "AME_time_m3a_1", "AME_time_m3a_2", "AME_time_m3a_3", "AME_time_m3a_4", "AME_time_m3a_5", "AME_time_m3a_6", "AME_time_m3a_7", "AME_time_m3a_8", "AME_time_m3b_0", "AME_time_m3b_1", "AME_time_m3b_2", "AME_time_m3b_3", "AME_time_m3b_4", "AME_time_m3b_5", "AME_time_m3b_6", "AME_time_m3b_7", "AME_time_m3b_8", "AME_time_m3c_0", "AME_time_m3c_1", "AME_time_m3c_2", "AME_time_m3c_3", "AME_time_m3c_4", "AME_time_m3c_5", "AME_time_m3c_6", "AME_time_m3c_7", "AME_time_m3c_8", "AME_time_m4_0", "AME_time_m4_1", "AME_time_m4_2", "AME_time_m4_3", "AME_time_m4_4", "AME_time_m4_5", "AME_time_m4_6", "AME_time_m4_7", "AME_time_m4_8",  "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.ames$t <- (df.ames$original / df.ames$se)


# remove the time=0 rows, as 0 is the reference category for time
rows_to_remove <- grep("^AME_time_m(1|2|3a|3b|3c|4)_0$", rownames(df.ames))
df.ames <- df.ames[-rows_to_remove, ]

round(df.ames, 5)

```

# dfs

```{r}

length(M1$coefficients)
length(M2$coefficients)
length(M3$coefficients)
length(M4$coefficients)
length(M5$coefficients)
length(M6$coefficients)


```



# Table "Results main analyses"

```{r}

# Creating neat labels
table_ames <- df.ames %>%
  mutate(term = rownames(df.ames),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m[1-4][abc]?")) %>%
  mutate(model = recode(model,
                        "m1" = "M1",
                        "m2" = "M2",
                        "m3a" = "M3",
                        "m3b" = "M4",
                        "m3c" = "M5",
                        "m4" = "M6"),
         model = factor(model, levels = paste0("M", 1:6))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "genderwomsv") ~ "Women supervisors * Woman",
    str_detect(term, "gender") ~ "Woman",
    str_detect(term, "time") ~ paste0("Time since PhD: ", str_extract(term, "[:digit:]$"), " years"),
    str_detect(term, "cohort") ~ "PhD cohort",
    str_detect(term, "womsv") ~ "Women supervisors",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "netsize") ~ "Team size",
    str_detect(term, "prof") ~ "2+ professors",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)", original, se)) %>%
  select(label, model, value)

# correct table ordering
rows_tab <- c("Woman", "Time since PhD: 1 years", "Time since PhD: 2 years", "Time since PhD: 3 years", "Time since PhD: 4 years", "Time since PhD: 5 years", "Time since PhD: 6 years", "Time since PhD: 7 years", "Time since PhD: 8 years", "PhD cohort", "PhD cohort * Woman", "Cumulative publications", "Previous publications", "Team size", "2+ professors", "Supervisors' productivity", "Women supervisors", "Women supervisors * Woman")


# Reshape to wide format
table_df <- table_ames %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab)) %>%
  arrange(label)

# Replace NA values (not in the model) with empty strings
table_df[is.na(table_df)] <- ""

# Create pretty table
kable(table_df, "html", escape = FALSE, align = "lcccccc",
      col.names = c("", paste0("M", 1:6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt" = 6))


```




# Mediation analyses

```{r,eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2


bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  
  
    M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) * phd_year + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
    M4_size <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize, family = binomial(link="cloglog"), data = df)
    
    M4_prof <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + as.factor(prof2p), family = binomial(link="cloglog"), data = df)
        
    M4_pubs <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)

  
  M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M5 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M6 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)


    suppressWarnings({
  
    # CREATING THE DATASETS

    #gender
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))  
    

      
    # MODEL 1  
    
    #calculate the predicted probabilities for gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    
    # MODEL 2
    
    #calculate the predicted probabilities for gender
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
  
    # MODEL 3
    
    #calculate the predicted probabilities for gender
    pw3 <- as.numeric(unlist(predict(M3, type="response", newdata=dfwomen)))
    pm3 <- as.numeric(unlist(predict(M3, type="response", newdata=dfmen)))
    # average marginal effects
    AME_gender_m3 <- mean(pw3 - pm3, na.rm=TRUE)
    
    
    
    # MODEL 4
    
    ### ONLY SIZE
    #calculate the predicted probabilities for gender
    pw4_size <- as.numeric(unlist(predict(M4_size, type="response", newdata=dfwomen)))
    pm4_size <- as.numeric(unlist(predict(M4_size, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4_size <- mean(pw4_size - pm4_size, na.rm=TRUE)
    
  
    
    ### ONLY PROF
    #calculate the predicted probabilities for gender
    pw4_prof <- as.numeric(unlist(predict(M4_prof, type="response", newdata=dfwomen)))
    pm4_prof <- as.numeric(unlist(predict(M4_prof, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4_prof <- mean(pw4_prof - pm4_prof, na.rm=TRUE)
    
    
    ### ONLY PUBS
    #calculate the predicted probabilities for gender
    pw4_pubs <- as.numeric(unlist(predict(M4_pubs, type="response", newdata=dfwomen)))
    pm4_pubs <- as.numeric(unlist(predict(M4_pubs, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4_pubs <- mean(pw4_pubs - pm4_pubs, na.rm=TRUE)
    
    
    ### FULL MODEL 4
    
    #calculate the predicted probabilities for gender
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    
    # MODEL 5
    
    #calculate the predicted probabilities for gender
    pw5 <- as.numeric(unlist(predict(M5, type="response", newdata=dfwomen)))
    pm5 <- as.numeric(unlist(predict(M5, type="response", newdata=dfmen)))
   
    # average marginal effects
    AME_gender_m5 <- mean(pw5 - pm5, na.rm=TRUE)
    
    
    # MODEL 6
    
    #calculate the predicted probabilities for gender
    pw6 <- as.numeric(unlist(predict(M6, type="response", newdata=dfwomen)))
    pm6 <- as.numeric(unlist(predict(M6, type="response", newdata=dfmen)))
    
    # average marginal effects
    AME_gender_m6 <- mean(pw6 - pm6, na.rm=TRUE)
    
  
    
    # MEDIATION
    AME_gender_d4size <- mean((pw4_size - pm4_size) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d4prof <- mean((pw4_prof - pm4_prof) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d4pubs <- mean((pw4_pubs - pm4_pubs) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d12 <- mean((pw2 - pm2) - (pw1 - pm1), na.rm=TRUE)
    
    AME_gender_d23 <- mean((pw3 - pm3) - (pw2 - pm2), na.rm=TRUE)
    
    AME_gender_d34 <- mean((pw4 - pm4) - (pw3 - pm3), na.rm=TRUE)
    
    AME_gender_d45 <- mean((pw5 - pm5) - (pw4 - pm4), na.rm=TRUE)

    AME_gender_d56 <- mean((pw6 - pm6) - (pw5 - pm5), na.rm=TRUE)

    
      })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3, AME_gender_m4_size, AME_gender_m4_prof, AME_gender_m4_pubs, AME_gender_m4, AME_gender_m5, AME_gender_m6, AME_gender_d12, AME_gender_d23, AME_gender_d4size, AME_gender_d4prof, AME_gender_d4pubs, AME_gender_d34, AME_gender_d45, AME_gender_d56)
   #save results
}

mediations <- boot(data=veni_ppf, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(mediations, file = "mediations.rda", location = "./results/")


```


```{r, echo=FALSE}

load("./results/20250609mediations.rda")
mediations <- x
rm(x)

```


```{r}

original <- mediations$t0
bias <- colMeans(mediations$t) - mediations$t0
se <- apply(mediations$t, 2, sd)

boot.dfmed <- data.frame(original=original, bias=bias, se=se)
row.names(boot.dfmed) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3", "AME_gender_m4_size", "AME_gender_m4_prof", "AME_gender_m4_pubs", "AME_gender_m4", "AME_gender_m5", "AME_gender_m6", "AME_gender_d12", "AME_gender_d23", "AME_gender_d4size", "AME_gender_d4prof", "AME_gender_d4pubs", "AME_gender_d34", "AME_gender_d45", "AME_gender_d56")

boot.dfmed$t <- (boot.dfmed$original / boot.dfmed$se)

round(boot.dfmed, 5)

```





# Post-hoc analyses (by cohort group)


## Cohort group 1 (1997-2006)
```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- .1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    time_levels <- levels(as.factor(df$time))
    ref_time <- "0"
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    AME_time_m1 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m1 <- predict(M1, newdata=df_l, type="response")
     pt0m1 <- predict(M1, newdata=df_ref, type="response")
     
     AME_time_m1[level] <- mean(pt1m1 - pt0m1, na.rm=TRUE)
     
    }
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # time
    AME_time_m2 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m2 <- predict(M2, newdata=df_l, type="response")
     pt0m2 <- predict(M2, newdata=df_ref, type="response")
     
     AME_time_m2[level] <- mean(pt1m2 - pt0m2, na.rm=TRUE)
     
   }
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
     # time
    AME_time_m3a <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3a <- predict(M3a, newdata=df_l, type="response")
     pt0m3a <- predict(M3a, newdata=df_ref, type="response")
     
     AME_time_m3a[level] <- mean(pt1m3a - pt0m3a, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # time
    AME_time_m3b <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3b <- predict(M3b, newdata=df_l, type="response")
     pt0m3b <- predict(M3b, newdata=df_ref, type="response")
     
     AME_time_m3b[level] <- mean(pt1m3b - pt0m3b, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # time
    AME_time_m3c <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3c <- predict(M3c, newdata=df_l, type="response")
     pt0m3c <- predict(M3c, newdata=df_ref, type="response")
     
     AME_time_m3c[level] <- mean(pt1m3c - pt0m3c, na.rm=TRUE)
     
   }
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # time
    AME_time_m4 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m4 <- predict(M4, newdata=df_l, type="response")
     pt0m4 <- predict(M4, newdata=df_ref, type="response")
     
     AME_time_m4[level] <- mean(pt1m4 - pt0m4, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_c1, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_c1.rda", location = "./results/robustness/bycohort/")


```


```{r, echo=FALSE}

load("./results/robustness/bycohort/20250609_c1.rda")
cohort1 <- x
rm(x)

```


```{r}

original <- cohort1$t0
bias <- colMeans(cohort1$t) - cohort1$t0
se <- apply(cohort1$t, 2, sd)

df.coh1 <- data.frame(original=original, bias=bias, se=se)
row.names(df.coh1) <- c(c('AME_gender_m1', 'AME_gender_m2', 'AME_gender_m3a', 'AME_gender_m3b', 'AME_gender_m3c', 'AME_gender_m4', "AME_time_m1_0", "AME_time_m1_1", "AME_time_m1_2", "AME_time_m1_3", "AME_time_m1_4", "AME_time_m1_5", "AME_time_m1_6", "AME_time_m1_7", "AME_time_m1_8", "AME_time_m2_0", "AME_time_m2_1", "AME_time_m2_2", "AME_time_m2_3", "AME_time_m2_4", "AME_time_m2_5", "AME_time_m2_6", "AME_time_m2_7", "AME_time_m2_8", "AME_time_m3a_0", "AME_time_m3a_1", "AME_time_m3a_2", "AME_time_m3a_3", "AME_time_m3a_4", "AME_time_m3a_5", "AME_time_m3a_6", "AME_time_m3a_7", "AME_time_m3a_8", "AME_time_m3b_0", "AME_time_m3b_1", "AME_time_m3b_2", "AME_time_m3b_3", "AME_time_m3b_4", "AME_time_m3b_5", "AME_time_m3b_6", "AME_time_m3b_7", "AME_time_m3b_8", "AME_time_m3c_0", "AME_time_m3c_1", "AME_time_m3c_2", "AME_time_m3c_3", "AME_time_m3c_4", "AME_time_m3c_5", "AME_time_m3c_6", "AME_time_m3c_7", "AME_time_m3c_8", "AME_time_m4_0", "AME_time_m4_1", "AME_time_m4_2", "AME_time_m4_3", "AME_time_m4_4", "AME_time_m4_5", "AME_time_m4_6", "AME_time_m4_7", "AME_time_m4_8", 'AME_cpubs_m3a', 'AME_cpubs_m3b', 'AME_cpubs_m3c', 'AME_cpubs_m4', 'AME_ppubs_m3a', 'AME_ppubs_m3b', 'AME_ppubs_m3c', 'AME_ppubs_m4', 'AME_netsize_m3b', 'AME_netsize_m3c', 'AME_netsize_m4', 'AME_prof_m3b', 'AME_prof_m3c', 'AME_prof_m4', 'AME_svpubs_m3b', 'AME_svpubs_m3c', 'AME_svpubs_m4', 'AME_womsv_m3c', 'AME_womsv_m4', 'AME_genderwomsv_m4'))

df.coh1$t <- (df.coh1$original / df.coh1$se)

# remove the time=0 rows, as 0 is the reference category for time
rows_to_remove <- grep("^AME_time_m(1|2|3a|3b|3c|4)_0$", rownames(df.coh1))
df.coh1 <- df.coh1[-rows_to_remove, ]

round(df.coh1, 5)

```




## Cohort group 2 (2007-2014)

Adding a variable: after 2015. To measure whether chances of obtaining a Veni are actually larger for this group in the years after the extension policy was introduced. 

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)

  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- .1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    time_levels <- levels(as.factor(df$time))
    ref_time <- "0"
    
    # 2015+ datasets
    dfp151 <- dfp150 <- df
    dfp151$p2015 <- 1
    dfp150$p2015 <- 0
    
    # 2015+ * gender datasets
    dfwomenp151 <- dfwomenp150 <- dfmenp151 <- dfmenp150 <- df
    
    dfwomenp151$gender_2 <- dfwomenp150$gender_2 <- "women"
    dfmenp151$gender_2 <- dfmenp150$gender_2 <- "men"
    dfwomenp151$gender_2 <- factor(dfwomenp151$gender_2, levels=levels(df$gender_2))
    dfwomenp150$gender_2 <- factor(dfwomenp150$gender_2, levels=levels(df$gender_2))
    dfmenp151$gender_2 <- factor(dfmenp151$gender_2, levels=levels(df$gender_2))
    dfmenp150$gender_2 <- factor(dfmenp150$gender_2, levels=levels(df$gender_2))
    
    dfwomenp151$p2015 <- dfmenp151$p2015 <- 1
    dfwomenp150$p2015 <- dfmenp150$p2015 <- 0
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    AME_time_m1 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m1 <- predict(M1, newdata=df_l, type="response")
     pt0m1 <- predict(M1, newdata=df_ref, type="response")
     
     AME_time_m1[level] <- mean(pt1m1 - pt0m1, na.rm=TRUE)
     
    }
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # time
    AME_time_m2 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m2 <- predict(M2, newdata=df_l, type="response")
     pt0m2 <- predict(M2, newdata=df_ref, type="response")
     
     AME_time_m2[level] <- mean(pt1m2 - pt0m2, na.rm=TRUE)
     
   }
    
    # 2015+
    p1512 <- as.numeric(unlist(predict(M2, type="response", newdata=dfp151)))
    p1502 <- as.numeric(unlist(predict(M2, type="response", newdata=dfp150)))
    AME_2015_m2 <- mean(p1512 - p1502, na.rm=TRUE)

    # gender * 2015+
    pw1512 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomenp151)))
    pw1502 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomenp150)))
    pm1512 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmenp151)))
    pm1502 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmenp150)))
    AME_gender2015_m2 <- mean(((pw1512 - pm1512) - (pw1502 - pm1502)), na.rm=TRUE)
    
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
     # time
    AME_time_m3a <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3a <- predict(M3a, newdata=df_l, type="response")
     pt0m3a <- predict(M3a, newdata=df_ref, type="response")
     
     AME_time_m3a[level] <- mean(pt1m3a - pt0m3a, na.rm=TRUE)
     
   }
    
    # 2015+
    p1513a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfp151)))
    p1503a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfp150)))
    AME_2015_m3a <- mean(p1513a - p1503a, na.rm=TRUE)

    # gender * 2015+
    pw1513a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomenp151)))
    pw1503a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomenp150)))
    pm1513a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmenp151)))
    pm1503a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmenp150)))
    AME_gender2015_m3a <- mean(((pw1513a - pm1513a) - (pw1503a - pm1503a)), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # time
    AME_time_m3b <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3b <- predict(M3b, newdata=df_l, type="response")
     pt0m3b <- predict(M3b, newdata=df_ref, type="response")
     
     AME_time_m3b[level] <- mean(pt1m3b - pt0m3b, na.rm=TRUE)
     
   }
    
    # 2015+
    p1513b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfp151)))
    p1503b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfp150)))
    AME_2015_m3b <- mean(p1513b - p1503b, na.rm=TRUE)

    # gender * 2015+
    pw1513b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomenp151)))
    pw1503b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomenp150)))
    pm1513b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmenp151)))
    pm1503b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmenp150)))
    AME_gender2015_m3b <- mean(((pw1513b - pm1513b) - (pw1503b - pm1503b)), na.rm=TRUE)
    
    
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # time
    AME_time_m3c <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3c <- predict(M3c, newdata=df_l, type="response")
     pt0m3c <- predict(M3c, newdata=df_ref, type="response")
     
     AME_time_m3c[level] <- mean(pt1m3c - pt0m3c, na.rm=TRUE)
     
   }
    
    # 2015+
    p1513c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfp151)))
    p1503c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfp150)))
    AME_2015_m3c <- mean(p1513c - p1503c, na.rm=TRUE)

    # gender * 2015+
    pw1513c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomenp151)))
    pw1503c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomenp150)))
    pm1513c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmenp151)))
    pm1503c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmenp150)))
    AME_gender2015_m3c <- mean(((pw1513c - pm1513c) - (pw1503c - pm1503c)), na.rm=TRUE)
    
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # time
    AME_time_m4 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m4 <- predict(M4, newdata=df_l, type="response")
     pt0m4 <- predict(M4, newdata=df_ref, type="response")
     
     AME_time_m4[level] <- mean(pt1m4 - pt0m4, na.rm=TRUE)
     
   }
    
    # 2015+
    p1514 <- as.numeric(unlist(predict(M4, type="response", newdata=dfp151)))
    p1504 <- as.numeric(unlist(predict(M4, type="response", newdata=dfp150)))
    AME_2015_m4 <- mean(p1514 - p1504, na.rm=TRUE)

    # gender * 2015+
    pw1514 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomenp151)))
    pw1504 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomenp150)))
    pm1514 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmenp151)))
    pm1504 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmenp150)))
    AME_gender2015_m4 <- mean(((pw1514 - pm1514) - (pw1504 - pm1504)), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_2015_m2, AME_2015_m3a, AME_2015_m3b, AME_2015_m3c, AME_2015_m4, AME_gender2015_m2, AME_gender2015_m3a, AME_gender2015_m3b, AME_gender2015_m3c, AME_gender2015_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_c2, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_c2.rda", location = "./results/robustness/bycohort/")

```


```{r, echo=FALSE}

load("./results/robustness/bycohort/20250610_c2.rda")
cohort2 <- x
rm(x)

```


```{r}

original <- cohort2$t0
bias <- colMeans(cohort2$t) - cohort2$t0
se <- apply(cohort2$t, 2, sd)

df.coh2 <- data.frame(original=original, bias=bias, se=se)
row.names(df.coh2) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1_0", "AME_time_m1_1", "AME_time_m1_2", "AME_time_m1_3", "AME_time_m1_4", "AME_time_m1_5", "AME_time_m1_6", "AME_time_m1_7", "AME_time_m1_8", "AME_time_m2_0", "AME_time_m2_1", "AME_time_m2_2", "AME_time_m2_3", "AME_time_m2_4", "AME_time_m2_5", "AME_time_m2_6", "AME_time_m2_7", "AME_time_m2_8", "AME_time_m3a_0", "AME_time_m3a_1", "AME_time_m3a_2", "AME_time_m3a_3", "AME_time_m3a_4", "AME_time_m3a_5", "AME_time_m3a_6", "AME_time_m3a_7", "AME_time_m3a_8", "AME_time_m3b_0", "AME_time_m3b_1", "AME_time_m3b_2", "AME_time_m3b_3", "AME_time_m3b_4", "AME_time_m3b_5", "AME_time_m3b_6", "AME_time_m3b_7", "AME_time_m3b_8", "AME_time_m3c_0", "AME_time_m3c_1", "AME_time_m3c_2", "AME_time_m3c_3", "AME_time_m3c_4", "AME_time_m3c_5", "AME_time_m3c_6", "AME_time_m3c_7", "AME_time_m3c_8", "AME_time_m4_0", "AME_time_m4_1", "AME_time_m4_2", "AME_time_m4_3", "AME_time_m4_4", "AME_time_m4_5", "AME_time_m4_6", "AME_time_m4_7", "AME_time_m4_8", "AME_2015_m2", "AME_2015_m3a", "AME_2015_m3b", "AME_2015_m3c", "AME_2015_m4", "AME_gender2015_m2", "AME_gender2015_m3a", "AME_gender2015_m3b", "AME_gender2015_m3c", "AME_gender2015_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh2$t <- (df.coh2$original / df.coh2$se)

# remove the time=0 rows, as 0 is the reference category for time
rows_to_remove <- grep("^AME_time_m(1|2|3a|3b|3c|4)_0$", rownames(df.coh2))
df.coh2 <- df.coh2[-rows_to_remove, ]

round(df.coh2, 5)

```



## Cohort group 3 (2015-2019)
```{r, eval=FALSE}


# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- .1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    time_levels <- levels(as.factor(df$time))
    ref_time <- "0"
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    AME_time_m1 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m1 <- predict(M1, newdata=df_l, type="response")
     pt0m1 <- predict(M1, newdata=df_ref, type="response")
     
     AME_time_m1[level] <- mean(pt1m1 - pt0m1, na.rm=TRUE)
     
    }
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # time
    AME_time_m2 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m2 <- predict(M2, newdata=df_l, type="response")
     pt0m2 <- predict(M2, newdata=df_ref, type="response")
     
     AME_time_m2[level] <- mean(pt1m2 - pt0m2, na.rm=TRUE)
     
   }
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
     # time
    AME_time_m3a <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3a <- predict(M3a, newdata=df_l, type="response")
     pt0m3a <- predict(M3a, newdata=df_ref, type="response")
     
     AME_time_m3a[level] <- mean(pt1m3a - pt0m3a, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # time
    AME_time_m3b <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3b <- predict(M3b, newdata=df_l, type="response")
     pt0m3b <- predict(M3b, newdata=df_ref, type="response")
     
     AME_time_m3b[level] <- mean(pt1m3b - pt0m3b, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # time
    AME_time_m3c <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3c <- predict(M3c, newdata=df_l, type="response")
     pt0m3c <- predict(M3c, newdata=df_ref, type="response")
     
     AME_time_m3c[level] <- mean(pt1m3c - pt0m3c, na.rm=TRUE)
     
   }
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # time
    AME_time_m4 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m4 <- predict(M4, newdata=df_l, type="response")
     pt0m4 <- predict(M4, newdata=df_ref, type="response")
     
     AME_time_m4[level] <- mean(pt1m4 - pt0m4, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_c3, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_c3.rda", location = "./results/robustness/bycohort/")


```



```{r, echo=FALSE}

load("./results/robustness/bycohort/20250610_c3.rda")
cohort3 <- x
rm(x)

```


```{r}

original <- cohort3$t0
bias <- colMeans(cohort3$t) - cohort3$t0
se <- apply(cohort3$t, 2, sd)

df.coh3 <- data.frame(original=original, bias=bias, se=se)

row.names(df.coh3) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1_0", "AME_time_m1_1", "AME_time_m1_2", "AME_time_m1_3", "AME_time_m1_4", "AME_time_m1_5", "AME_time_m2_0", "AME_time_m2_1", "AME_time_m2_2", "AME_time_m2_3", "AME_time_m2_4", "AME_time_m2_5", "AME_time_m3a_0", "AME_time_m3a_1", "AME_time_m3a_2", "AME_time_m3a_3", "AME_time_m3a_4", "AME_time_m3a_5", "AME_time_m3b_0", "AME_time_m3b_1", "AME_time_m3b_2", "AME_time_m3b_3", "AME_time_m3b_4", "AME_time_m3b_5", "AME_time_m3c_0", "AME_time_m3c_1", "AME_time_m3c_2", "AME_time_m3c_3", "AME_time_m3c_4", "AME_time_m3c_5", "AME_time_m4_0", "AME_time_m4_1", "AME_time_m4_2", "AME_time_m4_3", "AME_time_m4_4", "AME_time_m4_5","AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")


df.coh3$t <- (df.coh3$original / df.coh3$se)

# remove the time=0 rows, as 0 is the reference category for time
rows_to_remove <- grep("^AME_time_m(1|2|3a|3b|3c|4)_0$", rownames(df.coh3))
df.coh3 <- df.coh3[-rows_to_remove, ]

round(df.coh3, 5)

```

# Tables "Post-hoc analyses"

Cohort 1 (1997-2006)

```{r}

# Creating neat labels
table_ames_coh1 <- df.coh1 %>%
  mutate(term = rownames(df.coh1),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m[1-4][abc]?")) %>%
  mutate(model = recode(model,
                        "m1" = "M1",
                        "m2" = "M2",
                        "m3a" = "M3",
                        "m3b" = "M4",
                        "m3c" = "M5",
                        "m4" = "M6"),
         model = factor(model, levels = paste0("M", 1:6))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "genderwomsv") ~ "Women supervisors * Woman",
    str_detect(term, "gender") ~ "Woman",
    str_detect(term, "time") ~ paste0("Time since PhD: ", str_extract(term, "[:digit:]$"), " years"),
    str_detect(term, "cohort") ~ "PhD cohort",
    str_detect(term, "womsv") ~ "Women supervisors",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "netsize") ~ "Team size",
    str_detect(term, "prof") ~ "2+ professors",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)", original, se)) %>%
  select(label, model, value)

# correct table ordering
rows_tab <- c("Woman", "Time since PhD: 1 years", "Time since PhD: 2 years", "Time since PhD: 3 years", "Time since PhD: 4 years", "Time since PhD: 5 years", "Time since PhD: 6 years", "Time since PhD: 7 years", "Time since PhD: 8 years", "PhD cohort", "PhD cohort * Woman", "Cumulative publications", "Previous publications", "Team size", "2+ professors", "Supervisors' productivity", "Women supervisors", "Women supervisors * Woman")


# Reshape to wide format
table_df_coh1 <- table_ames_coh1 %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab)) %>%
  arrange(label)

# Replace NA values (not in the model) with empty strings
table_df_coh1$label <- as.character(table_df_coh1$label)
table_df_coh1[is.na(table_df_coh1$label), "label"] <- ""

# table_df_coh1[is.na(table_df_coh1)] <- ""

# Create pretty table
kable(table_df_coh1, "html", escape = FALSE, align = "lcccccc",
      col.names = c("", paste0("M", 1:6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt (Cohort 1: 1997-2006)" = 6))



```

Cohort 2 (2007-2014)

```{r}

# Creating neat labels
table_ames_coh2 <- df.coh2 %>%
  mutate(term = rownames(df.coh2),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m[1-4][abc]?")) %>%
  mutate(model = recode(model,
                        "m1" = "M1",
                        "m2" = "M2",
                        "m3a" = "M3",
                        "m3b" = "M4",
                        "m3c" = "M5",
                        "m4" = "M6"),
         model = factor(model, levels = paste0("M", 1:6))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "genderwomsv") ~ "Women supervisors * Woman",
    str_detect(term, "gender") ~ "Woman",
    str_detect(term, "time") ~ paste0("Time since PhD: ", str_extract(term, "[:digit:]$"), " years"),
    str_detect(term, "cohort") ~ "PhD cohort",
    str_detect(term, "womsv") ~ "Women supervisors",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "netsize") ~ "Team size",
    str_detect(term, "prof") ~ "2+ professors",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)", original, se)) %>%
  select(label, model, value)

# correct table ordering
rows_tab <- c("Woman", "Time since PhD: 1 years", "Time since PhD: 2 years", "Time since PhD: 3 years", "Time since PhD: 4 years", "Time since PhD: 5 years", "Time since PhD: 6 years", "Time since PhD: 7 years", "Time since PhD: 8 years", "PhD cohort", "PhD cohort * Woman", "Cumulative publications", "Previous publications", "Team size", "2+ professors", "Supervisors' productivity", "Women supervisors", "Women supervisors * Woman")


# Reshape to wide format
table_df_coh2 <- table_ames_coh2 %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab)) %>%
  arrange(label)

# Replace NA values (not in the model) with empty strings
table_df_coh2$label <- as.character(table_df_coh2$label)
table_df_coh2[is.na(table_df_coh2$label), "label"] <- ""

# Create pretty table
kable(table_df_coh2, "html", escape = FALSE, align = "lcccccc",
      col.names = c("", paste0("M", 1:6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt (Cohort 1: 1997-2006)" = 6))


```


Cohort 3 (2015-2019)

```{r}

# Creating neat labels
table_ames_coh3 <- df.coh3 %>%
  mutate(term = rownames(df.coh3),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m[1-4][abc]?")) %>%
  mutate(model = recode(model,
                        "m1" = "M1",
                        "m2" = "M2",
                        "m3a" = "M3",
                        "m3b" = "M4",
                        "m3c" = "M5",
                        "m4" = "M6"),
         model = factor(model, levels = paste0("M", 1:6))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "genderwomsv") ~ "Women supervisors * Woman",
    str_detect(term, "gender") ~ "Woman",
    str_detect(term, "time") ~ paste0("Time since PhD: ", str_extract(term, "[:digit:]$"), " years"),
    str_detect(term, "cohort") ~ "PhD cohort",
    str_detect(term, "womsv") ~ "Women supervisors",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "netsize") ~ "Team size",
    str_detect(term, "prof") ~ "2+ professors",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)", original, se)) %>%
  select(label, model, value)

# correct table ordering
rows_tab <- c("Woman", "Time since PhD: 1 years", "Time since PhD: 2 years", "Time since PhD: 3 years", "Time since PhD: 4 years", "Time since PhD: 5 years", "Time since PhD: 6 years", "Time since PhD: 7 years", "Time since PhD: 8 years", "PhD cohort", "PhD cohort * Woman", "Cumulative publications", "Previous publications", "Team size", "2+ professors", "Supervisors' productivity", "Women supervisors", "Women supervisors * Woman")


# Reshape to wide format
table_df_coh3 <- table_ames_coh3 %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab)) %>%
  arrange(label)

# Replace NA values (not in the model) with empty strings
table_df_coh3$label <- as.character(table_df_coh3$label)
table_df_coh3[is.na(table_df_coh3$label), "label"] <- ""

#table_df_coh3[is.na(table_df_coh3)] <- ""

# Create pretty table
kable(table_df_coh3, "html", escape = FALSE, align = "lcccccc",
      col.names = c("", paste0("M", 1:6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt (Cohort 1: 1997-2006)" = 6))


```


