---
title: "Mentoring for gender equality in early-career grant receipt: figures"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---

This lab journal demonstrates how we create the figures featured in the paper. 
  
----

# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}



fsave <- function(x, file, location="./data/processed/") {
  datename <- substr(gsub("[:-]", "", Sys.time()), 1,8)  
  totalname <- paste(location, datename, file, sep="")
  save(x, file = totalname)  
}



```

---  

# Packages


- `tidyverse`: For general data manipulation

- `boot`: To create bootstrapped standard errors, following the procedure delineated [here](https://www.jochemtolsma.nl/tutorials/me/)

- `ggtext`: to edit formatting of text in ggplot figures


```{r, results='hide'}

packages = c("tidyverse", "boot", "ggtext")

fpackage.check(packages)

```

--- 


# Input

We use several results objects:

* [veni_ppf](data/processed/veni_ppf.rda): Processed dataset containing all independent variables and the dependent variable
    - name of dataset: `veni_ppf`
    - used here to show Veni hazard rates per year after obtaining doctorate

* [20250506_ame.rda](https://github.com/ammulders/amatteroftime/results/cont_cohort/20250506_ame.rda): results of our main analyses with bootstrapped standard errors

* [20250507_c1-3.rda](https://github.com/ammulders/amatteroftime/results/robustness/bycohort/20250507_c1.rda): results of our models split out by cohort



```{r files, eval=TRUE}


load(file="./results/cont_cohort/20250506_ame.rda")
AMEs <- x

load("./data/processed/veni_ppf.rda")



load(file = "./results/robustness/bycohort/20250507_c1.rda")
coh1 <- x
rm(x)

load(file = "./results/robustness/bycohort/20250507_c2.rda")
coh2 <- x
rm(x)

load(file = "./results/robustness/bycohort/20250507_c3.rda")
coh3 <- x
rm(x)



```




## Figure 1: Veni hazard rate by time and gender


```{r}

menc <- "#D1C166"
womenc <- "#48a363"

veni_ppf %>%
  filter(year>2002) %>%
  group_by(time, gender_2) %>%
  summarise(event = sum(veni),
            total = n()) %>%
  mutate(hazard = event/total) %>%
  ggplot(aes(x=time, y = hazard, group = gender_2, color=gender_2)) +
  geom_point() +
  labs(x = "Time in years since doctorate receipt", y="Hazard") +
  geom_line() + 
  scale_color_manual(values=c(menc, womenc), name="Gender") +
  theme(axis.title=element_text(face="bold"), 
        legend.title=element_text(face="bold"),
        panel.grid.major.x = element_blank(), 
        panel.background = element_rect(fill="white"),
        panel.grid.major.y = element_line(color="#C9c9c9", linewidth=0.2),
        panel.grid.minor=element_blank())



veni_ppf %>%
  filter(year>2002) %>%
  group_by(time, gender_2) %>%
  summarise(event = sum(veni),
            total = n()) %>%
  mutate(hazard = event/total) -> datacheck
  

```




## Figure 2: Model coefficients


Loading in the model output and creating dataframes for each model


```{r}

original <- AMEs$t0
bias <- colMeans(AMEs$t) - AMEs$t0
se <- apply(AMEs$t, 2, sd)

AMEs.df <- data.frame(original=original, bias=bias, se=se)
row.names(AMEs.df) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

AMEs$t <- (AMEs$original / AMEs$se)


```


```{r}

tot <- "#414141"
menc <- "#D1C166"
womenc <- "#48a363"

```


Extracting relevant coefficients and creating a combined dataframe containing the results of all models
```{r}

models <- rownames(AMEs.df)

AMEs.df %>%
  mutate(ame = original,
         model = toupper(str_remove(models, "^.*_"))) %>%
  select(ame, model, se) -> ames
  
row.names(ames) <- models

ames$cov2 <- str_remove(rownames(ames), "_m[:digit:][abc]?")

ames$covariate <- ""
ames$covariate <- ifelse(ames$cov2=="AME_gender", "Woman **(H1)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_cohort", "PhD cohort **(H2a)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_time", "Time in years since PhD", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_gendercohort", "PhD cohort * Woman **(H2b)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_cpubs", "Publications: cumulative", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_ppubs", "Publications: previous year", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_netsize", "Supervision team: size **(H3a)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_prof", "Supervision team: 2+ professors **(H3b)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_svpubs", "Supervision team: publications **(H3c)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_womsv", "Supervision team: 1+ woman **(H4a)**", ames$covariate)
ames$covariate <- ifelse(ames$cov2=="AME_genderwomsv", "Woman * 1+ woman **(H4b)**", ames$covariate)

ames$covariate <- factor(ames$covariate, levels=c("Woman **(H1)**", "PhD cohort **(H2a)**", "Time in years since PhD", "PhD cohort * Woman **(H2b)**", "Supervision team: size **(H3a)**", "Supervision team: 2+ professors **(H3b)**", "Supervision team: publications **(H3c)**", "Supervision team: 1+ woman **(H4a)**", "Woman * 1+ woman **(H4b)**", "Publications: cumulative", "Publications: previous year"))

ames <- ames %>% mutate(model = ifelse(model=="M4", "M6", model),
                        model = ifelse(model=="M3A", "M3", model),
                        model = ifelse(model=="M3B", "M4", model),
                        model = ifelse(model=="M3C", "M5", model))

ames$model <- factor(ames$model, levels=c("M1", "M2", "M3", "M4", "M5", "M6"))
#AMEs$model <- factor(AMEs$model, levels=c("M6", "M5", "M4", "M3", "M2", "M1"))

ames <- ames %>% arrange(covariate, model)

```



```{r}

ggplot(ames, aes(y=ame, x=covariate)) +
  geom_hline(yintercept=0, color="brown4", linewidth=.5) +
  geom_point() +
  facet_wrap(model ~ ., nrow=3, ncol=2, scales = "free") + 
  geom_pointrange(aes(ymin = ame - 1.96*se, ymax = ame + 1.96*se), size=0.1) +
  scale_y_continuous(limits = c(-0.005, 0.005), breaks=seq(-0.005, 0.005, by = 0.005)) +
  labs(y="AME") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_markdown(angle=30, hjust=1, vjust=1),
        legend.position = "none",
        strip.text.x = element_markdown(angle=0, size=9, face="bold"),
        strip.background = element_blank(),
        panel.background = element_rect(fill="white"),
        panel.spacing = unit(0.1, 'points'),
        panel.grid.major.y = element_line(color="#C9c9c9", linewidth=0.2, linetype=3),
        panel.grid.minor=element_blank(),
        panel.grid.major.x=element_blank())

```



## Figure 3: Cohort splits


```{r}

original <- coh1$t0
bias <- colMeans(coh1$t) - coh1$t0
se <- apply(coh1$t, 2, sd)

df.coh1 <- data.frame(original=original, bias=bias, se=se)

row.names(df.coh1) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh1$t <- (df.coh1$original / df.coh1$se)

round(df.coh1, 5)

df.coh1 <- df.coh1[3,] # select only gender M3

df.coh1 %>%
  mutate(ame = original, 
         cohort = "Cohort 1") %>%
  select(ame, se, cohort) -> ames1


original <- coh2$t0
bias <- colMeans(coh2$t) - coh2$t0
se <- apply(coh2$t, 2, sd)

df.coh2 <- data.frame(original=original, bias=bias, se=se)

row.names(df.coh2) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_2015_m2", "AME_2015_m3a", "AME_2015_m3b", "AME_2015_m3c", "AME_2015_m4", "AME_gender2015_m2", "AME_gender2015_m3a", "AME_gender2015_m3b", "AME_gender2015_m3c", "AME_gender2015_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh2$t <- (df.coh2$original / df.coh2$se)

round(df.coh2, 5)  

df.coh2 <- df.coh2[3,]

df.coh2 %>%
  mutate(ame = original, 
         cohort = "Cohort 2") %>%
  select(ame, se, cohort) -> ames2


original <- coh3$t0
bias <- colMeans(coh3$t) - coh3$t0
se <- apply(coh3$t, 2, sd)

df.coh3 <- data.frame(original=original, bias=bias, se=se)


row.names(df.coh3) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh3$t <- (df.coh3$original / df.coh3$se)

round(df.coh3, 5)

df.coh3 <- df.coh3[3,]

df.coh3 %>%
  mutate(ame = original, 
         cohort = "Cohort 3") %>%
  select(ame, se, cohort) -> ames3

AMEs <- do.call("rbind", list(ames1, ames2, ames3))

AMEs$covariate <- c("Woman (coh. 1997-2006)", "Woman (coh. 2007-2014)", "Woman (coh. 2015-2019)")


```


```{r}

ggplot(AMEs, aes(y=ame, x=covariate)) +
  geom_hline(yintercept=0, color="brown4", linewidth=.5) +
  geom_point() +
  geom_pointrange(aes(ymin = ame - 1.96*se, ymax = ame + 1.96*se), size=0.1) +
  scale_y_continuous(limits = c(-0.004, 0.008), breaks=seq(-0.005, 0.010, by = 0.005)) +
  labs(y="AME") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_markdown(angle=20, hjust=1, vjust=1),
        legend.position = "none",
        strip.text.x = element_markdown(angle=0, size=9, face="bold"),
        strip.background = element_blank(),
        panel.background = element_rect(fill="white"),
        panel.spacing = unit(0.1, 'points'),
        panel.grid.major.y = element_line(color="#C9c9c9", linewidth=0.2, linetype=3),
        panel.grid.minor=element_blank(),
        panel.grid.major.x=element_blank())

```

