---
title: "Mentoring for gender equality in early-career grant receipt: supplementary analyses"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---

This lab journal details the additional analyses performed to ensure the robustness of our results.  
  
----

# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}



fsave <- function(x, file, location="./data/processed/") {
  datename <- substr(gsub("[:-]", "", Sys.time()), 1,8)  
  totalname <- paste(location, datename, file, sep="")
  save(x, file = totalname)  
}



```

---  

# Packages


- `tidyverse`: For general data manipulation

- `boot`: To create bootstrapped standard errors, following the procedure delineated [here](https://www.jochemtolsma.nl/tutorials/me/)


```{r, results='hide'}
packages = c("tidyverse", "boot")

fpackage.check(packages)


```

--- 


# Input

We use several processed datasets:

* [veni_ppf_c1](data/processed/veni_ppf_c1.rda): 
    - name of dataset: `veni_ppf_c1` 
    - data of Veni's obtained for scholars with PhD year 1997-2006

* [veni_ppf_c2](data/processed/veni_ppf_c2.rda): 
    - name of dataset: `veni_ppf_c2` 
    - data of Veni's obtained for scholars with PhD year 2007-2014

* [veni_ppf_c3](data/processed/veni_ppf_c3.rda): 
    - name of dataset: `veni_ppf_c3` 
    - data of Veni's obtained for scholars with PhD year 2015+

* [veni_ppf_r1](data/processed/veni_ppf_r1.rda): 
    - name of dataset: `veni_ppf_r1` 
    - veni_ppf data, but without PhDs who obtained doctorate at EUR, RUG, TUD, LU
    

* [veni_ppf_r2](data/processed/veni_ppf_r2.rda): 
    - name of dataset: `veni_ppf_r2` 
    - veni_ppf data, but with all publishing scholars
    
    
* [veni_ppf](data/processed/veni_ppf.rda): 
    - name of dataset: `veni_ppf` 
    - original veni_ppf data



```{r files, eval=TRUE}

load(file = "data/processed/veni_ppf_r1.rda")

load(file = "data/processed/veni_ppf_r2.rda")


load(file = "data/processed/veni_ppf_c1.rda")
load(file = "data/processed/veni_ppf_c2.rda")
load(file = "data/processed/veni_ppf_c3.rda")

load(file = "data/processed/veni_ppf.rda")

veni_ppf %>%
  distinct(.keep_all=TRUE) -> veni_ppf

```




# Post-2015 effects


## Cohort group 1 (1997-2006)
```{r, eval=FALSE}


# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    dftp <- dftm <- df
    dftp$time <- dftp$time + s
    dftm$time <- dftm$time - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftp)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftm)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftp)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftm)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftp)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftm)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftp)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftm)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftp)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftm)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftp)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftm)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_c1, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_c1.rda", location = "./results/robustness/bycohort/")


```


```{r, echo=FALSE}

load("./results/robustness/bycohort/20250507_c1.rda")
cohort1 <- x
rm(x)

```


```{r}

original <- cohort1$t0
bias <- colMeans(cohort1$t) - cohort1$t0
se <- apply(cohort1$t, 2, sd)

df.coh1 <- data.frame(original=original, bias=bias, se=se)
row.names(df.coh1) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh1$t <- (df.coh1$original / df.coh1$se)

round(df.coh1, 5)

```



## Cohort group 2 (2007-2014)

Adding a variable: after 2015. To measure whether chances of obtaining a Veni are actually larger for this group in the years after the extension policy was introduced. 

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(p2015) * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    dftp <- dftm <- df
    dftp$time <- dftp$time + s
    dftm$time <- dftm$time - s
    
    # 2015+ datasets
    dfp151 <- dfp150 <- df
    dfp151$p2015 <- 1
    dfp150$p2015 <- 0
    
    # 2015+ * gender datasets
    dfwomenp151 <- dfwomenp150 <- dfmenp151 <- dfmenp150 <- df
    
    dfwomenp151$gender_2 <- dfwomenp150$gender_2 <- "women"
    dfmenp151$gender_2 <- dfmenp150$gender_2 <- "men"
    dfwomenp151$gender_2 <- factor(dfwomenp151$gender_2, levels=levels(df$gender_2))
    dfwomenp150$gender_2 <- factor(dfwomenp150$gender_2, levels=levels(df$gender_2))
    dfmenp151$gender_2 <- factor(dfmenp151$gender_2, levels=levels(df$gender_2))
    dfmenp150$gender_2 <- factor(dfmenp150$gender_2, levels=levels(df$gender_2))
    
    dfwomenp151$p2015 <- dfmenp151$p2015 <- 1
    dfwomenp150$p2015 <- dfmenp150$p2015 <- 0
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftp)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftm)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftp)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftm)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)
    
    # 2015+
    p1512 <- as.numeric(unlist(predict(M2, type="response", newdata=dfp151)))
    p1502 <- as.numeric(unlist(predict(M2, type="response", newdata=dfp150)))
    AME_2015_m2 <- mean(p1512 - p1502, na.rm=TRUE)

    # gender * 2015+
    pw1512 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomenp151)))
    pw1502 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomenp150)))
    pm1512 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmenp151)))
    pm1502 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmenp150)))
    AME_gender2015_m2 <- mean(((pw1512 - pm1512) - (pw1502 - pm1502)), na.rm=TRUE)
    
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftp)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftm)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    # 2015+
    p1513a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfp151)))
    p1503a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfp150)))
    AME_2015_m3a <- mean(p1513a - p1503a, na.rm=TRUE)

    # gender * 2015+
    pw1513a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomenp151)))
    pw1503a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomenp150)))
    pm1513a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmenp151)))
    pm1503a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmenp150)))
    AME_gender2015_m3a <- mean(((pw1513a - pm1513a) - (pw1503a - pm1503a)), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftp)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftm)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
    # 2015+
    p1513b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfp151)))
    p1503b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfp150)))
    AME_2015_m3b <- mean(p1513b - p1503b, na.rm=TRUE)

    # gender * 2015+
    pw1513b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomenp151)))
    pw1503b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomenp150)))
    pm1513b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmenp151)))
    pm1503b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmenp150)))
    AME_gender2015_m3b <- mean(((pw1513b - pm1513b) - (pw1503b - pm1503b)), na.rm=TRUE)
    
    
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftp)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftm)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
    # 2015+
    p1513c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfp151)))
    p1503c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfp150)))
    AME_2015_m3c <- mean(p1513c - p1503c, na.rm=TRUE)

    # gender * 2015+
    pw1513c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomenp151)))
    pw1503c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomenp150)))
    pm1513c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmenp151)))
    pm1503c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmenp150)))
    AME_gender2015_m3c <- mean(((pw1513c - pm1513c) - (pw1503c - pm1503c)), na.rm=TRUE)
    
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftp)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftm)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    # 2015+
    p1514 <- as.numeric(unlist(predict(M4, type="response", newdata=dfp151)))
    p1504 <- as.numeric(unlist(predict(M4, type="response", newdata=dfp150)))
    AME_2015_m4 <- mean(p1514 - p1504, na.rm=TRUE)

    # gender * 2015+
    pw1514 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomenp151)))
    pw1504 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomenp150)))
    pm1514 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmenp151)))
    pm1504 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmenp150)))
    AME_gender2015_m4 <- mean(((pw1514 - pm1514) - (pw1504 - pm1504)), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_2015_m2, AME_2015_m3a, AME_2015_m3b, AME_2015_m3c, AME_2015_m4, AME_gender2015_m2, AME_gender2015_m3a, AME_gender2015_m3b, AME_gender2015_m3c, AME_gender2015_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_c2, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_c2.rda", location = "./results/robustness/bycohort/")

```


```{r, echo=FALSE}

load("./results/robustness/bycohort/20250507_c2.rda")
cohort2 <- x
rm(x)

```


```{r}

original <- cohort2$t0
bias <- colMeans(cohort2$t) - cohort2$t0
se <- apply(cohort2$t, 2, sd)

df.coh2 <- data.frame(original=original, bias=bias, se=se)
row.names(df.coh2) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_2015_m2", "AME_2015_m3a", "AME_2015_m3b", "AME_2015_m3c", "AME_2015_m4", "AME_gender2015_m2", "AME_gender2015_m3a", "AME_gender2015_m3b", "AME_gender2015_m3c", "AME_gender2015_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh2$t <- (df.coh2$original / df.coh2$se)

round(df.coh2, 5)

```



## Cohort group 3 (2015-2019)
```{r, eval=FALSE}


# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    dftp <- dftm <- df
    dftp$time <- dftp$time + s
    dftm$time <- dftm$time - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftp)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftm)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftp)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftm)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftp)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftm)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftp)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftm)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftp)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftm)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftp)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftm)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_c3, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "_c3.rda", location = "./results/robustness/bycohort/")


```



```{r, echo=FALSE}

load("./results/robustness/bycohort/20250507_c3.rda")
cohort3 <- x
rm(x)

```


```{r}

original <- cohort3$t0
bias <- colMeans(cohort3$t) - cohort3$t0
se <- apply(cohort3$t, 2, sd)

df.coh3 <- data.frame(original=original, bias=bias, se=se)
row.names(df.coh3) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.coh3$t <- (df.coh3$original / df.coh3$se)

round(df.coh3, 5)

```






# Sample without EUR/RUG/TUD/LU


```{r}

summary(as.factor(veni_ppf_r1$uni))

veni_ppf_r1$uni <- factor(veni_ppf_r1$uni, levels=c("RU", "TUE", "TI", "UM", "UT", "UU", "UvA", "VU", "WUR"))

summary(as.factor(veni_ppf_r1$uni))


nrow(veni_ppf_r1[!duplicated(veni_ppf_r1$id),])

summary(as.factor(veni_ppf_r1$veni))


```


AMEs model 1-4

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) * phd_year + time, family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    dftp <- dftm <- df
    dftp$time <- dftp$time + s
    dftm$time <- dftm$time - s
    
    # cohort * gender datasets
    dfwcp <- dfwcm <- dfmcp <- dfmcm <- df
    dfwcp$gender_2 <- dfwcm$gender_2 <- "women"
    dfmcp$gender_2 <- dfmcm$gender_2 <- "men"
    
    dfwcp$gender_2 <- factor(dfwcp$gender_2, levels=levels(df$gender_2))
    dfwcm$gender_2 <- factor(dfwcm$gender_2, levels=levels(df$gender_2))
    dfmcp$gender_2 <- factor(dfmcp$gender_2, levels=levels(df$gender_2))
    dfmcm$gender_2 <- factor(dfmcm$gender_2, levels=levels(df$gender_2))
    
    dfwcp$phd_year <- dfmcp$phd_year <- df$phd_year + s
    dfwcm$phd_year <- dfmcm$phd_year <- df$phd_year - s
    
    # cohort datasets
    dfcp <- dfcm <- df
    dfcp$phd_year <- df$phd_year + s
    dfcm$phd_year <- df$phd_year - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftp)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftm)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # cohort
    pcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcp)))
    pcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcm)))
    AME_cohort_m2 <- mean(pcp2 - pcm2, na.rm=TRUE)

    # gender * cohort
    pwcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcp)))
    pwcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcm)))
    pmcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcp)))
    pmcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcm)))
    AME_gendercohort_m2 <- mean(((pwcp2 - pmcp2) - (pwcm2 - pmcm2)) / (2*s), na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftp)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftm)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
   # cohort
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcm)))
    AME_cohort_m3a <- mean(pcp3a - pcm3a, na.rm=TRUE)

    # gender * cohort
    pwcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcp)))
    pwcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcm)))
    pmcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcp)))
    pmcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcm)))
    AME_gendercohort_m3a <- mean(((pwcp3a - pmcp3a) - (pwcm3a - pmcm3a)) / (2*s), na.rm=TRUE)

    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftp)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftm)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # cohort
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcm)))
    AME_cohort_m3b <- mean(pcp3b - pcm3b, na.rm=TRUE)

    # gender * cohort
    pwcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcp)))
    pwcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcm)))
    pmcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcp)))
    pmcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcm)))
    AME_gendercohort_m3b <- mean(((pwcp3b - pmcp3b) - (pwcm3b - pmcm3b)) / (2*s), na.rm=TRUE)

    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftp)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftm)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # cohort
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcm)))
    AME_cohort_m3c <- mean(pcp3c - pcm3c, na.rm=TRUE)
    
    # gender * cohort
    pwcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcp)))
    pwcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcm)))
    pmcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcp)))
    pmcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcm)))
    AME_gendercohort_m3c <- mean(((pwcp3c - pmcp3c) - (pwcm3c - pmcm3c)) / (2*s), na.rm=TRUE)

    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftp)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftm)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # cohort
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcm)))
    AME_cohort_m4 <- mean(pcp4 - pcm4, na.rm=TRUE)
    
    # gender * cohort
    pwcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcp)))
    pwcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcm)))
    pmcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcp)))
    pmcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcm)))
    AME_gendercohort_m4 <- mean(((pwcp4 - pmcp4) - (pwcm4 - pmcm4)) / (2*s), na.rm=TRUE)
    
    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftp)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftm)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_cohort_m2, AME_cohort_m3a, AME_cohort_m3b, AME_cohort_m3c, AME_cohort_m4, AME_gendercohort_m2, AME_gendercohort_m3a, AME_gendercohort_m3b, AME_gendercohort_m3c, AME_gendercohort_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_r1, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "uni_sel.rda", location = "./results/robustness/")


```

```{r, echo=FALSE}

load("./results/robustness/20250507uni_sel.rda")
uni_sel <- x
rm(x)

```


```{r, eval=FALSE}

original <- uni_sel$t0
bias <- colMeans(uni_sel$t) - uni_sel$t0
se <- apply(uni_sel$t, 2, sd)

df.uni_sel <- data.frame(original=original, bias=bias, se=se)


row.names(df.uni_sel) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

row.names(df.uni_sel) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.uni_sel$t <- (df.uni_sel$original / df.uni_sel$se)

round(df.uni_sel, 5)

```




# Sample with all Veni's awarded to scholars with a NARCIS profile



```{r}

nrow(veni_ppf_r2[!duplicated(veni_ppf_r2$id),])

summary(as.factor(veni_ppf_r2$veni))


```


AMEs model 1-4

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + time, family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) * phd_year + time, family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + time + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    dftp <- dftm <- df
    dftp$time <- dftp$time + s
    dftm$time <- dftm$time - s
    
    # cohort * gender datasets
    dfwcp <- dfwcm <- dfmcp <- dfmcm <- df
    dfwcp$gender_2 <- dfwcm$gender_2 <- "women"
    dfmcp$gender_2 <- dfmcm$gender_2 <- "men"
    
    dfwcp$gender_2 <- factor(dfwcp$gender_2, levels=levels(df$gender_2))
    dfwcm$gender_2 <- factor(dfwcm$gender_2, levels=levels(df$gender_2))
    dfmcp$gender_2 <- factor(dfmcp$gender_2, levels=levels(df$gender_2))
    dfmcm$gender_2 <- factor(dfmcm$gender_2, levels=levels(df$gender_2))
    
    dfwcp$phd_year <- dfmcp$phd_year <- df$phd_year + s
    dfwcm$phd_year <- dfmcm$phd_year <- df$phd_year - s
    
    # cohort datasets
    dfcp <- dfcm <- df
    dfcp$phd_year <- df$phd_year + s
    dfcm$phd_year <- df$phd_year - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftp)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dftm)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # cohort
    pcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcp)))
    pcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcm)))
    AME_cohort_m2 <- mean(pcp2 - pcm2, na.rm=TRUE)

    # gender * cohort
    pwcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcp)))
    pwcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcm)))
    pmcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcp)))
    pmcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcm)))
    AME_gendercohort_m2 <- mean(((pwcp2 - pmcp2) - (pwcm2 - pmcm2)) / (2*s), na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftp)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dftm)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
   # cohort
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcm)))
    AME_cohort_m3a <- mean(pcp3a - pcm3a, na.rm=TRUE)

    # gender * cohort
    pwcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcp)))
    pwcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcm)))
    pmcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcp)))
    pmcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcm)))
    AME_gendercohort_m3a <- mean(((pwcp3a - pmcp3a) - (pwcm3a - pmcm3a)) / (2*s), na.rm=TRUE)

    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftp)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dftm)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # cohort
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcm)))
    AME_cohort_m3b <- mean(pcp3b - pcm3b, na.rm=TRUE)

    # gender * cohort
    pwcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcp)))
    pwcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcm)))
    pmcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcp)))
    pmcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcm)))
    AME_gendercohort_m3b <- mean(((pwcp3b - pmcp3b) - (pwcm3b - pmcm3b)) / (2*s), na.rm=TRUE)

    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftp)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dftm)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # cohort
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcm)))
    AME_cohort_m3c <- mean(pcp3c - pcm3c, na.rm=TRUE)
    
    # gender * cohort
    pwcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcp)))
    pwcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcm)))
    pmcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcp)))
    pmcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcm)))
    AME_gendercohort_m3c <- mean(((pwcp3c - pmcp3c) - (pwcm3c - pmcm3c)) / (2*s), na.rm=TRUE)

    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftp)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dftm)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # cohort
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcm)))
    AME_cohort_m4 <- mean(pcp4 - pcm4, na.rm=TRUE)
    
    # gender * cohort
    pwcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcp)))
    pwcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcm)))
    pmcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcp)))
    pmcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcm)))
    AME_gendercohort_m4 <- mean(((pwcp4 - pmcp4) - (pwcm4 - pmcm4)) / (2*s), na.rm=TRUE)
    
    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftp)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftm)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_cohort_m2, AME_cohort_m3a, AME_cohort_m3b, AME_cohort_m3c, AME_cohort_m4, AME_gendercohort_m2, AME_gendercohort_m3a, AME_gendercohort_m3b, AME_gendercohort_m3c, AME_gendercohort_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_r2, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(AMEs, file = "allphds.rda", location = "./results/robustness/")


```

```{r, echo=FALSE}

load("./results/robustness/20250507allphds.rda")
allphds <- x
rm(x)

```


```{r}

original <- allphds$t0
bias <- colMeans(allphds$t) - allphds$t0
se <- apply(allphds$t, 2, sd)

df.allphds <- data.frame(original=original, bias=bias, se=se)

row.names(df.allphds) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")


df.allphds$t <- (df.allphds$original / df.allphds$se)

round(df.allphds, 5)

```


