---
title: "Mentoring for gender equality in early-career grant receipt: supplementary analyses"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---

This lab journal details the additional analyses performed to ensure the robustness of our results.  
  
----

# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}



fsave <- function(x, file, location="./data/processed/") {
  datename <- substr(gsub("[:-]", "", Sys.time()), 1,8)  
  totalname <- paste(location, datename, file, sep="")
  save(x, file = totalname)  
}



```

---  

# Packages


- `tidyverse`: For general data manipulation

- `boot`: To create bootstrapped standard errors, following the procedure delineated [here](https://www.jochemtolsma.nl/tutorials/me/)


```{r, results='hide'}
packages = c("tidyverse", "boot")

fpackage.check(packages)


```

--- 


# Input

We use several processed datasets:

* [veni3_ppf](data/processed/veni3_ppf.rda): 
    - name of dataset: `veni3_ppf` 
    - data of Veni's obtained within 3 years of obtaining doctorate


* [veni1_ppf](data/processed/veni1_ppf.rda): 
    - name of dataset: `veni1_ppf` 
    - data of Veni's obtained within 1 year of obtaining doctorate

    
* [veni48_ppf](data/processed/veni48_ppf.rda): 
    - name of dataset: `veni48_ppf` 
    - data of Veni's obtained between 4 to 8 years of obtaining doctorate
    

* [veni_ppf_r1](data/processed/veni_ppf_r1.rda): 
    - name of dataset: `veni_ppf_r1` 
    - veni_ppf data, but without PhDs who obtained doctorate at EUR, RUG, TUD, LU
    
    
* [veni_ppf](data/processed/veni_ppf.rda): 
    - name of dataset: `veni_ppf` 
    - original veni_ppf data, used for analyses split out by cohort



```{r files, eval=TRUE}

load(file = "data/processed/veni3_ppf.rda")

load(file = "data/processed/veni1_ppf.rda")

load(file = "data/processed/veni48_ppf.rda")

load(file = "data/processed/veni_ppf_r1.rda")

load(file = "data/processed/veni_ppf.rda")

```



# Veni within 3 years


AMEs model 1-4

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2


bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
 M1 <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)

  
  M2 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"), data = df)
  
  M3b_size <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize,
          family = binomial(link="cloglog"), data = df)
  
  M3b_prof <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)


  M4 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
     # extension gender interaction
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    # size * gender datasets
    womennsp <- womennsm <- mennsp <- mennsm <- df
    womennsp$gender_2 <- womennsm$gender_2 <- "women"
    mennsp$gender_2 <- mennsm$gender_2 <- "men"
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    womennsp$teamsize <- mennsp$teamsize <- df$teamsize + s
    womennsm$teamsize <- mennsm$teamsize <- df$teamsize - s
    
    # professors * gender
    womenpp <- womenpm <- menpp <- menpm <- df
    womenpp$gender_2 <- womenpm$gender_2 <- "women"
    menpp$gender_2 <- menpm$gender_2 <- "men"
    womenpp$gender_2 <- factor(womenpp$gender_2, levels=levels(df$gender_2))
    womenpm$gender_2 <- factor(womenpm$gender_2, levels=levels(df$gender_2))
    menpp$gender_2 <- factor(menpp$gender_2, levels=levels(df$gender_2))
    menpm$gender_2 <- factor(menpm$gender_2, levels=levels(df$gender_2))
    menpp$prof2p <- womenpp$prof2p <- 1 
    menpm$prof2p <- womenpm$prof2p <- 0
    
    # woman supervisor * gender
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext1)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext0)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    
    # gender * time
    pwp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene1)))
    pwm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene0)))
    pmp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene1)))
    pmm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene0)))
    AME_gendertime_m2 <- mean(((pwp2 - pmp2) - (pwm2 - pmm2)) / (2*s), na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext1)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext0)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)

    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # gender * time
    pwp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene1)))
    pwm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene0)))
    pmp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene1)))
    pmm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene0)))
    AME_gendertime_m3a <- mean(((pwp3a - pmp3a) - (pwm3a - pmm3a)) / (2*s), na.rm=TRUE)

    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext1)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext0)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # gender * time
    pwp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene1)))
    pwm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene0)))
    pmp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene1)))
    pmm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene0)))
    AME_gendertime_m3b <- mean(((pwp3b - pmp3b) - (pwm3b - pmm3b)) / (2*s), na.rm=TRUE)

    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext1)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext0)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # gender * time
    pwp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene1)))
    pwm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene0)))
    pmp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene1)))
    pmm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene0)))
    AME_gendertime_m3c <- mean(((pwp3c - pmp3c) - (pwm3c - pmm3c)) / (2*s), na.rm=TRUE)

    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext1)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext0)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene0)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomentm)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmentm)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)

    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof3a - noprof4, na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # size * gender
    wom_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsp)))
    wom_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsm)))
    men_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsp)))
    men_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsm)))
    AME_gendersize_m4 <- mean(((wom_nsp - men_nsp) - (wom_nsm - men_nsm)) / (2*s), na.rm=TRUE)
    
    # prof * gender
    wom_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpp)))
    wom_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpm)))
    men_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpp)))
    men_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpm)))
    AME_genderprof_m4 <- mean(((wom_pp - men_pp) - (wom_pm - men_pm)) / (2*s), na.rm=TRUE)
    
    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws - menws) - (womnows - mennows)) / (2*s), na.rm=TRUE)
    
    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_gendertime_m2, AME_gendertime_m3a, AME_gendertime_m3b, AME_gendertime_m3c, AME_gendertime_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_womsv_m3c, AME_womsv_m4, AME_gendersize_m4, AME_genderprof_m4, AME_genderwomsv_m4)
   #save results
}

veni3_r <- boot(data=veni3_ppf, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(veni3_r, file = "veni3.rda", location = "./results/veni3/")


```

```{r, echo=FALSE}

load("./results/veni3/20240305veni3.rda")
veni3_r <- x
rm(x)

```


```{r}

original <- veni3_r$t0
bias <- colMeans(veni3_r$t) - veni3_r$t0
se <- apply(veni3_r$t, 2, sd)

df.veni3 <- data.frame(original=original, bias=bias, se=se)
row.names(df.veni3) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m4", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m4", "AME_netsize_m3a", "AME_netsize_m3b", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m4", "AME_womsv_m3b", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4")

df.veni3$t <- (df.veni3$original / df.veni3$se)

round(df.veni3, 5)

```



Veni within 3 years: logistic

```{r}

veni3_ppf %>%
  group_by(id) %>%
  arrange(desc(year)) %>%
  top_n(1) -> veni3_log


M1 <- glm(formula = veni ~ as.factor(gender_2) + phd_year, family = "binomial", data = veni3_log)
summary(M1)
  
# M2: same as M1 because we don't have extended in the model anymore
# M2 <- glm(formula = veni ~ as.factor(gender_2) + phd_year, family = "binomial", data = veni3_log)
  
M3a <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = "binomial", data = veni3_log)
summary(M3a)

M3b <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = "binomial", data = veni3_log)
summary(M3b)

M3c <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = "binomial", data = veni3_log)
summary(M3c)

M4 <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = "binomial", data = veni3_log)
summary(M4)


```




# Veni within 1 year

AMEs model 1-4

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2


bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
 M1 <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)

  
  M2 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"), data = df)
  
  M3b_size <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize,
          family = binomial(link="cloglog"), data = df)
  
  M3b_prof <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)


  M4 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
     # extension gender interaction
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    # size * gender datasets
    womennsp <- womennsm <- mennsp <- mennsm <- df
    womennsp$gender_2 <- womennsm$gender_2 <- "women"
    mennsp$gender_2 <- mennsm$gender_2 <- "men"
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    womennsp$teamsize <- mennsp$teamsize <- df$teamsize + s
    womennsm$teamsize <- mennsm$teamsize <- df$teamsize - s
    
    # professors * gender
    womenpp <- womenpm <- menpp <- menpm <- df
    womenpp$gender_2 <- womenpm$gender_2 <- "women"
    menpp$gender_2 <- menpm$gender_2 <- "men"
    womenpp$gender_2 <- factor(womenpp$gender_2, levels=levels(df$gender_2))
    womenpm$gender_2 <- factor(womenpm$gender_2, levels=levels(df$gender_2))
    menpp$gender_2 <- factor(menpp$gender_2, levels=levels(df$gender_2))
    menpm$gender_2 <- factor(menpm$gender_2, levels=levels(df$gender_2))
    menpp$prof2p <- womenpp$prof2p <- 1 
    menpm$prof2p <- womenpm$prof2p <- 0
    
    # woman supervisor * gender
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext1)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext0)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    
    # gender * time
    pwp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene1)))
    pwm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene0)))
    pmp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene1)))
    pmm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene0)))
    AME_gendertime_m2 <- mean(((pwp2 - pmp2) - (pwm2 - pmm2)) / (2*s), na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext1)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext0)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)

    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # gender * time
    pwp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene1)))
    pwm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene0)))
    pmp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene1)))
    pmm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene0)))
    AME_gendertime_m3a <- mean(((pwp3a - pmp3a) - (pwm3a - pmm3a)) / (2*s), na.rm=TRUE)

    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext1)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext0)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # gender * time
    pwp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene1)))
    pwm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene0)))
    pmp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene1)))
    pmm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene0)))
    AME_gendertime_m3b <- mean(((pwp3b - pmp3b) - (pwm3b - pmm3b)) / (2*s), na.rm=TRUE)

    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext1)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext0)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # gender * time
    pwp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene1)))
    pwm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene0)))
    pmp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene1)))
    pmm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene0)))
    AME_gendertime_m3c <- mean(((pwp3c - pmp3c) - (pwm3c - pmm3c)) / (2*s), na.rm=TRUE)

    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext1)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext0)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene0)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomentm)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftimep)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dftimem)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)

    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof3a - noprof4, na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # size * gender
    wom_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsp)))
    wom_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsm)))
    men_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsp)))
    men_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsm)))
    AME_gendersize_m4 <- mean(((wom_nsp - men_nsp) - (wom_nsm - men_nsm)) / (2*s), na.rm=TRUE)
    
    # prof * gender
    wom_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpp)))
    wom_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpm)))
    men_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpp)))
    men_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpm)))
    AME_genderprof_m4 <- mean(((wom_pp - men_pp) - (wom_pm - men_pm)) / (2*s), na.rm=TRUE)
    
    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws - menws) - (womnows - mennows)) / (2*s), na.rm=TRUE)
    
    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_gendertime_m2, AME_gendertime_m3a, AME_gendertime_m3b, AME_gendertime_m3c, AME_gendertime_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_womsv_m3c, AME_womsv_m4, AME_gendersize_m4, AME_genderprof_m4, AME_genderwomsv_m4)
   #save results
}

veni1_r <- boot(data=veni1_ppf, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(veni1_r, file = "veni1.rda", location = "./results/veni1/")


```

```{r, echo=FALSE}

load("./results/veni1/20240305veni1.rda")
veni1_r <- x
rm(x)

```


```{r}

original <- veni1_r$t0
bias <- colMeans(veni1_r$t) - veni1_r$t0
se <- apply(veni1_r$t, 2, sd)

df.veni1 <- data.frame(original=original, bias=bias, se=se)
row.names(df.veni1) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m4", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m4", "AME_netsize_m3a", "AME_netsize_m3b", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m4", "AME_womsv_m3b", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4")

df.veni1$t <- (df.veni1$original / df.veni1$se)

round(df.veni1, 5)

```


Veni within 1 year: logistic

```{r}

veni1_ppf %>%
  group_by(id) %>%
  arrange(desc(year)) %>%
  top_n(1) -> veni1_log


M1 <- glm(formula = veni ~ as.factor(gender_2) + phd_year, family = "binomial", data = veni1_log)
summary(M1)
  
# M2: same as M1 because we don't have extended in the model anymore
# M2 <- glm(formula = veni ~ as.factor(gender_2) + phd_year, family = "binomial", data = veni1_log)
  
M3a <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = "binomial", data = veni1_log)
summary(M3a)

M3b <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = "binomial", data = veni1_log)
summary(M3b)

M3c <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = "binomial", data = veni1_log)
summary(M3c)

M4 <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = "binomial", data = veni1_log)
summary(M4)


```



# Veni between 4-8 years after PhD


```{r}

veni48_ppf %>%
  group_by(id) %>%
  arrange(desc(year)) %>%
  top_n(1) -> veni48_log


M1 <- glm(formula = veni ~ as.factor(gender_2) + phd_year, family = "binomial", data = veni48_log)
summary(M1)
  
# M2: same as M1 because we don't have extended in the model anymore
# M2 <- glm(formula = veni ~ as.factor(gender_2) + phd_year, family = "binomial", data = veni48_log)
  
M3a <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = "binomial", data = veni48_log)
summary(M3a)

M3b <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = "binomial", data = veni48_log)
summary(M3b)

M3c <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = "binomial", data = veni48_log)
summary(M3c)

M4 <- glm(formula = veni ~ as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = "binomial", data = veni48_log)
summary(M4)

```





# Sample without EUR/RUG/TUD/LU


```{r}

summary(as.factor(veni_ppf_r1$uni))

veni_ppf_r1$uni <- factor(veni_ppf_r1$uni, levels=c("RU", "TUE", "TI", "UM", "UT", "UU", "UvA", "VU", "WUR"))

summary(as.factor(veni_ppf_r1$uni))


nrow(veni_ppf_r1[!duplicated(veni_ppf_r1$id),])

summary(as.factor(veni_ppf_r1$veni))


```


AMEs model 1-4

```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2


bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
 M1 <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)

  
  M2 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)


  M4 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
     # extension gender interaction
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    # size * gender datasets
    womennsp <- womennsm <- mennsp <- mennsm <- df
    womennsp$gender_2 <- womennsm$gender_2 <- "women"
    mennsp$gender_2 <- mennsm$gender_2 <- "men"
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    womennsp$teamsize <- mennsp$teamsize <- df$teamsize + s
    womennsm$teamsize <- mennsm$teamsize <- df$teamsize - s
    
    # professors * gender
    womenpp <- womenpm <- menpp <- menpm <- df
    womenpp$gender_2 <- womenpm$gender_2 <- "women"
    menpp$gender_2 <- menpm$gender_2 <- "men"
    womenpp$gender_2 <- factor(womenpp$gender_2, levels=levels(df$gender_2))
    womenpm$gender_2 <- factor(womenpm$gender_2, levels=levels(df$gender_2))
    menpp$gender_2 <- factor(menpp$gender_2, levels=levels(df$gender_2))
    menpm$gender_2 <- factor(menpm$gender_2, levels=levels(df$gender_2))
    menpp$prof2p <- womenpp$prof2p <- 1 
    menpm$prof2p <- womenpm$prof2p <- 0
    
    # woman supervisor * gender
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext1)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext0)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    
    # gender * time
    pwp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene1)))
    pwm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene0)))
    pmp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene1)))
    pmm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene0)))
    AME_gendertime_m2 <- mean(((pwp2 - pmp2) - (pwm2 - pmm2)) / (2*s), na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext1)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext0)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)

    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # gender * time
    pwp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene1)))
    pwm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene0)))
    pmp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene1)))
    pmm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene0)))
    AME_gendertime_m3a <- mean(((pwp3a - pmp3a) - (pwm3a - pmm3a)) / (2*s), na.rm=TRUE)

    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext1)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext0)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # gender * time
    pwp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene1)))
    pwm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene0)))
    pmp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene1)))
    pmm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene0)))
    AME_gendertime_m3b <- mean(((pwp3b - pmp3b) - (pwm3b - pmm3b)) / (2*s), na.rm=TRUE)

    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext1)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext0)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # gender * time
    pwp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene1)))
    pwm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene0)))
    pmp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene1)))
    pmm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene0)))
    AME_gendertime_m3c <- mean(((pwp3c - pmp3c) - (pwm3c - pmm3c)) / (2*s), na.rm=TRUE)

    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext1)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext0)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene0)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene0)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)

    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # size * gender
    wom_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsp)))
    wom_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsm)))
    men_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsp)))
    men_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsm)))
    AME_gendersize_m4 <- mean(((wom_nsp4 - men_nsp4) - (wom_nsm4 - men_nsm4)) / (2*s), na.rm=TRUE)
    
    # prof * gender
    wom_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpp)))
    wom_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpm)))
    men_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpp)))
    men_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpm)))
    AME_genderprof_m4 <- mean(((wom_pp4 - men_pp4) - (wom_pm4 - men_pm4)) / (2*s), na.rm=TRUE)
    
    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)) / (2*s), na.rm=TRUE)
    
    
    # Mediation gender effect from M3A to M3B
    AME_gender_d3ab <- mean((pw3b - pm3b) - (pw3a - pm3a), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_gendertime_m2, AME_gendertime_m3a, AME_gendertime_m3b, AME_gendertime_m3c, AME_gendertime_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_womsv_m3c, AME_womsv_m4, AME_gendersize_m4, AME_genderprof_m4, AME_genderwomsv_m4, AME_gender_d3ab)
   #save results
}

robustness1 <- boot(data=veni_ppf_r1, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(robustness1, file = "robustness1.rda", location = "./results/robustness/")


```

```{r, echo=FALSE}

load("./results/robustness/20240320robustness1.rda")
robustness1 <- x
rm(x)

```


```{r}

original <- robustness1$t0
bias <- colMeans(robustness1$t) - robustness1$t0
se <- apply(robustness1$t, 2, sd)

df.robust1 <- data.frame(original=original, bias=bias, se=se)
row.names(df.robust1) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m3c", "AME_gendertime_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4", "AME_gender_d3ab")

df.robust1$t <- (df.robust1$original / df.robust1$se)

round(df.robust1, 5)

```




# Cohort splits


```{r}

veni_ppf[veni_ppf$veni==1,] -> veni1

summary(veni1$phd_year) # check the distribution of PhD years among Veni recipients

veni_ppf %>% filter(veni_ppf$phd_year<10) -> veni_ppfc1 # 1997-2006
veni_ppf %>% filter(veni_ppf$phd_year>9 & veni_ppf$phd_year<14) -> veni_ppfc2 # 2007-2010
veni_ppf %>% filter(veni_ppf$phd_year>13 & veni_ppf$phd_year<17) -> veni_ppfc3 # 2011-2013
veni_ppf %>% filter(veni_ppf$phd_year>16) -> veni_ppfc4 # 2014-2019


nrow(veni_ppfc1[veni_ppfc1$veni==1,]) / nrow(veni_ppfc1)
nrow(veni_ppfc2[veni_ppfc2$veni==1,]) / nrow(veni_ppfc2)
nrow(veni_ppfc3[veni_ppfc3$veni==1,]) / nrow(veni_ppfc3)
nrow(veni_ppfc4[veni_ppfc4$veni==1,]) / nrow(veni_ppfc4)

```


500 iterations for this check
```{r, eval=FALSE}

# defining some of the key values of the bootstrapping function
nIter <- 500
nCore <- parallel::detectCores() - 2


bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
 M1 <- glm(formula = veni ~ as.factor(extended) + as.factor(gender_2) + phd_year, family = binomial(link="cloglog"), data = df)

  
  M2 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year,
          family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni,
          family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p),
          family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p) + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)


  M4 <- glm(formula = veni ~ as.factor(extended) * as.factor(gender_2) + phd_year + npubs_cumul + npubs_prev + field + uni + gender_2*teamsize + gender_2*as.factor(prof2p) + gender_2*as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- 1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
     # extension gender interaction
    dfwomene1 <- dfwomene0 <- dfmene1 <- dfmene0 <- df
    
    dfwomene1$gender_2 <- dfwomene0$gender_2 <- "women"
    dfmene1$gender_2 <- dfmene0$gender_2 <- "men"
    dfwomene1$gender_2 <- factor(dfwomene1$gender_2, levels=levels(df$gender_2))
    dfwomene0$gender_2 <- factor(dfwomene0$gender_2, levels=levels(df$gender_2))
    dfmene1$gender_2 <- factor(dfmene1$gender_2, levels=levels(df$gender_2))
    dfmene0$gender_2 <- factor(dfmene0$gender_2, levels=levels(df$gender_2))
    
    dfwomene1$extended <- dfmene1$extended <- "after extension"
    dfwomene0$extended <- dfmene0$extended <- "before extension"
    dfwomene1$extended <- factor(dfwomene1$extended, levels=levels(df$extended))
    dfwomene0$extended <- factor(dfwomene0$extended, levels=levels(df$extended))
    dfmene1$extended <- factor(dfmene1$extended, levels=levels(df$extended))
    dfmene0$extended <- factor(dfmene0$extended, levels=levels(df$extended))
    
    # extension main effect
    dfext1 <- dfext0 <- df
    dfext1$extended <- "after extension"
    dfext0$extended <- "before extension"
    dfext1$extended <- factor(dfext1$extended, levels=levels(df$extended))
    dfext0$extended <- factor(dfext0$extended, levels=levels(df$extended))
    
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    # size * gender datasets
    womennsp <- womennsm <- mennsp <- mennsm <- df
    womennsp$gender_2 <- womennsm$gender_2 <- "women"
    mennsp$gender_2 <- mennsm$gender_2 <- "men"
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    womennsp$gender_2 <- factor(womennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    mennsp$gender_2 <- factor(mennsp$gender_2, levels=levels(df$gender_2))
    womennsp$teamsize <- mennsp$teamsize <- df$teamsize + s
    womennsm$teamsize <- mennsm$teamsize <- df$teamsize - s
    
    # professors * gender
    womenpp <- womenpm <- menpp <- menpm <- df
    womenpp$gender_2 <- womenpm$gender_2 <- "women"
    menpp$gender_2 <- menpm$gender_2 <- "men"
    womenpp$gender_2 <- factor(womenpp$gender_2, levels=levels(df$gender_2))
    womenpm$gender_2 <- factor(womenpm$gender_2, levels=levels(df$gender_2))
    menpp$gender_2 <- factor(menpp$gender_2, levels=levels(df$gender_2))
    menpm$gender_2 <- factor(menpm$gender_2, levels=levels(df$gender_2))
    menpp$prof2p <- womenpp$prof2p <- 1 
    menpm$prof2p <- womenpm$prof2p <- 0
    
    # woman supervisor * gender
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    ptp1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext1)))
    ptm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfext0)))
    AME_time_m1 <- mean((ptp1-ptm1) / (2*s), na.rm=TRUE)
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    
    # gender * time
    pwp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene1)))
    pwm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomene0)))
    pmp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene1)))
    pmm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmene0)))
    AME_gendertime_m2 <- mean(((pwp2 - pmp2) - (pwm2 - pmm2)) / (2*s), na.rm=TRUE)
    
    # time
    ptp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext1)))
    ptm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfext0)))
    AME_time_m2 <- mean((ptp2-ptm2) / (2*s), na.rm=TRUE)

    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
    # gender * time
    pwp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene1)))
    pwm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomene0)))
    pmp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene1)))
    pmm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmene0)))
    AME_gendertime_m3a <- mean(((pwp3a - pmp3a) - (pwm3a - pmm3a)) / (2*s), na.rm=TRUE)

    # time
    ptp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext1)))
    ptm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfext0)))
    AME_time_m3a <- mean((ptp3a-ptm3a) / (2*s), na.rm=TRUE)
    
    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # gender * time
    pwp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene1)))
    pwm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomene0)))
    pmp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene1)))
    pmm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmene0)))
    AME_gendertime_m3b <- mean(((pwp3b - pmp3b) - (pwm3b - pmm3b)) / (2*s), na.rm=TRUE)

    # time
    ptp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext1)))
    ptm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfext0)))
    AME_time_m3b <- mean((ptp3b-ptm3b) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # gender * time
    pwp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene1)))
    pwm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomene0)))
    pmp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene1)))
    pmm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmene0)))
    AME_gendertime_m3c <- mean(((pwp3c - pmp3c) - (pwm3c - pmm3c)) / (2*s), na.rm=TRUE)

    # time
    ptp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext1)))
    ptm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfext0)))
    AME_time_m3c <- mean((ptp3c-ptm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene0)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)
    
    
    # gender * time
    pwp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene1)))
    pwm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomene0)))
    pmp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene1)))
    pmm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmene0)))
    AME_gendertime_m4 <- mean(((pwp4 - pmp4) - (pwm4 - pmm4)) / (2*s), na.rm=TRUE)

    # time
    ptp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext1)))
    ptm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfext0)))
    AME_time_m4 <- mean((ptp4-ptm4) / (2*s), na.rm=TRUE)

    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # size * gender
    wom_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsp)))
    wom_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womennsm)))
    men_nsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsp)))
    men_nsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=mennsm)))
    AME_gendersize_m4 <- mean(((wom_nsp4 - men_nsp4) - (wom_nsm4 - men_nsm4)) / (2*s), na.rm=TRUE)
    
    # prof * gender
    wom_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpp)))
    wom_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=womenpm)))
    men_pp4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpp)))
    men_pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=menpm)))
    AME_genderprof_m4 <- mean(((wom_pp4 - men_pp4) - (wom_pm4 - men_pm4)) / (2*s), na.rm=TRUE)
    
    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)) / (2*s), na.rm=TRUE)
    
    
    # Mediation gender effect from M3A to M3B
    AME_gender_d3ab <- mean((pw3b - pm3b) - (pw3a - pm3a), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_gendertime_m2, AME_gendertime_m3a, AME_gendertime_m3b, AME_gendertime_m3c, AME_gendertime_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_womsv_m3c, AME_womsv_m4, AME_gendersize_m4, AME_genderprof_m4, AME_genderwomsv_m4, AME_gender_d3ab)
   #save results
}



# Cohort group 1
robustness3a <- boot(data=veni_ppfc1, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(robustness3a, file = "robustness3a.rda", location = "./results/robustness/")


# Cohort group 2

robustness3b <- boot(data=veni_ppfc2, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(robustness3b, file = "robustness3b.rda", location = "./results/robustness/")

# Cohort group 3

robustness3c <- boot(data=veni_ppfc3, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(robustness3c, file = "robustness3c.rda", location = "./results/robustness/")

# Cohort group 4

robustness3d <- boot(data=veni_ppfc4, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(robustness3d, file = "robustness3d.rda", location = "./results/robustness/")

```


```{r}

load(file="./results/robustness/20240322robustness3a.rda")
robustness3a <- x

load(file="./results/robustness/20240322robustness3b.rda")
robustness3b <- x

load(file="./results/robustness/20240322robustness3c.rda")
robustness3c <- x

load(file="./results/robustness/20240322robustness3d.rda")
robustness3d <- x

```


```{r}

original <- robustness3a$t0
bias <- colMeans(robustness3a$t) - robustness3a$t0
se <- apply(robustness3a$t, 2, sd)

df.robust3a <- data.frame(original=original, bias=bias, se=se)

row.names(df.robust3a) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m3c", "AME_gendertime_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4", "AME_gender_d3ab")

df.robust3a$t <- (df.robust3a$original / df.robust3a$se)

round(df.robust3a, 5)

```


```{r}

original <- robustness3b$t0
bias <- colMeans(robustness3b$t) - robustness3b$t0
se <- apply(robustness3b$t, 2, sd)

df.robust3b <- data.frame(original=original, bias=bias, se=se)


row.names(df.robust3b) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m3c", "AME_gendertime_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4", "AME_gender_d3ab")

df.robust3b$t <- (df.robust3b$original / df.robust3b$se)

round(df.robust3b, 5)

```


```{r}

original <- robustness3c$t0
bias <- colMeans(robustness3c$t) - robustness3c$t0
se <- apply(robustness3c$t, 2, sd)

df.robust3c <- data.frame(original=original, bias=bias, se=se)


row.names(df.robust3c) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m3c", "AME_gendertime_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4", "AME_gender_d3ab")

df.robust3c$t <- (df.robust3c$original / df.robust3c$se)

round(df.robust3c, 5)

```


```{r}

original <- robustness3d$t0
bias <- colMeans(robustness3d$t) - robustness3d$t0
se <- apply(robustness3d$t, 2, sd)

df.robust3d <- data.frame(original=original, bias=bias, se=se)


row.names(df.robust3d) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_time_m1", "AME_time_m2", "AME_time_m3a", "AME_time_m3b", "AME_time_m3c", "AME_time_m4", "AME_gendertime_m2", "AME_gendertime_m3a", "AME_gendertime_m3b", "AME_gendertime_m3c", "AME_gendertime_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_gendersize_m4", "AME_genderprof_m4", "AME_genderwomsv_m4", "AME_gender_d3ab")

df.robust3d$t <- (df.robust3d$original / df.robust3d$se)

round(df.robust3d, 5)

```


