---
title: "Mentoring for gender equality in early-career grant receipt: supplementary analyses"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---

This lab journal details the additional analyses performed to ensure the robustness of our results.  
  
----

# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}



fsave <- function(x, file, location="./data/processed/") {
  datename <- substr(gsub("[:-]", "", Sys.time()), 1,8)
  totalname <- paste(location, datename, file, sep="")
  save(x, file = totalname)
}

# significance stars from the bootstrap t-statistic (original/se), using
# standard normal critical values
sig_stars <- function(t) {
  case_when(
    abs(t) > 3.291 ~ "***",
    abs(t) > 2.576 ~ "**",
    abs(t) > 1.960 ~ "*",
    TRUE ~ ""
  )
}



```

---  

# Packages


- `tidyverse`: For general data manipulation

- `boot`: To create bootstrapped standard errors, following the procedure delineated [here](https://www.jochemtolsma.nl/tutorials/me/)


```{r, results='hide'}
packages = c("tidyverse", "boot", "kableExtra")

fpackage.check(packages)


```

The bootstrap chunks below are gated by a single switch, so a normal knit doesn't accidentally re-trigger a multi-hour bootstrap: keep `RUN_BOOTSTRAPS` at `FALSE` to skip them, or set it to `TRUE` to regenerate the results.

```{r}

RUN_BOOTSTRAPS <- FALSE

```

---


# Input

We use several processed datasets:

* [veni_ppf_r1](data/processed/veni_ppf_r1.rda): 
    - name of dataset: `veni_ppf_r1` 
    - veni_ppf data, but without PhDs who obtained doctorate at EUR, RUG, TUD, LU
    

* [veni_ppf_r2](data/processed/veni_ppf_r2.rda): 
    - name of dataset: `veni_ppf_r2` 
    - veni_ppf data, but with all publishing scholars
    
    
* [veni_ppf](data/processed/veni_ppf.rda): 
    - name of dataset: `veni_ppf` 
    - original veni_ppf data



```{r files, eval=TRUE}

load(file = "data/processed/veni_ppf_r1.rda")

load(file = "data/processed/veni_ppf_r2.rda")

load(file = "data/processed/veni_ppf.rda")

veni_ppf %>%
  distinct(.keep_all=TRUE) -> veni_ppf

```





# Sample without EUR/RUG/TUD/LU


```{r}

summary(as.factor(veni_ppf_r1$uni))

veni_ppf_r1$uni <- factor(veni_ppf_r1$uni, levels=c("RU", "TUE", "TI", "UM", "UT", "UU", "UvA", "VU", "WUR"))

summary(as.factor(veni_ppf_r1$uni))


nrow(veni_ppf_r1[!duplicated(veni_ppf_r1$id),])

summary(as.factor(veni_ppf_r1$veni))


```


AMEs model 1-4

```{r, eval=RUN_BOOTSTRAPS}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) * phd_year + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- .1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    time_levels <- levels(as.factor(df$time))
    ref_time <- "0"
    
    # cohort * gender datasets
    dfwcp <- dfwcm <- dfmcp <- dfmcm <- df
    dfwcp$gender_2 <- dfwcm$gender_2 <- "women"
    dfmcp$gender_2 <- dfmcm$gender_2 <- "men"
    
    dfwcp$gender_2 <- factor(dfwcp$gender_2, levels=levels(df$gender_2))
    dfwcm$gender_2 <- factor(dfwcm$gender_2, levels=levels(df$gender_2))
    dfmcp$gender_2 <- factor(dfmcp$gender_2, levels=levels(df$gender_2))
    dfmcm$gender_2 <- factor(dfmcm$gender_2, levels=levels(df$gender_2))
    
    dfwcp$phd_year <- dfmcp$phd_year <- df$phd_year + s
    dfwcm$phd_year <- dfmcm$phd_year <- df$phd_year - s
    
    # cohort datasets
    dfcp <- dfcm <- df
    dfcp$phd_year <- df$phd_year + s
    dfcm$phd_year <- df$phd_year - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    AME_time_m1 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m1 <- predict(M1, newdata=df_l, type="response")
     pt0m1 <- predict(M1, newdata=df_ref, type="response")
     
     AME_time_m1[level] <- mean(pt1m1 - pt0m1, na.rm=TRUE)
     
    }
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # cohort
    pcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcp)))
    pcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcm)))
    AME_cohort_m2 <- mean(pcp2 - pcm2, na.rm=TRUE)

    # gender * cohort
    pwcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcp)))
    pwcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcm)))
    pmcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcp)))
    pmcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcm)))
    AME_gendercohort_m2 <- mean(((pwcp2 - pmcp2) - (pwcm2 - pmcm2)) / (2*s), na.rm=TRUE)
    
    # time
    AME_time_m2 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m2 <- predict(M2, newdata=df_l, type="response")
     pt0m2 <- predict(M2, newdata=df_ref, type="response")
     
     AME_time_m2[level] <- mean(pt1m2 - pt0m2, na.rm=TRUE)
     
   }
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
   # cohort
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcm)))
    AME_cohort_m3a <- mean(pcp3a - pcm3a, na.rm=TRUE)

    # gender * cohort
    pwcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcp)))
    pwcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcm)))
    pmcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcp)))
    pmcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcm)))
    AME_gendercohort_m3a <- mean(((pwcp3a - pmcp3a) - (pwcm3a - pmcm3a)) / (2*s), na.rm=TRUE)

     # time
    AME_time_m3a <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3a <- predict(M3a, newdata=df_l, type="response")
     pt0m3a <- predict(M3a, newdata=df_ref, type="response")
     
     AME_time_m3a[level] <- mean(pt1m3a - pt0m3a, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # cohort
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcm)))
    AME_cohort_m3b <- mean(pcp3b - pcm3b, na.rm=TRUE)

    # gender * cohort
    pwcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcp)))
    pwcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcm)))
    pmcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcp)))
    pmcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcm)))
    AME_gendercohort_m3b <- mean(((pwcp3b - pmcp3b) - (pwcm3b - pmcm3b)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3b <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3b <- predict(M3b, newdata=df_l, type="response")
     pt0m3b <- predict(M3b, newdata=df_ref, type="response")
     
     AME_time_m3b[level] <- mean(pt1m3b - pt0m3b, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # cohort
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcm)))
    AME_cohort_m3c <- mean(pcp3c - pcm3c, na.rm=TRUE)
    
    # gender * cohort
    pwcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcp)))
    pwcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcm)))
    pmcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcp)))
    pmcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcm)))
    AME_gendercohort_m3c <- mean(((pwcp3c - pmcp3c) - (pwcm3c - pmcm3c)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3c <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3c <- predict(M3c, newdata=df_l, type="response")
     pt0m3c <- predict(M3c, newdata=df_ref, type="response")
     
     AME_time_m3c[level] <- mean(pt1m3c - pt0m3c, na.rm=TRUE)
     
   }
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # cohort
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcm)))
    AME_cohort_m4 <- mean(pcp4 - pcm4, na.rm=TRUE)
    
    # gender * cohort
    pwcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcp)))
    pwcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcm)))
    pmcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcp)))
    pmcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcm)))
    AME_gendercohort_m4 <- mean(((pwcp4 - pmcp4) - (pwcm4 - pmcm4)) / (2*s), na.rm=TRUE)
    
    # time
    AME_time_m4 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m4 <- predict(M4, newdata=df_l, type="response")
     pt0m4 <- predict(M4, newdata=df_ref, type="response")
     
     AME_time_m4[level] <- mean(pt1m4 - pt0m4, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_cohort_m2, AME_cohort_m3a, AME_cohort_m3b, AME_cohort_m3c, AME_cohort_m4, AME_gendercohort_m2, AME_gendercohort_m3a, AME_gendercohort_m3b, AME_gendercohort_m3c, AME_gendercohort_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_r1, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "uni_sel.rda", location = "./results/robustness/")


```

```{r, echo=FALSE}

load("./results/robustness/20260823uni_sel.rda")
uni_sel <- x
rm(x)

```


```{r}

original <- uni_sel$t0
bias <- colMeans(uni_sel$t) - uni_sel$t0
se <- apply(uni_sel$t, 2, sd)

df.uni_sel <- data.frame(original=original, bias=bias, se=se)
row.names(df.uni_sel) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1_0", "AME_time_m1_1", "AME_time_m1_2", "AME_time_m1_3", "AME_time_m1_4", "AME_time_m1_5", "AME_time_m1_6", "AME_time_m1_7", "AME_time_m1_8", "AME_time_m2_0", "AME_time_m2_1", "AME_time_m2_2", "AME_time_m2_3", "AME_time_m2_4", "AME_time_m2_5", "AME_time_m2_6", "AME_time_m2_7", "AME_time_m2_8", "AME_time_m3a_0", "AME_time_m3a_1", "AME_time_m3a_2", "AME_time_m3a_3", "AME_time_m3a_4", "AME_time_m3a_5", "AME_time_m3a_6", "AME_time_m3a_7", "AME_time_m3a_8", "AME_time_m3b_0", "AME_time_m3b_1", "AME_time_m3b_2", "AME_time_m3b_3", "AME_time_m3b_4", "AME_time_m3b_5", "AME_time_m3b_6", "AME_time_m3b_7", "AME_time_m3b_8", "AME_time_m3c_0", "AME_time_m3c_1", "AME_time_m3c_2", "AME_time_m3c_3", "AME_time_m3c_4", "AME_time_m3c_5", "AME_time_m3c_6", "AME_time_m3c_7", "AME_time_m3c_8", "AME_time_m4_0", "AME_time_m4_1", "AME_time_m4_2", "AME_time_m4_3", "AME_time_m4_4", "AME_time_m4_5", "AME_time_m4_6", "AME_time_m4_7", "AME_time_m4_8", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")

df.uni_sel$t <- (df.uni_sel$original / df.uni_sel$se)

# remove the time=0 rows, as 0 is the reference category for time
rows_to_remove <- grep("^AME_time_m(1|2|3a|3b|3c|4)_0$", rownames(df.uni_sel))
df.uni_sel <- df.uni_sel[-rows_to_remove, ]

round(df.uni_sel, 5)

```


## Table of AMEs

```{r}

# Creating neat labels
table_ames_unisel <- df.uni_sel %>%
  mutate(term = rownames(df.uni_sel),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m[1-4][abc]?")) %>%
  mutate(model = recode(model,
                        "m1" = "M1",
                        "m2" = "M2",
                        "m3a" = "M3",
                        "m3b" = "M4",
                        "m3c" = "M5",
                        "m4" = "M6"),
         model = factor(model, levels = paste0("M", 1:6))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "genderwomsv") ~ "Women supervisors * Woman",
    str_detect(term, "gender") ~ "Woman",
    str_detect(term, "time") ~ paste0("Time since PhD: ", str_extract(term, "[:digit:]$"), " years"),
    str_detect(term, "cohort") ~ "PhD cohort",
    str_detect(term, "womsv") ~ "Women supervisors",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "netsize") ~ "Team size",
    str_detect(term, "prof") ~ "2+ professors",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)%s", original, se, sig_stars(t))) %>%
  select(label, model, value)

# correct table ordering
rows_tab <- c("Woman", "Time since PhD: 1 years", "Time since PhD: 2 years", "Time since PhD: 3 years", "Time since PhD: 4 years", "Time since PhD: 5 years", "Time since PhD: 6 years", "Time since PhD: 7 years", "Time since PhD: 8 years", "PhD cohort", "PhD cohort * Woman", "Cumulative publications", "Previous publications", "Team size", "2+ professors", "Supervisors' productivity", "Women supervisors", "Women supervisors * Woman")


# Reshape to wide format
table_df_unisel <- table_ames_unisel %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab)) %>%
  arrange(label)

# Replace NA values (not in the model) with empty strings
table_df_unisel[is.na(table_df_unisel)] <- ""

# Create pretty table
kable(table_df_unisel, "html", escape = FALSE, align = "lcccccc",
      col.names = c("", paste0("M", 1:6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt (sample without EUR/RUG/TUD/LU)" = 6)) %>%
  footnote(general = "* p < .05, ** p < .01, *** p < .001 (based on the bootstrap t-statistic)",
           general_title = "")


```





# Sample with all Veni's awarded to scholars with a NARCIS profile



```{r}

nrow(veni_ppf_r2[!duplicated(veni_ppf_r2$id),])

summary(as.factor(veni_ppf_r2$veni))


```


AMEs model 1-4

```{r, eval=RUN_BOOTSTRAPS}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets
  
  M1 <- glm(formula = veni ~ as.factor(gender_2) + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M2 <- glm(formula = veni ~ as.factor(gender_2) * phd_year + as.factor(time), family = binomial(link="cloglog"), data = df)
  
  M3a <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni, family = binomial(link="cloglog"), data = df)
  
  M3b <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + teamsize + as.factor(prof2p) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)
  
  M3c <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1), family = binomial(link="cloglog"), data = df)
  
  M4 <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + teamsize + as.factor(prof2p)  + npubs_sv_norm + as.factor(wom_sv1)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)
  

    suppressWarnings({
  
    # CREATING THE DATASETS
    
    s <- .1
    
    # gender datasets  
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women" # one dataset of all women
    dfmen$gender_2 <- "men" # one dataset of all men
    
    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))
    
    # time datasets
    time_levels <- levels(as.factor(df$time))
    ref_time <- "0"
    
    # cohort * gender datasets
    dfwcp <- dfwcm <- dfmcp <- dfmcm <- df
    dfwcp$gender_2 <- dfwcm$gender_2 <- "women"
    dfmcp$gender_2 <- dfmcm$gender_2 <- "men"
    
    dfwcp$gender_2 <- factor(dfwcp$gender_2, levels=levels(df$gender_2))
    dfwcm$gender_2 <- factor(dfwcm$gender_2, levels=levels(df$gender_2))
    dfmcp$gender_2 <- factor(dfmcp$gender_2, levels=levels(df$gender_2))
    dfmcm$gender_2 <- factor(dfmcm$gender_2, levels=levels(df$gender_2))
    
    dfwcp$phd_year <- dfmcp$phd_year <- df$phd_year + s
    dfwcm$phd_year <- dfmcm$phd_year <- df$phd_year - s
    
    # cohort datasets
    dfcp <- dfcm <- df
    dfcp$phd_year <- df$phd_year + s
    dfcm$phd_year <- df$phd_year - s
    
    # cumulative pubs
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s
    
    # previous pubs
    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s
    
    # network size datasets
    dfnsp <- dfnsm <- df
    dfnsp$teamsize <- dfnsp$teamsize + s
    dfnsm$teamsize <- dfnsm$teamsize - s
    
    # professor datasets
    dfprof <- dfnoprof <- df
    dfprof$prof2p <- 1 
    dfnoprof$prof2p <- 0
    
     # pubs supervisor datasets
    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s
    
    # women sv datasets
    dfws <- dfms <- df
    dfws$wom_sv1 <- "1+ woman"
    dfms$wom_sv1 <- "no women"
    dfws$wom_sv1 <- factor(dfws$wom_sv1, levels=levels(df$wom_sv1))
    dfms$wom_sv1 <- factor(dfms$wom_sv1, levels=levels(df$wom_sv1))
    
    
    # woman supervisor * gender datasets
    dfwnows <- dfwws <- dfmnows <- dfmws <- df
    dfwnows$gender_2 <- dfwws$gender_2 <- "women"
    dfmnows$gender_2 <- dfmws$gender_2 <- "men"
    dfwnows$gender_2 <- factor(dfwnows$gender_2, levels=levels(df$gender_2))
    dfwws$gender_2 <- factor(dfwws$gender_2, levels=levels(df$gender_2))
    dfmnows$gender_2 <- factor(dfmnows$gender_2, levels=levels(df$gender_2))
    dfmws$gender_2 <- factor(dfmws$gender_2, levels=levels(df$gender_2))
    dfwws$wom_sv1 <- dfmws$wom_sv1 <- "1+ woman"
    dfwnows$wom_sv1 <- dfmnows$wom_sv1 <- "no women"
    dfwws$wom_sv1 <- factor(dfwws$wom_sv1, levels=levels(df$wom_sv1))
    dfwnows$wom_sv1 <- factor(dfwnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmnows$wom_sv1 <- factor(dfmnows$wom_sv1, levels=levels(df$wom_sv1))
    dfmws$wom_sv1 <- factor(dfmws$wom_sv1, levels=levels(df$wom_sv1))
    
    
      
    # MODEL 1  
    
    # gender
    pw1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfwomen)))
    pm1 <- as.numeric(unlist(predict(M1, type="response", newdata=dfmen)))
    AME_gender_m1 <- mean(pw1 - pm1, na.rm=TRUE)
    
    # time
    AME_time_m1 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m1 <- predict(M1, newdata=df_l, type="response")
     pt0m1 <- predict(M1, newdata=df_ref, type="response")
     
     AME_time_m1[level] <- mean(pt1m1 - pt0m1, na.rm=TRUE)
     
    }
    
    
    # MODEL 2
    
    # gender 
    pw2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwomen)))
    pm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmen)))
    AME_gender_m2 <- mean(pw2 - pm2, na.rm=TRUE)
    
    # cohort
    pcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcp)))
    pcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfcm)))
    AME_cohort_m2 <- mean(pcp2 - pcm2, na.rm=TRUE)

    # gender * cohort
    pwcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcp)))
    pwcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfwcm)))
    pmcp2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcp)))
    pmcm2 <- as.numeric(unlist(predict(M2, type="response", newdata=dfmcm)))
    AME_gendercohort_m2 <- mean(((pwcp2 - pmcp2) - (pwcm2 - pmcm2)) / (2*s), na.rm=TRUE)
    
    # time
    AME_time_m2 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m2 <- predict(M2, newdata=df_l, type="response")
     pt0m2 <- predict(M2, newdata=df_ref, type="response")
     
     AME_time_m2[level] <- mean(pt1m2 - pt0m2, na.rm=TRUE)
     
   }
    
    
    # MODEL 3A
    
    # gender
    pw3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwomen)))
    pm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmen)))
    AME_gender_m3a <- mean(pw3a - pm3a, na.rm=TRUE)
    
   # cohort
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfcm)))
    AME_cohort_m3a <- mean(pcp3a - pcm3a, na.rm=TRUE)

    # gender * cohort
    pwcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcp)))
    pwcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfwcm)))
    pmcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcp)))
    pmcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfmcm)))
    AME_gendercohort_m3a <- mean(((pwcp3a - pmcp3a) - (pwcm3a - pmcm3a)) / (2*s), na.rm=TRUE)

     # time
    AME_time_m3a <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3a <- predict(M3a, newdata=df_l, type="response")
     pt0m3a <- predict(M3a, newdata=df_ref, type="response")
     
     AME_time_m3a[level] <- mean(pt1m3a - pt0m3a, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcp)))
    pcm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfpcm)))
    AME_cpubs_m3a <- mean((pcp3a-pcm3a) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppp)))
    ppm3a <- as.numeric(unlist(predict(M3a, type="response", newdata=dfppm)))
    AME_ppubs_m3a <- mean((ppp3a-ppm3a) / (2*s), na.rm=TRUE)

    
    # MODEL 3B
    
    # gender
    pw3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmen)))
    AME_gender_m3b <- mean(pw3b - pm3b, na.rm=TRUE)
    
    # cohort
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfcm)))
    AME_cohort_m3b <- mean(pcp3b - pcm3b, na.rm=TRUE)

    # gender * cohort
    pwcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcp)))
    pwcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfwcm)))
    pmcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcp)))
    pmcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfmcm)))
    AME_gendercohort_m3b <- mean(((pwcp3b - pmcp3b) - (pwcm3b - pmcm3b)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3b <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3b <- predict(M3b, newdata=df_l, type="response")
     pt0m3b <- predict(M3b, newdata=df_ref, type="response")
     
     AME_time_m3b[level] <- mean(pt1m3b - pt0m3b, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcp)))
    pcm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfpcm)))
    AME_cpubs_m3b <- mean((pcp3b-pcm3b) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppp)))
    ppm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfppm)))
    AME_ppubs_m3b <- mean((ppp3b-ppm3b) / (2*s), na.rm=TRUE)
    
    # network size
    pnsp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsp)))
    pnsm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnsm)))
    AME_netsize_m3b <- mean((pnsp3b-pnsm3b) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfprof)))
    noprof3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfnoprof)))
    AME_prof_m3b <- mean(prof3b - noprof3b, na.rm=TRUE)
    
    # sv pubs 
    spp3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b, type="response", newdata=dfspm)))
    AME_svpubs_m3b <- mean((spp3b-spm3b) / (2*s), na.rm=TRUE)
    

    # MODEL 3C
    
    # gender
    pw3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmen)))
    AME_gender_m3c <- mean(pw3c - pm3c, na.rm=TRUE)
    
    # cohort
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfcm)))
    AME_cohort_m3c <- mean(pcp3c - pcm3c, na.rm=TRUE)
    
    # gender * cohort
    pwcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcp)))
    pwcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfwcm)))
    pmcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcp)))
    pmcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfmcm)))
    AME_gendercohort_m3c <- mean(((pwcp3c - pmcp3c) - (pwcm3c - pmcm3c)) / (2*s), na.rm=TRUE)

    # time
    AME_time_m3c <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m3c <- predict(M3c, newdata=df_l, type="response")
     pt0m3c <- predict(M3c, newdata=df_ref, type="response")
     
     AME_time_m3c[level] <- mean(pt1m3c - pt0m3c, na.rm=TRUE)
     
   }
    
    
    # cumulative pubs
    pcp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcp)))
    pcm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfpcm)))
    AME_cpubs_m3c <- mean((pcp3c-pcm3c) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppp)))
    ppm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfppm)))
    AME_ppubs_m3c <- mean((ppp3c-ppm3c) / (2*s), na.rm=TRUE)
    
     # network size
    pnsp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsp)))
    pnsm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnsm)))
    AME_netsize_m3c <- mean((pnsp3c-pnsm3c) / (2*s), na.rm=TRUE)
    
    # professors 
    prof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfprof)))
    noprof3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfnoprof)))
    AME_prof_m3c <- mean(prof3c - noprof3c, na.rm=TRUE)
    
    # sv pubs 
    spp3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfspm)))
    AME_svpubs_m3c <- mean((spp3c-spm3c) / (2*s), na.rm=TRUE)

    # women supervisors
    ws3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfws)))
    ms3c <- as.numeric(unlist(predict(M3c, type="response", newdata=dfms)))
    AME_womsv_m3c <- mean(ws3c - ms3c, na.rm=TRUE)
    
    
    # MODEL 4
    pw4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmen)))
    AME_gender_m4 <- mean(pw4 - pm4, na.rm=TRUE)
    
    # cohort
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfcm)))
    AME_cohort_m4 <- mean(pcp4 - pcm4, na.rm=TRUE)
    
    # gender * cohort
    pwcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcp)))
    pwcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwcm)))
    pmcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcp)))
    pmcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmcm)))
    AME_gendercohort_m4 <- mean(((pwcp4 - pmcp4) - (pwcm4 - pmcm4)) / (2*s), na.rm=TRUE)
    
    # time
    AME_time_m4 <- c()
    
    for (level in time_levels) {
     df_l <- df
     df_l$time <- factor(level, levels=time_levels)
     
     df_ref <- df
     df_ref$time <- factor(ref_time, levels=time_levels)
     
     pt1m4 <- predict(M4, newdata=df_l, type="response")
     pt0m4 <- predict(M4, newdata=df_ref, type="response")
     
     AME_time_m4[level] <- mean(pt1m4 - pt0m4, na.rm=TRUE)
     
   }
    
    # cumulative pubs
    pcp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcp)))
    pcm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfpcm)))
    AME_cpubs_m4 <- mean((pcp4-pcm4) / (2*s), na.rm=TRUE)
  
    # pubs previous year
    ppp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppp)))
    ppm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfppm)))
    AME_ppubs_m4 <- mean((ppp4-ppm4) / (2*s), na.rm=TRUE)
   
    # network size
    pnsp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsp)))
    pnsm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnsm)))
    AME_netsize_m4 <- mean((pnsp4-pnsm4) / (2*s), na.rm=TRUE)
    
    # professors 
    prof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfprof)))
    noprof4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfnoprof)))
    AME_prof_m4 <- mean(prof4 - noprof4, na.rm=TRUE)
    
    # sv pubs 
    spp4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfspm)))
    AME_svpubs_m4 <- mean((spp4-spm4) / (2*s), na.rm=TRUE)
    
    # women supervisors
    ws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfws)))
    ms4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfms)))
    AME_womsv_m4 <- mean(ws4 - ms4, na.rm=TRUE)

    # women supervisors * gender_2
    womnows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwnows)))
    womws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfwws)))
    mennows4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmnows)))
    menws4 <- as.numeric(unlist(predict(M4, type="response", newdata=dfmws)))
    AME_genderwomsv_m4 <- mean(((womws4 - menws4) - (womnows4 - mennows4)), na.rm=TRUE)

    })
  
  c(AME_gender_m1, AME_gender_m2, AME_gender_m3a, AME_gender_m3b, AME_gender_m3c, AME_gender_m4, AME_cohort_m2, AME_cohort_m3a, AME_cohort_m3b, AME_cohort_m3c, AME_cohort_m4, AME_gendercohort_m2, AME_gendercohort_m3a, AME_gendercohort_m3b, AME_gendercohort_m3c, AME_gendercohort_m4, AME_time_m1, AME_time_m2, AME_time_m3a, AME_time_m3b, AME_time_m3c, AME_time_m4, AME_cpubs_m3a, AME_cpubs_m3b, AME_cpubs_m3c, AME_cpubs_m4, AME_ppubs_m3a, AME_ppubs_m3b, AME_ppubs_m3c, AME_ppubs_m4, AME_netsize_m3b, AME_netsize_m3c, AME_netsize_m4, AME_prof_m3b, AME_prof_m3c, AME_prof_m4, AME_svpubs_m3b, AME_svpubs_m3c, AME_svpubs_m4, AME_womsv_m3c, AME_womsv_m4, AME_genderwomsv_m4)
   #save results
}


AMEs <- boot(data=veni_ppf_r2, bootFunc, R = nIter, parallel="snow", ncpus=nCore)


fsave(AMEs, file = "allphds.rda", location = "./results/robustness/")


```

```{r, echo=FALSE}

load("./results/robustness/20260823allphds.rda")
allphds <- x
rm(x)

```


```{r}

original <- allphds$t0
bias <- colMeans(allphds$t) - allphds$t0
se <- apply(allphds$t, 2, sd)

df.allphds <- data.frame(original=original, bias=bias, se=se)
row.names(df.allphds) <- c("AME_gender_m1", "AME_gender_m2", "AME_gender_m3a", "AME_gender_m3b", "AME_gender_m3c", "AME_gender_m4", "AME_cohort_m2", "AME_cohort_m3a", "AME_cohort_m3b", "AME_cohort_m3c", "AME_cohort_m4", "AME_gendercohort_m2", "AME_gendercohort_m3a", "AME_gendercohort_m3b", "AME_gendercohort_m3c", "AME_gendercohort_m4", "AME_time_m1_0", "AME_time_m1_1", "AME_time_m1_2", "AME_time_m1_3", "AME_time_m1_4", "AME_time_m1_5", "AME_time_m1_6", "AME_time_m1_7", "AME_time_m1_8", "AME_time_m2_0", "AME_time_m2_1", "AME_time_m2_2", "AME_time_m2_3", "AME_time_m2_4", "AME_time_m2_5", "AME_time_m2_6", "AME_time_m2_7", "AME_time_m2_8", "AME_time_m3a_0", "AME_time_m3a_1", "AME_time_m3a_2", "AME_time_m3a_3", "AME_time_m3a_4", "AME_time_m3a_5", "AME_time_m3a_6", "AME_time_m3a_7", "AME_time_m3a_8", "AME_time_m3b_0", "AME_time_m3b_1", "AME_time_m3b_2", "AME_time_m3b_3", "AME_time_m3b_4", "AME_time_m3b_5", "AME_time_m3b_6", "AME_time_m3b_7", "AME_time_m3b_8", "AME_time_m3c_0", "AME_time_m3c_1", "AME_time_m3c_2", "AME_time_m3c_3", "AME_time_m3c_4", "AME_time_m3c_5", "AME_time_m3c_6", "AME_time_m3c_7", "AME_time_m3c_8", "AME_time_m4_0", "AME_time_m4_1", "AME_time_m4_2", "AME_time_m4_3", "AME_time_m4_4", "AME_time_m4_5", "AME_time_m4_6", "AME_time_m4_7", "AME_time_m4_8", "AME_cpubs_m3a", "AME_cpubs_m3b", "AME_cpubs_m3c", "AME_cpubs_m4", "AME_ppubs_m3a", "AME_ppubs_m3b", "AME_ppubs_m3c", "AME_ppubs_m4", "AME_netsize_m3b", "AME_netsize_m3c", "AME_netsize_m4", "AME_prof_m3b", "AME_prof_m3c", "AME_prof_m4", "AME_svpubs_m3b", "AME_svpubs_m3c", "AME_svpubs_m4", "AME_womsv_m3c", "AME_womsv_m4", "AME_genderwomsv_m4")


df.allphds$t <- (df.allphds$original / df.allphds$se)

# remove the time=0 rows, as 0 is the reference category for time
rows_to_remove <- grep("^AME_time_m(1|2|3a|3b|3c|4)_0$", rownames(df.allphds))
df.allphds <- df.allphds[-rows_to_remove, ]

round(df.allphds, 5)

```



## Table of AMEs

```{r}

# Creating neat labels
table_ames_allphds <- df.allphds %>%
  mutate(term = rownames(df.allphds),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m[1-4][abc]?")) %>%
  mutate(model = recode(model,
                        "m1" = "M1",
                        "m2" = "M2",
                        "m3a" = "M3",
                        "m3b" = "M4",
                        "m3c" = "M5",
                        "m4" = "M6"),
         model = factor(model, levels = paste0("M", 1:6))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "genderwomsv") ~ "Women supervisors * Woman",
    str_detect(term, "gender") ~ "Woman",
    str_detect(term, "time") ~ paste0("Time since PhD: ", str_extract(term, "[:digit:]$"), " years"),
    str_detect(term, "cohort") ~ "PhD cohort",
    str_detect(term, "womsv") ~ "Women supervisors",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "netsize") ~ "Team size",
    str_detect(term, "prof") ~ "2+ professors",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)%s", original, se, sig_stars(t))) %>%
  select(label, model, value)

# correct table ordering
rows_tab <- c("Woman", "Time since PhD: 1 years", "Time since PhD: 2 years", "Time since PhD: 3 years", "Time since PhD: 4 years", "Time since PhD: 5 years", "Time since PhD: 6 years", "Time since PhD: 7 years", "Time since PhD: 8 years", "PhD cohort", "PhD cohort * Woman", "Cumulative publications", "Previous publications", "Team size", "2+ professors", "Supervisors' productivity", "Women supervisors", "Women supervisors * Woman")


# Reshape to wide format
table_df_allphds <- table_ames_allphds %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab)) %>%
  arrange(label)

# Replace NA values (not in the model) with empty strings
table_df_allphds[is.na(table_df_allphds)] <- ""

# Create pretty table
kable(table_df_allphds, "html", escape = FALSE, align = "lcccccc",
      col.names = c("", paste0("M", 1:6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt (sample including non-publishing scholars )" = 6)) %>%
  footnote(general = "* p < .05, ** p < .01, *** p < .001 (based on the bootstrap t-statistic)",
           general_title = "")

```


# Combined supervision-team variables

We re-estimate the models that include supervision-team predictors (M4/M5/M6, i.e. M3b/M3c/M4 below) replacing the separate `teamsize` + `as.factor(prof2p)` + `as.factor(wom_sv1)` predictors with the two combined variables `team_prof_size` (team size x number of professors) and `team_gender_prof` (women in team x professor status), built in `supervisors.Rmd`.

```{r, eval=RUN_BOOTSTRAPS}

# defining some of the key values of the bootstrapping function
nIter <- 1000
nCore <- parallel::detectCores() - 2

bootFunc <- function(data, i) {
  df <- data[i,] #bootstrap datasets

  M3b_tc <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + as.factor(uni) + as.factor(team_prof_size) + npubs_sv_norm, family = binomial(link="cloglog"), data = df)

  M3c_tc <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + as.factor(team_prof_size) + npubs_sv_norm + as.factor(team_gender_prof), family = binomial(link="cloglog"), data = df)

  M4_tc <- glm(formula = veni ~ phd_year * as.factor(gender_2) + as.factor(time) + npubs_cumul + npubs_prev + field + uni + as.factor(team_prof_size) + npubs_sv_norm + as.factor(team_gender_prof)*as.factor(gender_2), family = binomial(link="cloglog"), data = df)


    suppressWarnings({

    # CREATING THE DATASETS

    s <- .1

    # gender datasets
    dfmen <- dfwomen <- df
    dfwomen$gender_2 <- "women"
    dfmen$gender_2 <- "men"

    dfwomen$gender_2 <- factor(dfwomen$gender_2, levels=levels(df$gender_2))
    dfmen$gender_2 <- factor(dfmen$gender_2, levels=levels(df$gender_2))

    # cohort * gender datasets
    dfwcp <- dfwcm <- dfmcp <- dfmcm <- df
    dfwcp$gender_2 <- dfwcm$gender_2 <- "women"
    dfmcp$gender_2 <- dfmcm$gender_2 <- "men"

    dfwcp$gender_2 <- factor(dfwcp$gender_2, levels=levels(df$gender_2))
    dfwcm$gender_2 <- factor(dfwcm$gender_2, levels=levels(df$gender_2))
    dfmcp$gender_2 <- factor(dfmcp$gender_2, levels=levels(df$gender_2))
    dfmcm$gender_2 <- factor(dfmcm$gender_2, levels=levels(df$gender_2))

    dfwcp$phd_year <- dfmcp$phd_year <- df$phd_year + s
    dfwcm$phd_year <- dfmcm$phd_year <- df$phd_year - s

    # cohort datasets
    dfcp <- dfcm <- df
    dfcp$phd_year <- df$phd_year + s
    dfcm$phd_year <- df$phd_year - s

    # cumulative pubs / previous pubs / supervisor pubs datasets
    dfpcp <- dfpcm <- df
    dfpcp$npubs_cumul <- df$npubs_cumul + s
    dfpcm$npubs_cumul <- df$npubs_cumul - s

    dfppp <- dfppm <- df
    dfppp$npubs_prev <- df$npubs_prev + s
    dfppm$npubs_prev <- df$npubs_prev - s

    dfspp <- dfspm <- df
    dfspp$npubs_sv_norm <- dfspp$npubs_sv_norm + s
    dfspm$npubs_sv_norm <- dfspm$npubs_sv_norm - s

    # team composition counterfactual datasets: one level set for everyone,
    # vs. the reference level set for everyone, for each non-reference level
    team_prof_ref    <- "1 professor"
    team_prof_levels <- c("2 professors", "1 professor, 1 non-professor", "3 professors",
                           "2 professors, 1 non-professor", "1 professor, 2 non-professors",
                           "4-6 team, majority professors", "4-6 team, minority professors", "7+ team")

    team_gender_ref    <- "no women supervisors"
    team_gender_levels <- c("1+ woman (no professor)", "1+ woman professor")

    ame_level_vs_ref <- function(model, varname, level, ref) {
      d_level <- df; d_level[[varname]] <- level
      d_ref   <- df; d_ref[[varname]]   <- ref
      mean(predict(model, newdata = d_level, type = "response") -
           predict(model, newdata = d_ref,   type = "response"), na.rm = TRUE)
    }

    # MODEL 3B_TC (team_prof_size only)

    pw3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfwomen)))
    pm3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfmen)))
    AME_gender_m3b_tc <- mean(pw3b - pm3b, na.rm=TRUE)

    pcp3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfcp)))
    pcm3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfcm)))
    AME_cohort_m3b_tc <- mean(pcp3b - pcm3b, na.rm=TRUE)

    pwcp3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfwcp)))
    pwcm3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfwcm)))
    pmcp3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfmcp)))
    pmcm3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfmcm)))
    AME_gendercohort_m3b_tc <- mean(((pwcp3b - pmcp3b) - (pwcm3b - pmcm3b)) / (2*s), na.rm=TRUE)

    pcpc3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfpcp)))
    pcmc3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfpcm)))
    AME_cpubs_m3b_tc <- mean((pcpc3b - pcmc3b) / (2*s), na.rm=TRUE)

    pppp3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfppp)))
    pppm3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfppm)))
    AME_ppubs_m3b_tc <- mean((pppp3b - pppm3b) / (2*s), na.rm=TRUE)

    spp3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfspp)))
    spm3b <- as.numeric(unlist(predict(M3b_tc, type="response", newdata=dfspm)))
    AME_svpubs_m3b_tc <- mean((spp3b - spm3b) / (2*s), na.rm=TRUE)

    AME_teamprof_m3b_tc <- sapply(team_prof_levels, function(l) ame_level_vs_ref(M3b_tc, "team_prof_size", l, team_prof_ref))

    # MODEL 3C_TC (team_prof_size + team_gender_prof)

    pw3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfwomen)))
    pm3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfmen)))
    AME_gender_m3c_tc <- mean(pw3c - pm3c, na.rm=TRUE)

    pcp3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfcp)))
    pcm3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfcm)))
    AME_cohort_m3c_tc <- mean(pcp3c - pcm3c, na.rm=TRUE)

    pwcp3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfwcp)))
    pwcm3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfwcm)))
    pmcp3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfmcp)))
    pmcm3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfmcm)))
    AME_gendercohort_m3c_tc <- mean(((pwcp3c - pmcp3c) - (pwcm3c - pmcm3c)) / (2*s), na.rm=TRUE)

    pcpc3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfpcp)))
    pcmc3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfpcm)))
    AME_cpubs_m3c_tc <- mean((pcpc3c - pcmc3c) / (2*s), na.rm=TRUE)

    pppp3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfppp)))
    pppm3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfppm)))
    AME_ppubs_m3c_tc <- mean((pppp3c - pppm3c) / (2*s), na.rm=TRUE)

    spp3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfspp)))
    spm3c <- as.numeric(unlist(predict(M3c_tc, type="response", newdata=dfspm)))
    AME_svpubs_m3c_tc <- mean((spp3c - spm3c) / (2*s), na.rm=TRUE)

    AME_teamprof_m3c_tc <- sapply(team_prof_levels, function(l) ame_level_vs_ref(M3c_tc, "team_prof_size", l, team_prof_ref))
    AME_teamgender_m3c_tc <- sapply(team_gender_levels, function(l) ame_level_vs_ref(M3c_tc, "team_gender_prof", l, team_gender_ref))

    # MODEL 4_TC (team_prof_size * gender + team_gender_prof)

    pw4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfwomen)))
    pm4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfmen)))
    AME_gender_m4_tc <- mean(pw4 - pm4, na.rm=TRUE)

    pcp4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfcp)))
    pcm4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfcm)))
    AME_cohort_m4_tc <- mean(pcp4 - pcm4, na.rm=TRUE)

    pwcp4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfwcp)))
    pwcm4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfwcm)))
    pmcp4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfmcp)))
    pmcm4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfmcm)))
    AME_gendercohort_m4_tc <- mean(((pwcp4 - pmcp4) - (pwcm4 - pmcm4)) / (2*s), na.rm=TRUE)

    pcpc4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfpcp)))
    pcmc4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfpcm)))
    AME_cpubs_m4_tc <- mean((pcpc4 - pcmc4) / (2*s), na.rm=TRUE)

    pppp4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfppp)))
    pppm4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfppm)))
    AME_ppubs_m4_tc <- mean((pppp4 - pppm4) / (2*s), na.rm=TRUE)

    spp4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfspp)))
    spm4 <- as.numeric(unlist(predict(M4_tc, type="response", newdata=dfspm)))
    AME_svpubs_m4_tc <- mean((spp4 - spm4) / (2*s), na.rm=TRUE)

    AME_teamprof_m4_tc <- sapply(team_prof_levels, function(l) ame_level_vs_ref(M4_tc, "team_prof_size", l, team_prof_ref))
    AME_teamgender_m4_tc <- sapply(team_gender_levels, function(l) ame_level_vs_ref(M4_tc, "team_gender_prof", l, team_gender_ref))

    })

  c(AME_gender_m3b_tc, AME_gender_m3c_tc, AME_gender_m4_tc,
    AME_cohort_m3b_tc, AME_cohort_m3c_tc, AME_cohort_m4_tc,
    AME_gendercohort_m3b_tc, AME_gendercohort_m3c_tc, AME_gendercohort_m4_tc,
    AME_cpubs_m3b_tc, AME_cpubs_m3c_tc, AME_cpubs_m4_tc,
    AME_ppubs_m3b_tc, AME_ppubs_m3c_tc, AME_ppubs_m4_tc,
    AME_svpubs_m3b_tc, AME_svpubs_m3c_tc, AME_svpubs_m4_tc,
    AME_teamprof_m3b_tc, AME_teamprof_m3c_tc, AME_teamprof_m4_tc,
    AME_teamgender_m3c_tc, AME_teamgender_m4_tc)
}


AMEs <- boot(data=veni_ppf, bootFunc, R = nIter, parallel="snow", ncpus=nCore)

fsave(AMEs, file = "teamcomp.rda", location = "./results/robustness/")

```

```{r, echo=FALSE}

load("./results/robustness/20260823teamcomp.rda")
teamcomp <- x
rm(x)

```

```{r}

original <- teamcomp$t0
bias <- colMeans(teamcomp$t) - teamcomp$t0
se <- apply(teamcomp$t, 2, sd)

df.teamcomp <- data.frame(original=original, bias=bias, se=se)

# must match the exact order bootFunc returns its vector in
team_prof_slugs   <- c("2profs", "1prof1nonprof", "3profs", "2profs1nonprof", "1prof2nonprofs", "4to6majority", "4to6minority", "7plusteam")
team_gender_slugs <- c("womNoProf", "womProf")

row.names(df.teamcomp) <- c(
  "AME_gender_m3b_tc", "AME_gender_m3c_tc", "AME_gender_m4_tc",
  "AME_cohort_m3b_tc", "AME_cohort_m3c_tc", "AME_cohort_m4_tc",
  "AME_gendercohort_m3b_tc", "AME_gendercohort_m3c_tc", "AME_gendercohort_m4_tc",
  "AME_cpubs_m3b_tc", "AME_cpubs_m3c_tc", "AME_cpubs_m4_tc",
  "AME_ppubs_m3b_tc", "AME_ppubs_m3c_tc", "AME_ppubs_m4_tc",
  "AME_svpubs_m3b_tc", "AME_svpubs_m3c_tc", "AME_svpubs_m4_tc",
  paste0("AME_teamprof_", team_prof_slugs, "_m3b_tc"),
  paste0("AME_teamprof_", team_prof_slugs, "_m3c_tc"),
  paste0("AME_teamprof_", team_prof_slugs, "_m4_tc"),
  paste0("AME_teamgender_", team_gender_slugs, "_m3c_tc"),
  paste0("AME_teamgender_", team_gender_slugs, "_m4_tc")
)

df.teamcomp$t <- (df.teamcomp$original / df.teamcomp$se)

round(df.teamcomp, 5)

```

## Table of AMEs (combined team-composition variables)

```{r}

team_prof_label_map <- c(
  "2profs"         = "2 professors",
  "1prof1nonprof"  = "1 professor, 1 non-professor",
  "3profs"         = "3 professors",
  "2profs1nonprof" = "2 professors, 1 non-professor",
  "1prof2nonprofs" = "1 professor, 2 non-professors",
  "4to6majority"   = "4-6 team, majority professors",
  "4to6minority"   = "4-6 team, minority professors",
  "7plusteam"      = "7+ team"
)
team_gender_label_map <- c(
  "womNoProf" = "1+ woman (no professor)",
  "womProf"   = "1+ woman professor"
)

table_ames_teamcomp <- df.teamcomp %>%
  mutate(term = rownames(df.teamcomp),
         var = str_extract(term, "(?<=AME_)[^_]+"),
         model = str_extract(term, "m(3b|3c|4)_tc"),
         # sort alternatives longest-first: regex alternation matches the
         # first alternative that fits, not the longest, so e.g. "2profs"
         # would otherwise match inside "2profs1nonprof" and swallow it
         team_prof_slug = str_extract(term, paste0("(?<=AME_teamprof_)(", paste(names(team_prof_label_map)[order(-nchar(names(team_prof_label_map)))], collapse = "|"), ")")),
         team_gender_slug = str_extract(term, paste0("(?<=AME_teamgender_)(", paste(names(team_gender_label_map)[order(-nchar(names(team_gender_label_map)))], collapse = "|"), ")"))) %>%
  mutate(model = recode(model,
                        "m3b_tc" = "M4 (team comp.)",
                        "m3c_tc" = "M5 (team comp.)",
                        "m4_tc" = "M6 (team comp.)"),
         model = factor(model, levels = c("M4 (team comp.)", "M5 (team comp.)", "M6 (team comp.)"))) %>%
  mutate(label = case_when(
    str_detect(term, "gendercohort") ~ "PhD cohort * Woman",
    str_detect(term, "^AME_gender_") ~ "Woman",
    str_detect(term, "^AME_cohort_") ~ "PhD cohort",
    str_detect(term, "cpubs") ~ "Cumulative publications",
    str_detect(term, "ppubs") ~ "Previous publications",
    str_detect(term, "svpubs") ~ "Supervisors' productivity",
    !is.na(team_prof_slug) ~ paste0("Team: ", team_prof_label_map[team_prof_slug]),
    !is.na(team_gender_slug) ~ paste0("Team: ", team_gender_label_map[team_gender_slug]),
    TRUE ~ str_to_title(var)
  )) %>%
  mutate(value = sprintf("%.4f (%.4f)%s", original, se, sig_stars(t))) %>%
  select(label, model, value)

rows_tab_tc <- c(
  "Woman", "PhD cohort", "PhD cohort * Woman",
  "Cumulative publications", "Previous publications", "Supervisors' productivity",
  paste0("Team: ", team_prof_label_map),
  paste0("Team: ", team_gender_label_map)
)

table_df_teamcomp <- table_ames_teamcomp %>%
  pivot_wider(names_from = model, values_from = value) %>%
  distinct() %>%
  mutate(label = factor(label, levels=rows_tab_tc)) %>%
  arrange(label)

table_df_teamcomp[is.na(table_df_teamcomp)] <- ""

kable(table_df_teamcomp, "html", escape = FALSE, align = "lccc",
      col.names = c("", "M4 (team comp.)", "M5 (team comp.)", "M6 (team comp.)")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  add_header_above(c(" " = 1, "Average Marginal Effects (AMEs) on Veni Receipt -- combined supervision-team variables" = 3)) %>%
  pack_rows("Team: size x professors (ref. = 1 professor)", 7, 14) %>%
  pack_rows("Team: gender x professors (ref. = no women supervisors)", 15, 16) %>%
  footnote(general = "* p < .05, ** p < .01, *** p < .001 (based on the bootstrap t-statistic)",
           general_title = "")

```

