---
title: "Mentoring for gender equality in early-career grant receipt: sample selectivity analyses"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---


# Purpose of this appendix

Our sample of Veni laureates is constructed by starting from the population of
scholars who obtained doctorate in the Netherlands and matching them to NWO Veni
grant records. This appendix is used to assess whether our matching
procedure introduces selection bias into the sample of laureates we analyze.

To do so, we took the following steps:

1. Search for Veni laureates among PhDs who were present in our full,
   pre-selection dataset but excluded from the final analytic sample (Q1
   below), which lets us compare laureates *inside* vs. *outside* our
   analytic sample. We compare our original set of Veni recipients to
   the additionally matched laureates on: university of doctorate, PhD cohort,
   gender and ethnicity.
2. Characterize *all* Veni laureates we could not match at all — inside or
   outside our original sample — and test whether being matched is related to Veni
   cohort, university, gender, or ethnicity (Q2).

## A note on privacy and reproducibility

Building the comparison groups above requires linking individuals by name and
by a unique person identifier, and our ethnicity/origin variable is derived
from surnames. This underlying data cannot be shared on this replication
website for privacy reasons.

To keep this appendix both transparent and reproducible, we use a hybrid
setup:

- All code chunks that require the restricted, identifying data — loading the
  raw files, and matching and constructing the comparison groups for both Q1
  and Q2 — are grouped together in the next section and shown in full, but
  set to `eval=FALSE`. They are included to demonstrate how we matched Veni's
  to PhDs, but cannot be executed because they require non-anonymised data.
- That section ends by writing out two small, de-identified data frames.
  All checks can be executed on the anonymised data published in the
  repository, so every table and figure in the Analyses section below can be
  regenerated live from this data.

---

# Constructing the comparison data (not executed on this website)

## Setup

### Custom functions

- `fpackage.check()`: checks whether packages are installed (and installs
  them if not) ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)).

```{r, results='hide'}
rm(list = ls())

fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}
```

### Packages

```{r, results='hide'}
packages <- c("tidyverse", "stringr", "stringi", "zoo", "kableExtra")
fpackage.check(packages)
```

### Table prep

Some code to make the tables look more readable. 

```{r}
# Basic kable styling, reused for every table below
fkable <- function(df, digits = 3, caption = NULL) {
  df %>%
    kable("html", digits = digits, caption = caption) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)
}

# Turns a prop.table()/table() crosstab into a readable table, with the row
# variable (e.g. group, matched_original) as its own first column
fkable_prop <- function(tab, rowname = " ") {
  tab %>%
    as.data.frame.matrix() %>%
    tibble::rownames_to_column(rowname) %>%
    fkable(digits = 3)
}

# Turns a chisq.test()/wilcox.test() result into a one-row readable table
fkable_test <- function(test, digits = 3) {
  # capture values first: naming a tibble column "test" while `test` is also
  # the argument would otherwise make later rows see the new column instead
  # of the original htest object
  test_name <- test$method
  test_statistic <- unname(test$statistic)
  test_df <- if (!is.null(test$parameter)) unname(test$parameter) else NA_real_
  test_p <- test$p.value

  tibble::tibble(
    test = test_name,
    statistic = test_statistic,
    df = test_df,
    p.value = test_p
  ) %>%
    fkable(digits = digits)
}
```

## Data (restricted — not run on the website)

We load the processed PhD and Veni datasets used throughout the paper, plus
two small manually-coded lookup files used to fill in gender and
ethnicity/origin for laureates that could not be classified automatically
(`data/lookups/gender_veni_additional_filled.csv` and
`data/lookups/ethnicity_veni_additional_cleaned.csv`). These files contain
names and unique person identifiers and are not published; this chunk is shown
for transparency only.

```{r files, eval=FALSE}
load(file = "data/processed/phds_variables.rda")
load(file = "data/processed/phd_supervisors.rda")
load(file = "data/processed/veni_ppf.rda")
load(file = "data/processed/veni_ppf_r2.rda")
load(file = "data/processed/veni_narcis_p.rda")
load(file = "data/processed/veni_NWO_p.rda")
load(file = "data/processed/fn_gender.rda")

genderize_addit <- read.csv(file = "data/lookups/gender_veni_additional_filled.csv")

load(file = "data/processed/ln_origin.rda")

origin_addit <- read.csv(file = "data/lookups/ethnicity_veni_additional_cleaned.csv")
```

Next, we pull out the Veni laureates who are part of our original, analyzed
sample of PhDs, and attach their first and last names (needed for the
name-based matching below).

```{r, eval=FALSE}
veni_ppf %>%
  filter(veni == 1) -> oursample_winners

phds_variables %>%
  select(id, firstname, lastname) %>%
  right_join(oursample_winners, by = c("id")) -> oursample_winners
```

## Q1 matching: Veni laureates outside our analytic sample

Our analytic sample excludes PhDs for several reasons (e.g., no publication
record after the PhD, PhD cohort selection). Here we take the PhDs who were
originally excluded and check whether any of them are Veni laureates we missed.
We use the same two matching strategies used to build the original sample:

- **PRS strategy (NARCIS):** matching on a unique person identifier.
- **Name strategy (NWO):** matching on first and last name.

```{r, eval=FALSE}
# Selecting only PhDs outside our analytic sample
phds <- phds_variables %>% filter(!id %in% veni_ppf$id)

# Creating matching data frames
# Dataset 1: PRS strategy (NARCIS)
match_df1 <- veni_narcis %>% select(veni, year, prs) %>% rename(veni1 = "veni", year1 = "year")

# Dataset 2: First and last name (NWO)
match_df2 <- veni_NWO %>%
  filter(!is.na(first)) %>%
  filter(!is.na(ln)) %>%
  select(veni, year, first, ln) %>%
  rename(veni2 = "veni", year2 = "year")

# Match 1: PRS
phds <- phds %>% left_join(match_df1, by = "prs")
phds$veni1 <- ifelse(is.na(phds$veni1), 0, phds$veni1)

nrow(phds[duplicated(phds$id), ])
summary(as.factor(phds$veni1))

# Match 2: first name / last name
phds <- phds %>% left_join(match_df2, by = c("firstname" = "first", "lastname" = "ln"))
phds$veni2 <- ifelse(is.na(phds$veni2), 0, phds$veni2)

nrow(phds[duplicated(phds$id), ])
summary(as.factor(phds$veni2))

# Removing duplicates introduced by the two matching strategies
duplicatedids <- phds$id[which(duplicated(phds$id))]
inspect <- phds[phds$id %in% duplicatedids, ]
# no convergence similar to the actual matching procedure used for the
# analytic sample, so we just remove one of the duplicates at random
inspect <- inspect %>%
  group_by(id) %>%
  sample_n(1)
phds <- phds %>% filter(!phds$id %in% duplicatedids)
phds <- rbind.data.frame(phds, inspect)

# Collating the results of both matching strategies: matched if either
# strategy found a match
phds$veni <- pmax(phds$veni1, phds$veni2)
summary(as.factor(phds$veni))

# Comparing the Veni years found by each strategy
xtabs(~ phds$year1 + phds$year2)

phds$year <- phds$year1
phds$year <- ifelse(is.na(phds$year1), phds$year2, phds$year1)

# Keep only matches where the Veni year is plausible given the PhD year
# (Veni is an early-career grant, awarded within a fixed window after the PhD)
phds <- phds[phds$year >= phds$phd_year, ]
phds <- phds[phds$year < phds$phd_year + 9, ]

outsidesample_winners <- phds %>% filter(veni == 1)

oursample_winners$group <- "in_sample"
outsidesample_winners$group <- "outside_sample"
outsidesample_winners$phd_year <- outsidesample_winners$phd_year - 1997

# Kept under a separate name (not `df_all`) because it still carries prs and
# firstname, which the Q2 matching below needs. `df_all` itself is reserved
# for the de-identified, publishable version created further down.
df_all_full <- bind_rows(oursample_winners, outsidesample_winners)

# Adding ethnicity/origin (same lookup used later for Q2's `checks`)
ln_origin <- ln_origin %>%
  mutate(
    origin = as.character(origin),
    origin = ifelse(is.na(origin), "other", origin)
  )

df_all_full <- df_all_full %>%
  left_join(ln_origin, by = "lastname") %>%
  left_join(origin_addit, by = "lastname") %>%
  mutate(origin = ifelse(is.na(origin.y), origin.x, origin.y)) %>%
  select(-c(origin.x, origin.y))

# Turkish/Moroccan/Caribbean are individually very sparse, so we collapse
# them into one "minority" category for a more robust test, as we do for Q2.
df_all_full <- df_all_full %>%
  mutate(origin_collapsed = case_when(
    origin %in% c("turkish", "moroccan", "carribean") ~ "minority",
    TRUE ~ origin
  ))
```

## Q2 matching: Veni laureates matched to any PhD at all

The check above compares laureates matched inside vs. outside our analytic
sample. This second check is broader: among *all* Veni laureates (from both
the NARCIS and NWO source lists), which ones can we match to any PhD at all,
and does the probability of being matched depend on the laureate's Veni
cohort, university, gender, or ethnicity? As above, this requires names and
identifiers.

```{r, eval=FALSE}
# Continues from df_all_full (the identity-bearing object built for Q1).
df_all_full <- df_all_full %>%
  mutate(
    matched_prs = ifelse(prs %in% veni_narcis$prs, 1, 0),
    matched_fnln = ifelse(matched_prs == 1, 0, 1)
  )

# Matched Veni's - NARCIS source
veni_narcis <- veni_narcis %>%
  mutate(
    matched = ifelse(prs %in% df_all_full$prs, 1, 0),
    # matched to the original (pre-selection) sample specifically, i.e. the
    # sample actually analyzed in the paper
    matched_original = ifelse(prs %in% oursample_winners$prs, 1, 0)
  )

# Matched Veni's - NWO source
veni_NWO <- veni_NWO %>%
  distinct(first, ln, .keep_all = TRUE)

veni_NWO <- df_all_full %>%
  filter(!is.na(firstname)) %>%
  mutate(matched = 1) %>%
  select(firstname, lastname, matched) %>%
  right_join(veni_NWO, by = c("firstname" = "first", "lastname" = "ln")) %>%
  mutate(matched = ifelse(is.na(matched), 0, matched))

# Note: after the previous right_join, veni_NWO's key columns are already
# named firstname/lastname (dplyr renames to the left-hand side's names), so
# this second join no longer needs the first/ln renaming
veni_NWO <- oursample_winners %>%
  filter(!is.na(firstname)) %>%
  mutate(matched_original = 1) %>%
  select(firstname, lastname, matched_original) %>%
  right_join(veni_NWO, by = c("firstname", "lastname")) %>%
  mutate(matched_original = ifelse(is.na(matched_original), 0, matched_original))

# Number of matched and unmatched laureates per source
summary(as.factor(veni_narcis$matched))
summary(as.factor(veni_NWO$matched))
summary(as.factor(veni_narcis$matched_original))
summary(as.factor(veni_NWO$matched_original))
```

### Combining the NARCIS and NWO Veni lists

Next, we combine the Veni data from NARCIS and NWO into a single laureate
list, so each laureate is counted once regardless of which source we found
them in.

```{r, eval=FALSE}
# Standardizing variable names/selection across sources
veni_narcis %>%
  mutate(lastname = ln) %>%
  select(year, lastname, uni, matched, matched_original, prs) -> veni_narcis_std

veni_NWO %>%
  select(year, firstname, lastname, uni, matched, matched_original) -> veni_NWO_std

# There appeared to be some duplicates in both lists - remove these
veni_NWO_std <- veni_NWO_std %>%
  distinct(year, lastname, uni, .keep_all = TRUE)

# NARCIS needs special treatment because of NA values on last name (matching
# is still possible there via prs)
veni_narcis_std %>%
  filter(is.na(lastname)) -> veni_narcis_std_noln

veni_narcis_std %>%
  filter(!is.na(lastname)) -> veni_narcis_std_ln

veni_narcis_std_ln <- veni_narcis_std_ln %>%
  distinct(year, lastname, uni, .keep_all = TRUE)

# Combining the data frames
veni_combined <- full_join(
  veni_narcis_std_ln %>%
    select(year, lastname, uni, prs, matched_narcis = matched, matched_narcis_original = matched_original),
  veni_NWO_std %>%
    select(year, lastname, uni, firstname, matched_NWO = matched, matched_NWO_original = matched_original),
  by = c("year", "lastname", "uni")
)

# Combining 'matched': matched in either source counts as matched
# - matched: matched to the original sample OR the additional outside-sample search
# - matched_original: matched to the original (pre-selection) sample specifically,
#   i.e. the sample actually analyzed in the paper -> primary check for
#   representativeness/selectivity of the analytic sample
veni_combined <- veni_combined %>%
  mutate(
    matched = case_when(
      matched_narcis == 1 | matched_NWO == 1 ~ 1,
      TRUE ~ 0
    ),
    matched_original = case_when(
      matched_narcis_original == 1 | matched_NWO_original == 1 ~ 1,
      TRUE ~ 0
    )
  )
```

### Adding gender

```{r, eval=FALSE}
veni_combined %>%
  left_join(fn_gender, by = "firstname") -> veni_combined

# A small number of first names were not covered by our existing gender
# lookup, so we executed an additional scrape of these first names from the same
# database (i.e. Meertens Voornamenbank). The code below regenerates the list of
# names that needed manual coding; it is commented out now.

# veni_combined %>%
#   filter(!is.na(firstname)) %>%
#   filter(is.na(gender)) %>%
#   select(firstname) -> additional_checks
# write.csv(additional_checks, file = "./data/lookups/gender_veni_additional.csv")

genderize_addit %>%
  select(firstname, gender) %>%
  mutate(gender = case_when(
    gender == "male" ~ "men",
    gender == "female" ~ "women",
    TRUE ~ NA
  )) %>%
  distinct(firstname, .keep_all = TRUE) -> genderize_addit

genderize_addit$gender <- as.factor(genderize_addit$gender)

veni_combined %>%
  left_join(genderize_addit, by = "firstname") %>%
  mutate(gender = ifelse(is.na(gender.x), as.character(gender.y), as.character(gender.x))) %>%
  select(-c(gender.x, gender.y)) -> veni_combined
```

### Adding ethnicity/origin

```{r, eval=FALSE}
ln_origin <- ln_origin %>%
  mutate(
    origin = as.character(origin),
    origin = ifelse(is.na(origin), "other", origin)
  )

veni_combined %>%
  left_join(ln_origin, by = "lastname") -> veni_combined

# As with gender, a small number of last names needed additional scraping.
# Again, we commented out the code below as it was used to generate the list of
# names that couldn't be matched to an ethnic origin label using our original data.

# veni_combined %>%
#   filter(!is.na(lastname)) %>%
#   filter(is.na(origin)) %>%
#   select(lastname) -> additional_checks_origin
# write.csv(additional_checks_origin, file = "./data/lookups/ethnicity_veni_additional.csv")

veni_combined %>%
  left_join(origin_addit, by = "lastname") %>%
  mutate(origin = ifelse(is.na(origin.y), origin.x, origin.y)) %>%
  select(-c(origin.x, origin.y)) -> checks

# Turkish/Moroccan/Caribbean are individually very sparse (especially
# Moroccan), which makes the chi-square approximation unreliable for the
# 5-category origin variable. We collapse these three named minority groups
# into one category for a more robust test, keeping "other" (unspecified
# foreign) and "dutch" separate.
checks <- checks %>%
  mutate(origin_collapsed = case_when(
    origin %in% c("turkish", "moroccan", "carribean") ~ "minority",
    TRUE ~ origin
  ))
```

## De-identifying the comparison data

We save the necessary columns for the sample selectivity checks, but remove
identifying columns from the data to maintain anonymity of the sample.  
This anonymised dataset can be used to replicate our
analyses.

```{r, eval=FALSE}
df_all_public <- df_all_full %>%
  select(group, uni, phd_year, gender_2, origin, origin_collapsed)

checks_public <- checks %>%
  select(matched, matched_original, year, uni, gender, origin, origin_collapsed)

save(df_all_public, file = "data/selectivity/df_all_public.rda")
save(checks_public, file = "data/selectivity/checks_public.rda")

```

---

# Analyses

From here on, all code chunks can be run.

```{r}
load(file = "data/selectivity/df_all_public.rda")
df_all <- df_all_public

load(file = "data/selectivity/checks_public.rda")
checks <- checks_public
```

## Q1: How many Veni laureates can be matched to PhDs outside our analytic sample?

### Comparing in-sample and out-of-sample laureates

If the PhDs we ended up excluding from the analytic sample differ
systematically from the PhDs we kept, the laureates matched *only* outside
our sample should look different (in university, PhD cohort, gender, or
ethnicity/origin) from the laureates matched *within* our sample. We test
this directly.

```{r}
# Crosstabulate
fkable_prop(prop.table(table(df_all$group, df_all$uni), margin = 1), rowname = "group")
fkable_prop(prop.table(table(df_all$group, df_all$phd_year), margin = 1), rowname = "group")
fkable_prop(prop.table(table(df_all$group, df_all$gender_2), margin = 1), rowname = "group")
fkable_prop(prop.table(table(df_all$group, df_all$origin), margin = 1), rowname = "group")

# Test differences with chi-square
fkable_test(chisq.test(table(df_all$group, df_all$uni)))
fkable_test(chisq.test(table(df_all$group, df_all$phd_year)))
fkable_test(chisq.test(table(df_all$group, df_all$gender_2)))
fkable_test(chisq.test(table(df_all$group, df_all$origin)))

# Robustness: collapsed origin categories, since the 5-category version can
# have sparse cells
fkable_test(chisq.test(table(df_all$group, df_all$origin_collapsed)))
fkable_test(chisq.test(table(df_all$group, df_all$origin_collapsed), simulate.p.value = TRUE))

# Distribution of PhD year, to gain insight into the direction of any difference
summary(df_all$phd_year[df_all$group == "in_sample"])
summary(df_all$phd_year[df_all$group == "outside_sample"])
```

#### University

```{r}
df_uni <- df_all %>%
  count(group, uni) %>%
  group_by(group) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(df_uni, aes(x = uni, y = prop, fill = group)) +
  geom_col(position = "dodge") +
  labs(x = "University", y = "Proportion within group", fill = "Group") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#### PhD year

```{r}
ggplot(df_all, aes(x = phd_year, fill = group)) +
  geom_density(alpha = 0.4)
```

#### Ethnicity/origin

```{r}
df_origin <- df_all %>%
  filter(!is.na(origin)) %>%
  count(group, origin) %>%
  group_by(group) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(df_origin, aes(x = origin, y = prop, fill = group)) +
  geom_col(position = "dodge") +
  labs(x = "Origin", y = "Proportion within group", fill = "Group") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Q2: What characterizes Veni laureates we cannot match at all?

For each characteristic (Veni cohort, university, gender, ethnicity)
we report two checks:

- **Primary check:** matched to the original (analyzed) sample vs. not. This
  is the check that speaks most directly to whether *our analytic sample* is
  selective.
- **Secondary check:** matched to the original sample *or* the additional
  outside-sample search vs. not matched anywhere. This is a broader check on
  whether the overall matching procedure (not just our sample selection) is
  selective.

### Veni cohort (year)

```{r}

# Primary check
fkable_prop(prop.table(table(checks$matched_original, checks$year), margin = 1), rowname = "matched_original")

# Year has many distinct values, so cell counts in the chi-square table can
# get sparse; we therefore also run a non-parametric test that doesn't rely
# on that assumption
fkable_test(chisq.test(table(checks$matched_original, checks$year)))
fkable_test(wilcox.test(year ~ matched_original, data = checks))

ggplot(checks, aes(x = year, fill = as.factor(matched_original))) +
  geom_density(alpha = 0.4) +
  labs(x = "Veni jaar", fill = "Matched (original sample)")

summary(checks$year[checks$matched_original == 1])
summary(checks$year[checks$matched_original == 0])
```

```{r}

# Secondary check
fkable_prop(prop.table(table(checks$matched, checks$year), margin = 1), rowname = "matched")
fkable_test(chisq.test(table(checks$matched, checks$year)))
fkable_test(wilcox.test(year ~ matched, data = checks))
```

### University

```{r}

# Primary check
fkable_prop(prop.table(table(checks$matched_original, checks$uni), margin = 1), rowname = "matched_original")
fkable_test(chisq.test(table(checks$matched_original, checks$uni)))

df_uni_matched <- checks %>%
  filter(!is.na(uni)) %>%
  count(matched_original, uni) %>%
  group_by(matched_original) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(df_uni_matched, aes(x = uni, y = prop, fill = as.factor(matched_original))) +
  geom_col(position = "dodge") +
  labs(x = "University", y = "Proportion within group", fill = "Matched (original sample)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}

# Secondary check
fkable_prop(prop.table(table(checks$matched, checks$uni), margin = 1), rowname = "matched")
fkable_test(chisq.test(table(checks$matched, checks$uni)))
```

### Gender

```{r}

# Primary check
fkable_prop(prop.table(table(checks$matched_original, checks$gender), margin = 1), rowname = "matched_original")
fkable_test(chisq.test(table(checks$matched_original, checks$gender)))

df_gender_matched <- checks %>%
  filter(!is.na(gender)) %>%
  count(matched_original, gender) %>%
  group_by(matched_original) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(df_gender_matched, aes(x = gender, y = prop, fill = as.factor(matched_original))) +
  geom_col(position = "dodge") +
  labs(x = "Gender", y = "Proportion within group", fill = "Matched (original sample)") +
  theme_minimal()
```

```{r}

# Secondary check
fkable_prop(prop.table(table(checks$matched, checks$gender), margin = 1), rowname = "matched")
fkable_test(chisq.test(table(checks$matched, checks$gender)))
```

### Ethnicity

```{r}

# Primary check
fkable_prop(prop.table(table(checks$matched_original, checks$origin), margin = 1), rowname = "matched_original")
fkable_test(chisq.test(table(checks$matched_original, checks$origin)))

df_origin_matched <- checks %>%
  filter(!is.na(origin)) %>%
  count(matched_original, origin) %>%
  group_by(matched_original) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(df_origin_matched, aes(x = origin, y = prop, fill = as.factor(matched_original))) +
  geom_col(position = "dodge") +
  labs(x = "Origin", y = "Proportion within group", fill = "Matched (original sample)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# Robustness: collapsing the sparse Turkish/Moroccan/Caribbean categories
# into a single "minority" category
fkable_prop(prop.table(table(checks$matched_original, checks$origin_collapsed), margin = 1), rowname = "matched_original")
fkable_test(chisq.test(table(checks$matched_original, checks$origin_collapsed)))
fkable_test(chisq.test(table(checks$matched_original, checks$origin_collapsed), simulate.p.value = TRUE))
```

```{r}
# Secondary check
fkable_prop(prop.table(table(checks$matched, checks$origin), margin = 1), rowname = "matched")
fkable_test(chisq.test(table(checks$matched, checks$origin)))
fkable_test(chisq.test(table(checks$matched, checks$origin_collapsed), simulate.p.value = TRUE))
```

## Summary: is matching selective?

The table below collects the chi-square test p-values from the Q2 checks
above, for both the primary check (matched to our analytic sample vs. not)
and the secondary check (matched anywhere vs. not matched at all).

```{r}
robustness_checks <- tibble::tibble(
  variable = c(
    "Veni cohort (year)", "Institution (uni)", "Gender", "Ethnicity/origin",
    "Ethnicity/origin (turkish/moroccan/carribean collapsed)"
  ),
  chisq_p_original_sample = c(
    chisq.test(table(checks$matched_original, checks$year))$p.value,
    chisq.test(table(checks$matched_original, checks$uni))$p.value,
    chisq.test(table(checks$matched_original, checks$gender))$p.value,
    chisq.test(table(checks$matched_original, checks$origin))$p.value,
    chisq.test(table(checks$matched_original, checks$origin_collapsed), simulate.p.value = TRUE)$p.value
  ),
  chisq_p_incl_outside_sample = c(
    chisq.test(table(checks$matched, checks$year))$p.value,
    chisq.test(table(checks$matched, checks$uni))$p.value,
    chisq.test(table(checks$matched, checks$gender))$p.value,
    chisq.test(table(checks$matched, checks$origin))$p.value,
    chisq.test(table(checks$matched, checks$origin_collapsed), simulate.p.value = TRUE)$p.value
  )
)

robustness_checks %>%
  fkable(
    digits = 3,
    caption = "Chi-square test p-values for each characteristic, testing whether matched status is related to Veni cohort, university, gender, or ethnicity/origin."
  )
```
