---
title: "Mentoring for gender equality in early-career grant receipt: supervisor variables"
date: "Last compiled on `r Sys.Date()`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes
    
---


```{r, globalsettings, echo=FALSE, warning=FALSE, results="hide"}

library(knitr)
library(formatR)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=FALSE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"), cache.lazy = FALSE)
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```




----


This lab journal shows how we construct the variables for resources present in the supervision team. 


----


# Custom functions

- `package.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)). 


```{r, results='hide'}

rm(list=ls())


fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}


```

---  

# Packages



- `tidyverse`: For general data manipulaion

- `stringr`: For string manipulations

- `stringi`: For string manipulations

- `tidyr`: For pivoting from wide to long & vice versa


```{r, results='hide'}

packages = c("tidyverse", "stringr", "stringi")

fpackage.check(packages)


```

--- 


# Input

We use four processed datasets and one raw dataset

* [phdgender](https://github.com/ammulders/amatteroftime/data/processed/phdgender.rda): example dataset of 8 (fictional) PhDs with first and last names and gender
    - For construction of this dataset see [Independent variables: gender](gender.html)
    - name of dataset: `phdgender` 
    
* [profs](https://github.com/ammulders/amatteroftime/data/professors/profs.rda): a (fictional) list of professors, the structure of which is a copy of the original lists obtained from NARCIS
    - name of dataset: `profs`     

* [ln_origin](https://github.com/ammulders/amatteroftime/data/processed/ln_origin.rda): ethnicity information associated with the last names in our data 
    - Ethnicity is not a main covariate in this paper, so we do not have a separate page detailing how we 
    construct it here, but our method can be found [here](https://ammulders.github.io/amatteroftime/ethnicity.html)
    - name of dataset: `ln_origin` 
    
* [gender](https://github.com/ammulders/amatteroftime/data/processed/gender.rda): web scraped gender data for the 8 first names in the example data, from Meertens Voornamenbank
    - name of dataset: `gender` 

* [genderizer](https://github.com/ammulders/amatteroftime/data/processed/genderizer.rda): web scraped gender data for the first names in the example data, from GenderizeR global, Morocco, Turkey and Netherlands
    - name of dataset: `genderizer`
    
* [pubs_sv](data/processed/pubs_sv.rda): web scraped OpenAlex publication/citation data
    - name of dataset: `pubs_sv`


```{r files, eval=TRUE}

load(file = "data/processed/phdgender.rda")

load(file = "data/professors/profs.rda")

load(file = "./data/processed/ln_origin.rda")

load(file = "data/processed/gender.rda")

load(file = "data/processed/genderizer.rda")

load(file = "./data/processed/pubs_sv.rda")

```


---  



# Combining the two supervisor columns in phd_metadf to one 



# Transforming the data so that we have one supervisor per row

```{r}

# create one object for each supervisor

# str_remove()/str_remove_all() error (or, for the _all variant, warn) when
# `pattern` contains NA or "" per row. Throughout this block, a NA/"" pattern
# always means "nothing to remove here" for that row, so this helper swaps
# those out for a regex that never matches -- a true no-op removal -- instead
# of coalescing to "" (which is fine for str_remove but still triggers a
# warning in str_remove_all when a row's pattern is genuinely "").
safe_str_remove <- function(string, pattern, all = FALSE) {
  never_match <- "(?!)"
  pattern <- ifelse(is.na(pattern) | pattern == "", never_match, pattern)
  if (all) str_remove_all(string, pattern) else str_remove(string, pattern)
}

# supervisor 1 and 2
phdgender$supervisor1 <- str_remove(phdgender$supervisors, ";.*") # delete everything after the first ;
phdgender$supervisor2 <- safe_str_remove(phdgender$supervisors, phdgender$supervisor1, all = TRUE) # remove supervisor1 from the supervisor object to get supervisors 2-k
phdgender$supervisor2 <- str_remove_all(phdgender$supervisor2, "^(\\s)?;\\s") # remove ; at the beginning of this object
phdgender$supervisor2 <- ifelse(phdgender$supervisor2=="" | phdgender$supervisor2==" ", NA, phdgender$supervisor2)

# supervisor 3
phdgender$supervisor3 <- str_extract(phdgender$supervisor2, ";.*$") # get supervisor 3 by extracting everything after ; in supervisor 2
phdgender$supervisor2 <- safe_str_remove(phdgender$supervisor2, phdgender$supervisor3)
# remove supervisor 3 from the supervisor 2 object, but only if there is a third supervisor present
phdgender$supervisor3 <- str_extract(phdgender$supervisor3, "[:upper:].*") # remove ; at the beginning of this object

# supervisor 4
phdgender$supervisor4 <- str_extract(phdgender$supervisor3, ";.*$") # same procedure as for supervisor 3 from now on
phdgender$supervisor3 <- safe_str_remove(phdgender$supervisor3, phdgender$supervisor4)
phdgender$supervisor4 <- str_extract(phdgender$supervisor4, "[:upper:].*")

# supervisor 5
phdgender$supervisor5 <- str_extract(phdgender$supervisor4, ";.*$")
phdgender$supervisor4 <- safe_str_remove(phdgender$supervisor4, phdgender$supervisor5)
phdgender$supervisor5 <- str_extract(phdgender$supervisor5, "[:upper:].*")

# supervisor 6
phdgender$supervisor6 <- str_extract(phdgender$supervisor5, ";.*$")
phdgender$supervisor5 <- safe_str_remove(phdgender$supervisor5, phdgender$supervisor6)
phdgender$supervisor6 <- str_extract(phdgender$supervisor6, "[:upper:].*")

# supervisor 7
phdgender$supervisor7 <- str_extract(phdgender$supervisor6, ";.*$")
phdgender$supervisor6 <- safe_str_remove(phdgender$supervisor6, phdgender$supervisor7)
phdgender$supervisor7 <- str_extract(phdgender$supervisor7, "[:upper:].*")

# supervisor 8
phdgender$supervisor8 <- str_extract(phdgender$supervisor7, ";.*$")
phdgender$supervisor7 <- safe_str_remove(phdgender$supervisor7, phdgender$supervisor8)
phdgender$supervisor8 <- str_extract(phdgender$supervisor8, "[:upper:].*")

# supervisor 9
phdgender$supervisor9 <- str_extract(phdgender$supervisor8, ";.*$")
phdgender$supervisor8 <- safe_str_remove(phdgender$supervisor8, phdgender$supervisor9)
phdgender$supervisor9 <- str_extract(phdgender$supervisor9, "[:upper:].*")

# supervisor 10
phdgender$supervisor10 <- str_extract(phdgender$supervisor9, ";.*$")
phdgender$supervisor9 <- safe_str_remove(phdgender$supervisor9, phdgender$supervisor10)
phdgender$supervisor10 <- str_extract(phdgender$supervisor10, "[:upper:].*")

# supervisor 11
phdgender$supervisor11 <- str_extract(phdgender$supervisor10, ";.*$")
phdgender$supervisor10 <- safe_str_remove(phdgender$supervisor10, phdgender$supervisor11)
phdgender$supervisor11 <- str_extract(phdgender$supervisor11, "[:upper:].*")

# trim whitespaces
phdgender$supervisor1 <- trimws(phdgender$supervisor1)
phdgender$supervisor2 <- trimws(phdgender$supervisor2)
phdgender$supervisor3 <- trimws(phdgender$supervisor3)
phdgender$supervisor4 <- trimws(phdgender$supervisor4)
phdgender$supervisor5 <- trimws(phdgender$supervisor5)
phdgender$supervisor6 <- trimws(phdgender$supervisor6)
phdgender$supervisor7 <- trimws(phdgender$supervisor7)
phdgender$supervisor8 <- trimws(phdgender$supervisor8)
phdgender$supervisor9 <- trimws(phdgender$supervisor9)
phdgender$supervisor10 <- trimws(phdgender$supervisor10)
phdgender$supervisor11 <- trimws(phdgender$supervisor11)


phdgender <- tidyr::pivot_longer(phdgender, cols=c(supervisor1, supervisor2, supervisor3, supervisor4, supervisor5, supervisor6, supervisor7, supervisor8, supervisor9, supervisor10, supervisor11), names_to="sv_n", values_to="supervisor")


# adding a phd-supervisor ID variable
phdgender$id_phd_sv <- paste0(phdgender$id, "-", str_extract(phdgender$sv_n, "[:digit:]+"))

# removing empty lines
phdgender <- phdgender[!is.na(phdgender$supervisor), ]

```





# Gathering supervisors' first and last names into separate columns

```{r}

# defining nobiliary particles so that these can be removed
vande0 <- c("(V|v)an (D|d)er", "(V|v)an (D|d)en", "(V|v)an (D|d)e", "(V|v)ande(n)?", "(V|v)an '(T|t)", "(V|v)an'(T|t)", "(V|v)an (H|h)et", "(V|v)on (D|d)er", "(O|o)p den", "(O|o)p 't", "(O|o)f ten", "(A|a)an de(n)?", "(D|d)e (L|l)a", "(I|i)n (H|h)et", "(I|i)n '(T|t)", "(I|i)n'(T|t)", "(I|i)n (D|d)er", "(B|b)ij (D|d)e") # nobiliary particles anywhere in string

vande1 <- c("^(L|l)a\\s", "^(O|o)p\\s" ,"^(V|v)an\\s", "^(V|v)on\\s", "^(D|d)en\\s", "^(D|d)er\\s", "^(D|d)el\\s", "^(D|d)(e|a|u|i)\\s", "^(D|d)os?\\s", "^(T|t)er\\s" , "^(T|t)en\\s", "^(T|t)e\\s", "^'(T|t)\\s", "^(L|l)e\\s", "^El-", "^[(A|a)(E|e)](L|l)'?\\s", "^(D|d)'", "^zu\\s", "^(Z|z)ur\\s", "^e\\s") # starts with np

vande2 <- c("\\s(L|l)a$", "\\s(O|o)p$" ,"\\s(V|v)an$", "\\s(V|v)on$", "\\s(D|d)en$", "\\s(D|d)er$", "\\s(D|d)el$", "\\s(D|d)(e|a|u|i)$", "\\s(D|d)os?$", "\\s(T|t)er$", "\\s(T|t)en$", "\\s(T|t)e$", "\\s'(T|t)$", "\\s(L|l)e$", "\\s[(A|a)(E|e)](L|l)'?$", "\\s(D|d)'$", "\\szu$", "\\s(Z|z)ur$") # ends with np

vande3 <- c("\\s(L|l)a\\s", "\\s(O|o)p\\s" ,"\\s(V|v)an\\s", "\\s(V|v)on\\s", "\\s(D|d)en\\s", "\\s(D|d)er\\s", "\\s(D|d)el\\s", "\\s(D|d)(e|a|u|i)\\s", "\\s(D|d)os?\\s", "\\s(T|t)er\\s", "\\s(T|t)en\\s", "\\s(T|t)e\\s", "\\s'(T|t)\\s", "\\s(L|l)e\\s", "\\s(E|A)l-", "\\s[(A|a)(E|e)](L|l)'?\\s", "\\s(D|d)'", "\\szu\\s", "\\s(Z|z)ur\\s", "\\s(Y|y)\\s", "\\s(E|e)\\s") # np in the middle

vande4 <- c("^(L|l)a$", "^(O|o)p$" , "^(V|v)an$", "^(V|v)on$", "^(D|d)en$", "^(D|d)er$", "^(D|d)el$", "^(D|d)(e|a|u|i)$", "^(D|d)os?$", "^Vande[$//s]", "^(T|t)er$",  "^(T|t)en$", "^(T|t)e$", "^'(T|t)$", "^(L|l)e$", "^[(A|a)(E|e)](L|l)'?$", "^(D|d)'$", "^zu$", "^(Z|z)ur$") # entire string is a np




# first name of supervisor
phdgender$sv_fn <- str_remove(phdgender$supervisor, "^.*,") # name after comma
phdgender$sv_fn <- ifelse(as.numeric(str_detect(phdgender$sv_fn, "(?<=\\().*(?=\\))"))==1, str_extract(phdgender$sv_fn,  "(?<=\\().*(?=\\))"), phdgender$sv_fn)  # name in brackets
phdgender$sv_fn <- trimws(phdgender$sv_fn, which="both")

# Extract nobiliary particles
phdgender$sv_np <- str_extract(phdgender$sv_fn, paste0(c(vande0, vande1, vande2), collapse="|"))
phdgender$sv_np <- tolower(phdgender$sv_np)

# Remove nobiliary particles from the firstname
phdgender$sv_fn <- str_remove_all(phdgender$sv_fn, paste0(vande0, collapse="|")) # remove nobiliary particles
phdgender$sv_fn <- str_remove_all(phdgender$sv_fn, paste0(vande1, collapse="|")) # remove nobiliary particles
phdgender$sv_fn <- str_remove_all(phdgender$sv_fn, paste0(vande2, collapse="|")) # remove nobiliary particles
phdgender$sv_fn <- str_remove_all(phdgender$sv_fn, paste0(vande3, collapse="|")) # remove nobiliary particles

phdgender$sv_fn <- ifelse(phdgender$sv_fn == "", NA, phdgender$sv_fn) # set to NA if missing


# extract initials based on full first names
phdgender$sv_ini <- str_extract_all(phdgender$sv_fn, "[:upper:]")
# combine multiple initials in c() object into a single string
phdgender$sv_ini <- gsub("c\\(\"", "", phdgender$sv_ini)
phdgender$sv_ini <- gsub("\", \"", ".", phdgender$sv_ini)
phdgender$sv_ini <- gsub("\"\\)", ".", phdgender$sv_ini)
# add full stop at the end of single-letter initials
phdgender$sv_ini <- trimws(phdgender$sv_ini)
phdgender$sv_ini <- ifelse(as.numeric(str_detect(phdgender$sv_ini, "^[:upper:]$"))==1, paste0(phdgender$sv_ini, "."), phdgender$sv_ini)


# next, we remove initials from the supervisors' names
initialpattern <- paste(c("^([:upper:]\\.?\\-\\.?)+",                 # A- or A-. or A.-
                          "(T|t|C|c|P|p)h\\.\\s?",                    # Th. Ph. Ch. 
                          "^([:upper:]\\.)+[:upper:](\\s)?$",         # A.A.A
                          "([:upper:]\\.+)+", "([:lower:]\\.){2,}",   # A.  or a.
                          "^\\s?([:alpha:]\\s)+",                     # A or a surrounded by whitespace
                          "^\\s?[:alpha:]\\.?\\s?$",                  # entire string consists of a single letter
                          "^\\s?[:upper:]{2,4}\\s?$"),                # entire string consists of 2-4 capital letters
                        collapse = "|")

# removing lowercase v.d. at the beginning of first name, since this tends to signal "van de" in Dutch
phdgender$sv_fn <- gsub("^v.d.\\s", "", phdgender$sv_fn)
phdgender$sv_fn <- gsub("^v\\s", "", phdgender$sv_fn)

# removing initials from first name object
phdgender$sv_fn <- str_remove_all(phdgender$sv_fn, initialpattern)


# some cleaning: lowercase names and extracting only the first-mentioned last name
phdgender$sv_fn <- trimws(phdgender$sv_fn)
phdgender$sv_fn <- tolower(phdgender$sv_fn) # lowercase
phdgender$sv_fn <- stri_trans_general(phdgender$sv_fn, id="latin-ascii")

phdgender$sv_fn <- str_extract(phdgender$sv_fn, "[a-z]+\\-*[a-z]*")

# last names of supervisor 
phdgender$sv_ln <- str_remove(phdgender$supervisor, ",.*$")
phdgender$sv_ln <- str_remove(phdgender$sv_ln, paste0(vande0, collapse="|")) # remove nobiliary particles
phdgender$sv_ln <- str_remove(phdgender$sv_ln, paste0(vande1, collapse="|")) # remove nobiliary particles

phdgender$sv_ln <- tolower(phdgender$sv_ln) # lowercase
phdgender$sv_ln <- stri_trans_general(phdgender$sv_ln, id="latin-ascii")

phdgender$sv_ln <- str_extract(phdgender$sv_ln, "[a-z]+") # first-mentioned last name


```



# Create a matchable dataframe of supervisors

```{r}

supervisors <- subset(phdgender, select=c(id, id_phd_sv, phd_year, supervisors, sv_fn, sv_ini, sv_ln, sv_n))

supervisors %>%
  rename(id_phd = id,
         phd_year_phd = phd_year) -> supervisors


# fill first names for supervisors in case the name format varies per PhD (e.g. some have only initials, some have name and initials) 
supervisors %>%
  group_by(sv_ln, sv_ini) %>%
  tidyr::fill(sv_fn, .direction="downup") -> supervisors


```





# Adding professor titles

```{r}

full <- profs[profs$title=="full",]


full <- subset(full, select=c("id_pr", "firstname_pr", "ini", "lastname", "fullname_pr", "np_pr", "firstyear"))

# We first match supervisors to the professor database based on firstname 
full_firstname <- full[!is.na(full$firstname_pr),]


supervisors <- left_join(supervisors, full_firstname, by=c("sv_ln"="lastname", "sv_fn"="firstname_pr"))
# creates about 2k duplicates, upon inspection, these seem to be the same people

# remove duplicates
supervisors %>%
  group_by(id_phd_sv) %>%
  slice_head() %>%
  ungroup -> supervisors


# Then, we match supervisors to the professor database based on initials
# But only the part that is not yet matched 

supervisors_match <- supervisors[!is.na(supervisors$firstyear),] # 58K supervisors are matched

supervisors_nomatch <- supervisors[is.na(supervisors$firstyear),] # not yet matched supervisors 
supervisors_nomatch <- subset(supervisors_nomatch, select=c("id_phd", "id_phd_sv", "phd_year_phd", "supervisors", "sv_fn", "sv_ini", "sv_ln", "sv_n" ))

supervisors_nomatch <- left_join(supervisors_nomatch, full, by=c("sv_ln"="lastname", "sv_ini"="ini"))

# removing duplicates again

supervisors_nomatch %>%
  group_by(id_phd_sv) %>%
  tidyr::fill(firstname_pr, .direction="downup") %>%
  tidyr::fill(id_pr, .direction="downup") %>%
  slice_head() -> supervisors_nomatch


```


# Adding names from the professors database

```{r}

nrow(supervisors_nomatch[!is.na(supervisors_nomatch$sv_fn),])


# Copy the professors' first names if they are not yet filled
supervisors_nomatch$sv_fn <- ifelse(is.na(supervisors_nomatch$sv_fn), supervisors_nomatch$firstname_pr, supervisors_nomatch$sv_fn)


nrow(supervisors_nomatch[!is.na(supervisors_nomatch$sv_fn),])


```


# Combining the professor info based on the two matching strategies

```{r}

supervisors_match <- subset(supervisors_match, select=c("id_phd", "id_phd_sv", "phd_year_phd", "supervisors", "sv_fn", "sv_ini", "sv_ln", "id_pr", "firstyear"))

supervisors_nomatch <- subset(supervisors_nomatch, select=c("id_phd", "id_phd_sv", "phd_year_phd", "supervisors", "sv_fn", "sv_ini", "sv_ln",  "id_pr", "firstyear"))


supervisors <- rbind.data.frame(supervisors_match, supervisors_nomatch)

supervisors$prof <- ifelse((!is.na(supervisors$firstyear) & supervisors$firstyear < supervisors$phd_year_phd), 1, 0)

```


# Adding names from publications co-authored with PhDs

The code below is provided to show how we extracted supervisors' names from the publications co-authored with their PhDs. 


```{r, eval=FALSE}

# load in the publications


# We only select supervisors from the batch whose name we do not yet know
missingname <- supervisors[is.na(supervisors$sv_fn),]

# Keep the variables that are necessary to match on
missingname <- subset(missingname, select=c("sv_ln", "id_phd", "id_phd_sv"))


# adding pubs
pubsmissingname <- left_join(missingname, pubs, by=c("id_phd"="id"))


# Make sure the format of last name aligns with the notation in the 'auteur' column of the publications data
pubsmissingname$lastname <- str_to_title(pubsmissingname$sv_ln) # start with a capital letter
pubsmissingname$lastname <- unaccent(pubsmissingname$lastname) # no diacritics
pubsmissingname$lastname <- paste0(pubsmissingname$lastname, ",") # add comma so that only a 1:1 match is detected, not partial matches 

# Create a 0/1 variable indicating whether a certain publication is co-authored by supervisor
pubsmissingname$with_sv <- as.numeric(str_detect(pubsmissingname$auteur, pubsmissingname$lastname))

# Only select publications co-authored by the supervisor
pubsmissingname <- pubsmissingname[pubsmissingname$with_sv==1,]


# Get everything after the last name of the supervisor
pubsmissingname$fullname <- str_remove_all(pubsmissingname$auteur, paste0("^\n?.*", pubsmissingname$lastname))

# Remove author information that comes after the supervisor (if present)
pubsmissingname$fullname <- ifelse(as.numeric(str_detect(pubsmissingname$fullname, ";"))==1, str_remove(pubsmissingname$fullname, ";.*$"), pubsmissingname$fullname)


# Remove double last names (usually separated by a -)
# A good signal that this is the case, is when the string (after above manipulations starts with "-")
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, paste0("^-((V|v)an)?\\s?((D|d)e)?\\s?[A-Za-z]+"))


# Remove initials
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, initialpattern)

# Remove commas
# I do this before removing nobiliary particles, because sometimes, a nobiliary particle is immediately followed by a comma
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, ",")
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

# Remove nobiliary particles
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, paste0(vande0, collapse="|"))
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, paste0(vande1, collapse="|"))
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, paste0(vande2, collapse="|"))
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, paste0(vande3, collapse="|"))
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, paste0(vande4, collapse="|"))
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

# Remove a couple of odd characters and non-names I detected
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "†")
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "(co-)?promotor")
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "[Ii]n\\.")
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "[Vv]an\\.")
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "[Dd]e\\.")
# Removing brackets
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "\\(")
pubsmissingname$fullname <- str_remove_all(pubsmissingname$fullname, "\\)")
pubsmissingname$fullname <- trimws(pubsmissingname$fullname)

# Extract only the first-mentioned name
pubsmissingname$firstname <- str_extract(pubsmissingname$fullname, "[:alpha:]+")

# Remove one-character (initial) names
pubsmissingname$firstname <- ifelse(nchar(pubsmissingname$firstname)==1, NA, pubsmissingname$firstname) 
pubsmissingname$firstname <- ifelse(pubsmissingname$firstname=="^Th$", NA, pubsmissingname$firstname) 

# lowercase
pubsmissingname$firstname <- unaccent(tolower(pubsmissingname$firstname))

pubsmissingname$firstname <- tolower(pubsmissingname$firstname)


# levels(as.factor(pubsmissingname$firstname)) # optional check


# selecting only the relevant columns
pubsmissingname <- subset(pubsmissingname, select=c("id_phd_sv", "firstname"))
pubsmissingname <- rename(pubsmissingname, firstname_pubs = firstname)


# removing empty lines
pubsmissingname <- pubsmissingname[!is.na(pubsmissingname$firstname_pubs),]


# in case a PhD has multiple co-authors with the same last name but different first names, we pick the name that is most common
pubsmissingname %>%
  group_by(id_phd_sv, firstname_pubs) %>%
  summarise(counter = n(), .groups='drop') %>%
  ungroup() -> namecounter


# this piece of code is used to check how many names are added
namecounter %>%
group_by(id_phd_sv) %>%
arrange(desc(counter)) %>%
filter(row_number()==1) %>%
select(id_phd_sv, firstname_pubs) -> namecounter


# merging the names back into the data
nrow(supervisors[!is.na(supervisors$sv_fn),]) nrow(supervisors[!is.na(supervisors$sv_fn),]) # check how many supervisors' first names are missing before adding names from publications
 
supervisors %>% left_join(namecounter, by="id_phd_sv") -> supervisors # add names

supervisors$sv_fn <- ifelse(is.na(supervisors$sv_fn), supervisors$firstname_pubs, supervisors$sv_fn) # fill names based on the publications


nrow(supervisors[!is.na(supervisors$sv_fn),]) # check how many supervisors' first names are missing after adding names from publications

```



# Adding gender

From Meertens first name database

```{r}

supervisors <- left_join(supervisors, gender, by=c("sv_fn" = "firstname"))


supervisors %>% 
  mutate(freq_m = ifelse((freq_m=="--"), 0, freq_m), 
         freq_f = ifelse((freq_f=="--"), 0, freq_f), 
         female = ifelse((freq_f > freq_m), 1, 0),
         female = ifelse((freq_m == freq_f), NA, female)) -> supervisors


# renaming the variable and transforming into a factor

supervisors$female <- as.factor(supervisors$female)
levels(supervisors$female)
levels(supervisors$female) <- c("men", "women")
supervisors <- supervisors %>% dplyr::rename(sv_gender = female)

# dropping the frequency variables
supervisors <- supervisors %>% select(id_phd, id_phd_sv, phd_year_phd, supervisors, sv_fn, sv_ini, sv_ln,  id_pr, firstyear, prof, sv_gender)

```


## Gender based on GenderizeR 

We use GenderizeR to supplement gender based on Meertens Voornamenbank, the same way we do for PhDs themselves as detailed in [gender](gender.html). Given that the method is exactly the same, we repeat the code here to illuminate our workflow, but set it to non-active. 

```{r, eval=FALSE}

# Merging the origin variables onto supervisors
supervisors <- left_join(supervisors, ln_origin, by = c("sv_ln" = "lastname"))

supervisors <- supervisors %>% rename(sv_ethnicity=origin) # rename the variable to make clear it is the supervisors

supervisors <- left_join(supervisors, genderizer, by=c("sv_fn" = "firstname"))


# Take country-specific genderizeR data where applicable, else the complete genderizeR database
supervisors %>%
  mutate(genderZ = gender_all,
         genderZ = ifelse(sv_ethnicity=="dutch", gender_nl, genderZ),
         genderZ = ifelse(sv_ethnicity=="moroccan", gender_ma, genderZ),
         genderZ = ifelse(sv_ethnicity=="turkish", gender_tr, genderZ)) -> supervisors

supervisors$genderZ <- as.factor(supervisors$genderZ)

# Only use genderizeR when gender is not present from Meertens
supervisors$sv_gender <- ifelse(is.na(supervisors$sv_gender), supervisors$genderZ, supervisors$sv_gender)

supervisors$sv_gender <- as.factor(supervisors$sv_gender)
levels(supervisors$sv_gender) <- c("men", "women")

# recall Meertens + genderizeR
nrow(supervisors[(!is.na(supervisors$sv_gender)),]) / nrow(supervisors) * 100


# Create an extra value for missing
supervisors$sv_gender <- fct_explicit_na(supervisors$sv_gender, "missing")


# Only keeping relevant variables
supervisors %>%
  select(c("id_phd", "id_phd_sv", "phd_year_phd", "supervisors", "sv_fn", "sv_ini", "sv_ln", "sv_gender", "prof", "id_pr")) -> supervisors



```



# Creating variables at the level of the supervisory team

More than 1 professor

```{r}

supervisors %>%
  group_by(id_phd) %>%
  summarise(sumprof = sum(prof)) -> sumprof # group by id and then sum the number of supervisors who are professor

supervisors %>%
  left_join(sumprof, by="id_phd") %>%
  mutate(prof2p = ifelse(sumprof<2, 0, 1)) -> professorsteam # create a new variable on the level of PhDs specifying if the phd has 2+ professors in their team (prof2p)

professorsteam <- subset(professorsteam, select=c("id_phd", "prof2p")) # extract only the id and the relevant variable so we can easily add this to our dataframe of phds

professorsteam <- professorsteam[!duplicated(professorsteam$id_phd),] # remove duplicaties

summary(as.factor(professorsteam$prof2p)) # check how many people score a 0 and a 1 on the new variable


```



Size of the team

```{r}

supervisors %>%
  group_by(id_phd) %>%
  summarise(teamsize = n()) %>%
  select(id_phd, teamsize) -> teamsize # grouping the dataframe by PhD and tallying up the number of supervisors

summary(as.factor(teamsize$teamsize))

```

Combining team size and professor count (robustness check: replacing individual supervision-team predictors with combined variables)

```{r}

team_comp <- teamsize %>%
  left_join(sumprof, by = "id_phd")

table(team_comp$teamsize, team_comp$sumprof)

# Cross-tab shows sumprof==0 occurring for every teamsize, which shouldn't be
# possible in practice (the promotor must formally hold a professorship), so
# those rows are a data-quality gap rather than a genuine "0 professors" team
# -- they're merged into the next-lowest professor count below.
#
# From teamsize 4 onward, exact professor counts get too sparse to use
# directly (e.g. teamsize 5 with 5 professors: n=129; teamsize 6 with 6
# professors: n=38), so those are grouped into size bands (4-6 vs. 7+) split
# by professor *share* instead of exact count; teamsize 7+ (n=505 combined)
# is left as a single catch-all since it's too thin to split further.
team_comp <- team_comp %>%
  mutate(
    prof_share = sumprof / teamsize,
    team_prof_size = case_when(
      teamsize == 1                         ~ "1 professor",
      teamsize == 2 & sumprof >= 2          ~ "2 professors",
      teamsize == 2 & sumprof <  2          ~ "1 professor, 1 non-professor",
      teamsize == 3 & sumprof == 3          ~ "3 professors",
      teamsize == 3 & sumprof == 2          ~ "2 professors, 1 non-professor",
      teamsize == 3 & sumprof <  2          ~ "1 professor, 2 non-professors",
      teamsize %in% 4:6 & prof_share >= 0.5 ~ "4-6 team, majority professors",
      teamsize %in% 4:6 & prof_share <  0.5 ~ "4-6 team, minority professors",
      teamsize >= 7                         ~ "7+ team",
      TRUE ~ NA_character_
    )
  )

summary(as.factor(team_comp$team_prof_size))

team_comp <- subset(team_comp, select = c("id_phd", "team_prof_size"))

summary(as.factor(team_comp$team_prof_size))

```


Percentage of women in the team

```{r}

summary(as.factor(supervisors$sv_gender))

supervisors %>%
  group_by(id_phd) %>%
  count(sv_gender) -> teamgender # creating a dataframe with the number of women/men/missing gender per phd


teamgender %>%
  left_join(teamsize, by="id_phd") -> teamgender # adding the teamsize variable we created in the chunk before, so we can calculate the share of supervisors from each gender


teamgender$prop <- teamgender$n / teamgender$teamsize # calculating the share of m/f/missing gender supervisors


teamgender <- tidyr::pivot_wider(teamgender, id_cols="id_phd", names_from = "sv_gender", names_prefix = "prop", values_from = "prop") # reshaping the dataframe so that one phd has one row again

# set NA values to 0
teamgender$propmen <- ifelse(is.na(teamgender$propmen), 0, teamgender$propmen) # some PhDs have no men on their supervision team
teamgender$propwomen <- ifelse(is.na(teamgender$propwomen), 0, teamgender$propwomen) # or no women
teamgender$propNA <- ifelse(is.na(teamgender$propNA), 0, teamgender$propNA) # or no supervisors with a missing gender



```

1+ woman in the team

```{r}

teamgender$wom_sv1 <- ifelse(teamgender$propwomen==0, 0, 1)


```

Combining gender and professor status (robustness check)

```{r}

# per-supervisor flag: is this supervisor a woman AND a professor?
supervisors$fem_prof <- ifelse(supervisors$sv_gender == "women" & supervisors$prof == 1, 1, 0)

supervisors %>%
  group_by(id_phd) %>%
  summarise(any_fem_prof = max(fem_prof, na.rm = TRUE)) -> team_femprof

team_gender_prof <- teamgender %>%
  select(id_phd, wom_sv1) %>%
  left_join(team_femprof, by = "id_phd") %>%
  mutate(team_gender_prof = case_when(
    wom_sv1 == 0 ~ "no women supervisors",
    wom_sv1 == 1 & any_fem_prof == 0 ~ "1+ woman (no professor)",
    any_fem_prof == 1 ~ "1+ woman professor"
  ))

team_gender_prof <- subset(team_gender_prof, select = c("id_phd", "team_gender_prof"))

summary(as.factor(team_gender_prof$team_gender_prof))

```



Adding both variables to the PhD dataframe

```{r}

# selecting relevant variables
phd_supervisors <- subset(phdgender, select=c(id, supervisors))

# collapsing the data again
phd_supervisors <- phd_supervisors[!duplicated(phd_supervisors$id),]

# adding teamsize, gender variables and professor variable
phd_supervisors <- left_join(phd_supervisors, teamsize, by=c("id"="id_phd"))
phd_supervisors <- left_join(phd_supervisors, teamgender, by=c("id"="id_phd"))
phd_supervisors <- left_join(phd_supervisors, professorsteam, by=c("id"="id_phd"))

# adding combined team-composition variables
phd_supervisors <- left_join(phd_supervisors, team_comp, by=c("id"="id_phd"))
phd_supervisors <- left_join(phd_supervisors, team_gender_prof, by=c("id"="id_phd"))

# removing the supervisors string, as it is already present in the base data
phd_supervisors <- subset(phd_supervisors, select=-supervisors)
supervisors <- subset(supervisors, select=-supervisors)

```




# Adding no. pubs / citations of supervisor

Scraping and cleaning of this data in `supervisors-pubs.rmd`

```{r}


supervisors %>%
  left_join(pubs_sv, by="id_phd_sv") -> supervisors 

# calculating the mean number of publications and citations at the level of phds, then log-transforming it
supervisors %>%
  group_by(id_phd) %>%
  summarise(npubs_sv = log(mean(pubs_sv, na.rm=TRUE)+1),
            ncites_sv = log(mean(cites_sv, na.rm=TRUE)+1)) -> teampubs


# adding the variables to the dataframe
phd_supervisors <- phd_supervisors %>% left_join(teampubs, by=c("id"="id_phd"))


```




# Next, we normalize the publications + citation counts

We deactivated this line of code for this replication example, because it would all be 0 due to there being only one observation per PhD year. But we still show the code below, which we used to compute the normalized publication count.


```{r, eval=FALSE}

# Calculate mean publication counts/cites per PhD year
phdgender %>%
  select(id, phd_year) %>%
  right_join(phd_supervisors, by="id") %>%
  group_by(phd_year) %>%
  summarise(teamsize = mean(teamsize, na.rm=TRUE),
            prof2p = mean(prof2p, na.rm=TRUE),
            wom_sv1 = mean(wom_sv1, na.rm=TRUE),
            npubs = mean(npubs_sv, na.rm=TRUE),
            ncites = mean(ncites_sv, na.rm=TRUE)) -> stats_by_cohort


# adding phd year to our original dataframe
phdgender %>%
  select(id, phd_year) %>%
  right_join(phd_supervisors, by="id") -> phd_supervisors

# subtracting average counts by PhD year from the observed counts
stats_by_cohort %>%
  select(phd_year, npubs, ncites) %>%
  right_join(phd_supervisors, by=c("phd_year")) %>%
  mutate(npubs_sv_norm = npubs_sv - npubs,
         ncites_sv_norm = ncites_sv - ncites) %>%
  select(-phd_year) -> phd_supervisors


```



# One row per PhD

```{r}

phd_supervisors %>%
  distinct(id, .keep_all = TRUE) -> phd_supervisors


```





# saving

```{r}

save(supervisors, file="./data/processed/supervisors.rda") # saving the data in the format of one row per supervisor

save(phd_supervisors, file="./data/processed/phd_supervisors.rda") # saving the data with the variables at the level of phds

```




