---
title: "Table 1"
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output:
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: yes

---



```{r, globalsettings, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"), cache.lazy = FALSE)
options(width = 100)

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

----

This lab journal replicates table 1.


----

# Custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R ([source](https://vbaliga.github.io/verify-that-r-packages-are-installed-and-loaded/)).


```{r, results='hide'}

rm(list = ls())

fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}


```


---

# Packages

- `tidyverse`: tidy data manipulations
- `kableExtra`: creating tables in consistent formatting


```{r, results='hide'}

packages = c("tidyverse", "kableExtra")

fpackage.check(packages)

```


---

# Input

We use the same `veni_ppf` person-period file as the main analyses, collapsed
to one row per PhD. This reproduces the actual published Table 1 (N=6,409
women / N=7,514 men).

```{r data}

load(file = "./data/processed/veni_ppf.rda")

# one row per PhD; drop the period-level veni flag, since it's only 1 in the
# person-period row where the Veni was actually received, not a person-level summary
veni_ppf %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-veni) -> phds

# person-level "ever received a Veni" flag, from the person-period file
veni_ppf %>%
  group_by(id) %>%
  summarize(veni = max(veni)) -> veni_person

phds <- phds %>% left_join(veni_person, by = "id")

```




# Tables


## Table 1

Descriptives

```{r}

phds_wom <- phds[phds$gender_2 == "women", ]
phds_men <- phds[phds$gender_2 == "men", ]

n_wom <- nrow(phds_wom)
n_men <- nrow(phds_men)

# time to Veni is only defined for actual recipients, and lives in the
# person-period file (veni_ppf$time), not in phds
veni_ppf %>% filter(veni == 1, gender_2 == "women") %>% pull(time) -> time_wom
veni_ppf %>% filter(veni == 1, gender_2 == "men") %>% pull(time) -> time_men

# continuous variable: Min/Max/Mean/SD for both genders in one row
cont_row <- function(x_wom, x_men) {
  c(min(x_wom, na.rm=TRUE), max(x_wom, na.rm=TRUE), mean(x_wom, na.rm=TRUE), sd(x_wom, na.rm=TRUE),
    min(x_men, na.rm=TRUE), max(x_men, na.rm=TRUE), mean(x_men, na.rm=TRUE), sd(x_men, na.rm=TRUE))
}

# binary variable: Min/Max fixed at 0/1, no SD (matches the published table)
bin_row <- function(x_wom, x_men) {
  c(0, 1, mean(x_wom, na.rm=TRUE), NA,
    0, 1, mean(x_men, na.rm=TRUE), NA)
}

# one level of a categorical variable, treated as its own 0/1 dummy row
cat_row <- function(x_wom, x_men, level) {
  c(0, 1, mean(x_wom == level, na.rm=TRUE), NA,
    0, 1, mean(x_men == level, na.rm=TRUE), NA)
}

# data level -> published row label
field_map <- c(
  "Biological and Health Sciences"     = "Biological and Health Sciences",
  "Physical and Mathematical Sciences" = "Physical and mathematical sciences",
  "Social and Behavioral Sciences"     = "Social and behavioral sciences",
  "Engineering"                        = "Engineering",
  "Agricultural Sciences"              = "Agricultural sciences",
  "Humanities"                         = "Humanities",
  "other"                              = "Other",
  "missing"                            = "Missing"
)

uni_map <- c(
  "EUR" = "Erasmus University Rotterdam",
  "LU"  = "Leiden University",
  "RU"  = "Radboud University",
  "RUG" = "University of Groningen",
  "TUD" = "Delft University of Technology",
  "TUE" = "Eindhoven University of Technology",
  "TI"  = "Tilburg University",
  "UM"  = "Maastricht University",
  "UT"  = "University of Twente",
  "UU"  = "Utrecht University",
  "UvA" = "University of Amsterdam",
  "VU"  = "Vrije Universiteit Amsterdam",
  "WUR" = "Wageningen University and Research Centre"
)

rows <- list(
  "Veni receipt"             = bin_row(phds_wom$veni, phds_men$veni),
  "Time to Veni (in years)"  = cont_row(time_wom, time_men),
  "PhD cohort"                = cont_row(phds_wom$phd_year, phds_men$phd_year),
  "Team size"                = cont_row(phds_wom$teamsize, phds_men$teamsize),
  "2+ Professors"            = bin_row(phds_wom$prof2p, phds_men$prof2p),
  "Publication productivity" = cont_row(phds_wom$npubs_sv_norm, phds_men$npubs_sv_norm),
  "1+ Women"                 = bin_row(phds_wom$wom_sv1, phds_men$wom_sv1)
)

for (lvl in names(field_map)) {
  rows[[field_map[[lvl]]]] <- cat_row(phds_wom$field, phds_men$field, lvl)
}

for (code in names(uni_map)) {
  rows[[uni_map[[code]]]] <- cat_row(phds_wom$uni, phds_men$uni, code)
}

t1 <- as.data.frame(do.call(rbind, rows))
colnames(t1) <- c("Min", "Max", "Mean", "SD", "Min", "Max", "Mean", "SD")

# section header rows (no data, matches "Supervision team"/"Field"/"University"
# in the published table) -- tracked as index positions for pack_rows() below
supervision_start <- match("Team size", rownames(t1))
supervision_end   <- match("1+ Women", rownames(t1))
field_start       <- match(field_map[[1]], rownames(t1))
field_end         <- match(field_map[[length(field_map)]], rownames(t1))
uni_start         <- match(uni_map[[1]], rownames(t1))
uni_end           <- match(uni_map[[length(uni_map)]], rownames(t1))

# Min/Max print at their natural precision (so 0/1/7/22 show as plain
# integers, matching the published table), while Mean/SD are always padded
# to 3 decimals
minmax_cols <- c(1, 2, 5, 6)
meansd_cols <- c(3, 4, 7, 8)

t1_fmt <- t1
t1_fmt[minmax_cols] <- lapply(t1[minmax_cols], function(x) ifelse(is.na(x), "", format(round(x, 3), trim = TRUE)))
t1_fmt[meansd_cols] <- lapply(t1[meansd_cols], function(x) ifelse(is.na(x), "", format(round(x, 3), nsmall = 3, trim = TRUE)))
rownames(t1_fmt) <- rownames(t1)

```


```{r}

t1_fmt %>%
  kable(format = 'html', align = "cccccccc", escape = FALSE,
        caption = '<b>Table 1.</b> Descriptive statistics, split out by gender') %>%
  add_header_above(c(" " = 1,
                      setNames(4, paste0("Women (N=", format(n_wom, big.mark=","), ")")),
                      setNames(4, paste0("Men (N=", format(n_men, big.mark=","), ")")))) %>%
  kable_classic(full_width = FALSE, html_font = "Cambria") %>%
  pack_rows("Supervision team", supervision_start, supervision_end) %>%
  pack_rows("Field", field_start, field_end) %>%
  pack_rows("University", uni_start, uni_end) %>%
  kable_styling(font_size = 14) %>%
  footnote(general = c("Time to Veni only summarized for Veni recipients.",
                        "Source: Dutch Doctoral Recipients (D3) data 1997-2019."),
           general_title = "") -> table1

table1

```



-----
